### 2022-09-02 src/tex/ms.tex
[showyourwork] overleaf sync

%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style

%
\documentclass{aa}  
\usepackage{graphicx}
\usepackage{rotating}
\usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{color}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{hyperref}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\usepackage{showyourwork}

\begin{document}

   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards Beta Pictoris}

   \author{M.A. Kenworthy
          \inst{1}
          \and
          E. de Mooij\inst{2}
          \and
          C. Opitom\inst{3}
          \and
          A.\ Brandeker\inst{4}
          \and 
          F. Kiefer\inst{5}
          \and
          A. Fitzsimmons \inst{6}
          }

   \institute{Institute for Astronomy (IfA), University of Vienna,
              T\"urkenschanzstrasse 17, A-1180 Vienna\\
              \email{wuchterl@amok.ast.univie.ac.at}
         \and
             DCU, ...\\
        \and
             ESO (European Southern Observatory) - Alonso de Cordova 3107, Vitacura, Santiago, Chile\\
        \and
        Department of Astronomy, AlbaNova University Center, Stockholm University, 106 91 Stockholm, Sweden, \email{alexis@astro.su.se}\\
        \and
        Paris
        \and
            Astrophysics Research Centre, School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, UK
             }

   \date{Received XXXX; Accepted XXXX}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {Beta Pic has FEBs which are seen as variable transient absorption features towards Beta Pictoris.}
  % aims heading (mandatory)
   {To detect cyanogen (CN) in the FEB spectrum, confirming that they are similar to comets in the Solar System.}
  % methods heading (mandatory)
   {We combine the HARPS spectra from the past 20 years to make a high signal to noise ratio spectrum and look for the CN band head. We also combine UVES data to confirm our non-detections/detections.}
  % results heading (mandatory)
   {No CN is seen to a level of XXX ppt, indicating that there is less CN in these FEBs than Solar system comets.}
  % conclusions heading (optional), leave it empty if necessary 
   {FEBs are not Solar System comets in composition.}

   \keywords{comets --- transits, spectroscopy}

   \maketitle
%
%________________________________________________________________

\section{Introduction}

Comets and exocomets are Cool!

Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).

To the contrary of what is observed in the case of FEBs, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.

%Spectroscopy of Solar system comets when they are very close to the Sun is rare due to observational difficulties. The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki. For this comets, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun. At distances greater than 0.4~au, CH, CN, C$_2$, and C$_3$ emission bands dominated the spectrum. However, at 0.15 au from the Sun, the only molecular emission detected was CN, while numerous atomic lines were visible ([OI], NaI, KI, CaII, CrI, MnI, FeI, NiI, CuI, VI) (\citealp{Dufay65}; \citealp{Thackeray1966}; \citealp{Preston1967}; \citealp{Slaughter1969}).

While the above neutral/ionic signatures in FEBs are well established, it is important to note that detection of these species in Solar system comets is rare. Ca~II and Fe~I have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki. For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun. At distances greater than 0.4~au, CH, CN, C$_2$, and C$_3$ emission bands dominated the spectrum. However, at 0.15 au from the Sun, the only molecular emission detected was CN, while numerous atomic lines were visible ([OI], NaI, KI, CaII, CrI, MnI, FeI, NiI, CuI, VI) (\citealp{Dufay65}; \citealp{Thackeray1966}; \citealp{Preston1967}; \citealp{Slaughter1969}).
Additionally, a tail of FE~I atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.

On the other hand, Na~I D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines [REFs]. The high efficiency of the NaI D transition makes it easily detectable, even for relatively low column density. A notable discovery was a spectacular tail of Na~I associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.

These characteristics imply that Ca~II and Fe~I are predominantly locked up within cometary dust gains, and only observed when a comet is close enough to the Sun to allow their sublimation. This occurs at $r\leq 0.03-0.06$ au for a dust grain with Bond albedo $\sim0.01$ and a sublimation temperature of $T\simeq 1600$K, depending on the thermal model assumed. On the other hand, the origin of the NaI tail observed in numerous comets at larger distances from the Sun is still not very well understood [Cremonese+2002]. Release from dust grains as well as molecular processes have been suggested as possible sources of NaI in the coma and tail of comets annd explain its presence at large solar distances \citep{Cremonese1997}.
%Na appears to be weakly bound to the dust grains and released at larger solar distances.

For the majority of Solar system comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines [{\it e.g.} \citep{hyland2019}]. Most of the neutral and ionic molecular emission results from resonance fluorescence with solar photons. Some species, such as H$_2$O$^+$ and  CO$^+$ result from ionization of parent molecules (i.e. molecules released directly by the sublimation of nuclear ices), all other molecules observed are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma. Another process also observed in optical spectrum of comets is prompt atomic emission  ([OI], [CI], and [NI]). Those forbidden transitions are the result of atoms produced in an excited state by the photodissociation of parent molecules in the coma. 
%Only the Na~I emission is currently thought to be generated by release mainly from dust grains ejected by the comet.

Of all cometary gas emission, the highest signal to noise normally occurs with the CN (0-0) band at $\lambda\simeq 3880$\AA. It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun {\it e.g.}  \cite{Fitzsimmons1996}. The relative abundance in the coma of most comets of CN/OH$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1 au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae. Historically, the CN was believed to be created from photodissociation of HCN, which is present in abundances of the order of 1\% relative to water in cometary ices.  High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner 2014}. However, it is now known that in many comets a substantial fraction of CN is released from sub-micron dust grains in the inner coma of comets {\it e.g.} \cite{Fray2005}.

The C$_2$ (0-0) band at $\lambda\simeq 5160$\AA \ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth. The OH (0-0) band at $\lambda\simeq 3080$ \AA \ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux. Strong CO$^+$ emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) [REFS]). However this is normally significantly weaker than the observed CN emission, with only ??? comets

Given the ubiquitous signature of CN emission in Solar system comets, we have embarked on an archival search for this species in the FEBs around Beta Pic. Detection of this species would provide a solid link between cometary bodies in our Solar system and the Beta Pic system.

\section{Data description and analysis}
For the study in this paper, we use all the available data from the High Accuracy Radial Velocity Planet Searcher (HARPS) and the ESO 3.6m telescope in Chile. In addition, we complement this with observations with the Ultra-violet Visible Echelle Spectrograph (UVES) at the Very Large Telescope in Chile.

\subsection{HARPS observations}
We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and May 2018. Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years. Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.

\subsection{UVES observations}
To supplement the HARPS observations, we use 160 epochs of UVES observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751. The details for these observations are explained in more detail in \cite{vansluijs2019}, and only briefly summarised here. These observations were all obtained using the same instrument setup. We used the standard 437+760 mode of UVES, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm. In this mode, the CD\#2 and CD\#4 crossdispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm. For the remainder of the paper, we will only focus on the data from the blue arm of UVES, as this covers the strong CN band-head seen in Solar system comets. 
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

The data were reduced using the ESO UVES pipeline version 5.7.0 through ESO Reflex tool in order to provide as homogeneous a dataset as possible.

\subsection{Initial data processing}
The data from both instruments was processed in very similar ways. For both datasets, we used the 2d-unmerged echelle spectra, and we treated each order separately. Initially, we aligned all the spectra in the stellar rest-frame using a linear interpolation.

Subsequently, we applied a correction for variations in the instrumental blaze by selecting a reference spectrum and dividing all the spectra by this reference. The ratio was then binned, removing outliers, and a polynomial was fit to the data. For UVES we used a Nth degree polynomial, while for HARPS we used a 2nd degree polynomial. This polynomial was then divided from the spectrum under consideration. We note that the blaze correction will also remove non-instrumental effects, including variations in atmospheric transmission and seeing.

The blaze-corrected spectra taken within a night were averaged together [Should we use a weighted average?]. We note that for HARPS, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.

\section{Searches for cometary species}
After the initial data analysis, we proceed to with our search for lines from CN. Although we are interested in lines from the exocomets, we first coadd the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar CN absorption. These coadded spectra for HARPS and UVES are shown in Fig.~\ref{fig:coadd_restframe}. No obvious feature jumps out, and we can rule out circumstellar CN down to NNNN.

Since the exocomets have a clear radial velocity with respect to $\beta$ Pic, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the Ca II H \& K lines, as well as the MM epochs with the weakest cometary features. The selection was done by .......
The spectra with only weak exocometary features were co-averaged in the stellar restframe in order to create a stellar master spectrum. This master-spectrum was divided out of all the remaining spectra in order to create relative spectra. 
The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined. The combined exocomet aligned spectra for both the CA H\&K lines and CN band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present. [Do we need to add a correction to account for any radiation pressure, if so, is there a way to estimate that?]

[Do we want to do a simple CCF to see if we can combine the individual lines?]

\subsection{CN}

\subsection{Other Species? CO$^+$, C$_2$?}

\section{Discussion}

\section{Conclusions}

\begin{acknowledgements}

      The authors thank the Lorentz Centre at Leiden University for organising the workshop ``Exocomets: Understanding the Composition of Planetary Building Blocks'' which led to the study in this paper. 
%
      Part of this work was supported by the German
      \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project
      number Ts~17/2--1.
      %
We made use of the {\tt Python} programming language \citep{rossum1995} and the open-source {\tt Python} packages {\tt numpy} \citep{walt2011}, {\tt matplotlib} \citep{hunter2007}, {\tt astropy} \citep{astropy2013}.
%      
An online repository with materials used in this work is available at \url{https://github.com/sebastian-zieba/betaPic_comet}
\end{acknowledgements}

%-------------------------------------------------------------------

\bibliographystyle{aa}
\bibliography{febspec.bib}

%\begin{thebibliography}{}

%  \bibitem[1966]{baker} Baker, N. 1966,
%      in Stellar Evolution,
%      ed.\ R. F. Stein,\& A. G. W. Cameron
%      (Plenum, New York) 333

%   \bibitem[1988]{balluch} Balluch, M. 1988,
%      A\&A, 200, 58

%   \bibitem[1980]{cox} Cox, J. P. 1980,
%      Theory of Stellar Pulsation
%      (Princeton University Press, Princeton) 165

 %  \bibitem[1969]{cox69} Cox, A. N.,\& Stewart, J. N. 1969,
 %     Academia Nauk, Scientific Information 15, 1

 %  \bibitem[1980]{mizuno} Mizuno H. 1980,
 %     Prog. Theor. Phys., 64, 544

%   \bibitem[1987]{tscharnuter} Tscharnuter W. M. 1987,
%      A\&A, 188, 55

%   \bibitem[1992]{terlevich} Terlevich, R. 1992, in ASP Conf. Ser. 31, 
%      Relationships between Active Galactic Nuclei and Starburst Galaxies, 
%      ed. A. V. Filippenko, 13

%   \bibitem[1980a]{yorke80a} Yorke, H. W. 1980a,
%      A\&A, 86, 286

%   \bibitem[1997]{zheng} Zheng, W., Davidsen, A. F., Tytler, D. \& Kriss, G. A.
%      1997, preprint
%\end{thebibliography}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Examples for figures using graphicx
A guide "Using Imported Graphics in LaTeX2e"  (Keith Reckdahl)
is available on a lot of LaTeX public servers or ctan mirrors.
The file is : epslatex.pdf 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%_____________________________________________________________
%                 A figure as large as the width of the column
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[width=\hsize]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%_____________________________________________________________
%                                    One column rotated figure
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[angle=-90,width=3cm]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%_____________________________________________________________
%                        Figure with caption on the right side 
%-------------------------------------------------------------
   \begin{figure}
   \sidecaption
   \includegraphics[width=3cm]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%_____________________________________________________________
%
%_____________________________________________________________
%                                Figure with a new BoundingBox 
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[bb=10 20 100 300,width=3cm,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%_____________________________________________________________
%
%_____________________________________________________________
%                                      The "resizebox" command 
%-------------------------------------------------------------
   \begin{figure}
   \resizebox{\hsize}{!}
            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%______________________________________________________________
%
%_____________________________________________________________
%                                             Two column Figure 
%-------------------------------------------------------------
   \begin{figure*}
   \resizebox{\hsize}{!}
            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure*}
%
%______________________________________________________________
%
%_____________________________________________________________
%                                             Simple A&A Table
%_____________________________________________________________
%
\begin{table}
\caption{Nonlinear Model Results}             % title of Table
\label{table:1}      % is used to refer this table in the text
\centering                          % used for centering table
\begin{tabular}{c c c c}        % centered columns (4 columns)
\hline\hline                 % inserts double horizontal lines
HJD & $E$ & Method\#2 & Method\#3 \\    % table heading 
\hline                        % inserts single horizontal line
   1 & 50 & $-837$ & 970 \\      % inserting body of the table
   2 & 47 & 877    & 230 \\
   3 & 31 & 25     & 415 \\
   4 & 35 & 144    & 2356 \\
   5 & 45 & 300    & 556 \\ 
\hline                                   %inserts single line
\end{tabular}
\end{table}
%
%_____________________________________________________________
%                                             Two column Table 
%_____________________________________________________________
%
\begin{table*}
\caption{Nonlinear Model Results}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c l l l }     % 7 columns 
\hline\hline       
                      % To combine 4 columns into a single one 
HJD & $E$ & Method\#2 & \multicolumn{4}{c}{Method\#3}\\ 
\hline                    
   1 & 50 & $-837$ & 970 & 65 & 67 & 78\\  
   2 & 47 & 877    & 230 & 567& 55 & 78\\
   3 & 31 & 25     & 415 & 567& 55 & 78\\
   4 & 35 & 144    & 2356& 567& 55 & 78 \\
   5 & 45 & 300    & 556 & 567& 55 & 78\\
\hline                  
\end{tabular}
\end{table*}
%
%-------------------------------------------------------------
%                                          Table with notes 
%-------------------------------------------------------------
%
% A single note
\begin{table}
\caption{\label{t7}Spectral types and photometry for stars in the
  region.}
\centering
\begin{tabular}{lccc}
\hline\hline
Star&Spectral type&RA(J2000)&Dec(J2000)\\
\hline
69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
LS~1267~(86) &O8\,V     &09 15 52.787&11.07\\
24.6         &7.58      &1.37 &0.20\\
\hline
LS~1262      &B0\,V     &09 15 05.17&11.17\\
MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\\
LS~1269      &O8.5\,V   &09 15 56.60&10.85\\
\hline
\end{tabular}
\tablefoot{The top panel shows likely members of Pismis~11. The second
panel contains likely members of Alicante~5. The bottom panel
displays stars outside the clusters.}
\end{table}
%
% More notes
%
\begin{table}
\caption{\label{t7}Spectral types and photometry for stars in the
  region.}
\centering
\begin{tabular}{lccc}
\hline\hline
Star&Spectral type&RA(J2000)&Dec(J2000)\\
\hline
69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
LS~1267~(86) &O8\,V     &09 15 52.787&11.07\tablefootmark{a}\\
24.6         &7.58\tablefootmark{1}&1.37\tablefootmark{a}   &0.20\tablefootmark{a}\\
\hline
LS~1262      &B0\,V     &09 15 05.17&11.17\tablefootmark{b}\\
MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\tablefootmark{c}\\
LS~1269      &O8.5\,V   &09 15 56.60&10.85\tablefootmark{d}\\
\hline
\end{tabular}
\tablefoot{The top panel shows likely members of Pismis~11. The second
panel contains likely members of Alicante~5. The bottom panel
displays stars outside the clusters.\\
\tablefoottext{a}{Photometry for MF13, LS~1267 and HD~80077 from
Dupont et al.}
\tablefoottext{b}{Photometry for LS~1262, LS~1269 from
Durand et al.}
\tablefoottext{c}{Photometry for MO2-119 from
Mathieu et al.}
}
\end{table}
%
%-------------------------------------------------------------
%                                       Table with references 
%-------------------------------------------------------------
%
\begin{table*}[h]
 \caption[]{\label{nearbylistaa2}List of nearby SNe used in this work.}
\begin{tabular}{lccc}
 \hline \hline
  SN name &
  Epoch &
 Bands &
  References \\
 &
  (with respect to $B$ maximum) &
 &
 \\ \hline
1981B   & 0 & {\it UBV} & 1\\
1986G   &  $-$3, $-$1, 0, 1, 2 & {\it BV}  & 2\\
1989B   & $-$5, $-$1, 0, 3, 5 & {\it UBVRI}  & 3, 4\\
1990N   & 2, 7 & {\it UBVRI}  & 5\\
1991M   & 3 & {\it VRI}  & 6\\
\hline
\noalign{\smallskip}
\multicolumn{4}{c}{ SNe 91bg-like} \\
\noalign{\smallskip}
\hline
1991bg   & 1, 2 & {\it BVRI}  & 7\\
1999by   & $-$5, $-$4, $-$3, 3, 4, 5 & {\it UBVRI}  & 8\\
\hline
\noalign{\smallskip}
\multicolumn{4}{c}{ SNe 91T-like} \\
\noalign{\smallskip}
\hline
1991T   & $-$3, 0 & {\it UBVRI}  &  9, 10\\
2000cx  & $-$3, $-$2, 0, 1, 5 & {\it UBVRI}  & 11\\ %
\hline
\end{tabular}
\tablebib{(1)~\citet{branch83};
(2) \citet{phillips87}; (3) \citet{barbon90}; (4) \citet{wells94};
(5) \citet{mazzali93}; (6) \citet{gomez98}; (7) \citet{kirshner93};
(8) \citet{patat96}; (9) \citet{salvo01}; (10) \citet{branch03};
(11) \citet{jha99}.
}
\end{table}
%_____________________________________________________________
%                      A rotated Two column Table in landscape  
%-------------------------------------------------------------
\begin{sidewaystable*}
\caption{Summary for ISOCAM sources with mid-IR excess 
(YSO candidates).}\label{YSOtable}
\centering
\begin{tabular}{crrlcl} 
\hline\hline             
ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
& YSO type$^{d}$ & Status & Comments\\
\hline
  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
\hline
  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
  2 & 0.79:           & 0.97: & Class II ?     & New & \\
  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
\hline
  \multicolumn{6}{c}{\it Previously known YSOs} \\
\hline
  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
\hline
\end{tabular}
\end{sidewaystable*}
%_____________________________________________________________
%                      A rotated One column Table in landscape  
%-------------------------------------------------------------
\begin{sidewaystable}
\caption{Summary for ISOCAM sources with mid-IR excess 
(YSO candidates).}\label{YSOtable}
\centering
\begin{tabular}{crrlcl} 
\hline\hline             
ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
& YSO type$^{d}$ & Status & Comments\\
\hline
  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
\hline
  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
  2 & 0.79:           & 0.97: & Class II ?     & New & \\
  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
\hline
  \multicolumn{6}{c}{\it Previously known YSOs} \\
\hline
  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
\hline
\end{tabular}
\end{sidewaystable}
%
%_____________________________________________________________
%                              Table longer than a single page  
%-------------------------------------------------------------
% All long tables will be placed automatically at the end, after 
%                                        \end{thebibliography}
%
\begin{longtab}
\begin{longtable}{lllrrr}
\caption{\label{kstars} Sample stars with absolute magnitude}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endfirsthead
\caption{continued.}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endhead
\hline
\endfoot
%%
Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
         &      &      &      & H & 0.008686\\
Gl 86 
\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
         & 5.92 & K0 V & 10.91& S & 0.058230\\
\end{longtable}
\end{longtab}
%
%_____________________________________________________________
%                              Table longer than a single page
%                                             and in landscape 
%  In the preamble, use:       \usepackage{lscape}
%-------------------------------------------------------------
% All long tables will be placed automatically at the end, after
%                                        \end{thebibliography}
%
\begin{longtab}
\begin{landscape}
\begin{longtable}{lllrrr}
\caption{\label{kstars} Sample stars with absolute magnitude}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endfirsthead
\caption{continued.}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endhead
\hline
\endfoot
%%
Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
         &      &      &      & H & 0.008686\\
Gl 86
\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
         & 5.92 & K0 V & 10.91& S & 0.058230\\
\end{longtable}
\end{landscape}
\end{longtab}
%
% Online Material
%_____________________________________________________________
%        Online appendices have to be placed at the end, after
%                                        \end{thebibliography}
%-------------------------------------------------------------
\end{thebibliography}

\Online

\begin{appendix} %First online appendix
\section{Background galaxy number counts and shear noise-levels}
Because the optical images used in this analysis...

\begin{figure*}
\centering
\includegraphics[width=16.4cm,clip]{1787f24.ps}
\caption{Plotted above...}
\label{appfig}
\end{figure*}

Because the optical images...
\end{appendix}

\begin{appendix} %Second online appendix
These studies, however, have faced...
\end{appendix}

\end{document}
%
%_____________________________________________________________
%        Some tables or figures are in the printed version and
%                      some are only in the electronic version
%-------------------------------------------------------------
%
% Leave all the tables or figures in the text, at their right place 
% and use the commands \onlfig{} and \onltab{}. These elements
% will be automatically placed at the end, in the section
% Online material.

\documentclass{aa}
...
\begin{document}
text of the paper...
\begin{figure*}%f1
\includegraphics[width=10.9cm]{1787f01.eps}
\caption{Shown in greyscale is a...}
\label{cl12301}}
\end{figure*}
...
from the intrinsic ellipticity distribution.
% Figure 2 available electronically only
\onlfig{
\begin{figure*}%f2
\includegraphics[width=11.6cm]{1787f02.eps}
\caption {Shown in greyscale...}
\label{cl1018}
\end{figure*}
}

% Figure 3 available electronically only
\onlfig{
\begin{figure*}%f3
\includegraphics[width=11.2cm]{1787f03.eps}
\caption{Shown in panels...}
\label{cl1059}
\end{figure*}
}

\begin{figure*}%f4
\includegraphics[width=10.9cm]{1787f04.eps}
\caption{Shown in greyscale is...}
\label{cl1232}}
\end{figure*}

\begin{table}%t1
\caption{Complexes characterisation.}\label{starbursts}
\centering
\begin{tabular}{lccc}
\hline \hline
Complex & $F_{60}$ & 8.6 &  No. of  \\
...
\hline
\end{tabular}
\end{table}
The second method produces...

% Figure 5 available electronically only
\onlfig{
\begin{figure*}%f5
\includegraphics[width=11.2cm]{1787f05.eps}
\caption{Shown in panels...}
\label{cl1238}}
\end{figure*}
}

As can be seen, in general the deeper...
% Table 2 available electronically only
\onltab{
\begin{table*}%t2
\caption{List of the LMC stellar complexes...}\label{Properties}
\centering
\begin{tabular}{lccccccccc}
\hline  \hline
Stellar & RA & Dec & ...
...
\hline
\end{tabular}
\end{table*}
}

% Table 3 available electronically only
\onltab{
\begin{table*}%t3
\caption{List of the derived...}\label{IrasFluxes}
\centering
\begin{tabular}{lcccccccccc}
\hline \hline
Stellar & $f12$ & $L12$ &...
...
\hline
\end{tabular}
\end{table*}
}
%
%-------------------------------------------------------------
%     For the online material, table longer than a single page
%                 In the preamble for landscape case, use : 
%                                          \usepackage{lscape}
%-------------------------------------------------------------
\documentclass{aa}
\usepackage[varg]{txfonts}
\usepackage{graphicx}
\usepackage{lscape}

\begin{document}
text of the paper
% Table will be print automatically at the end, in the section Online material.
\onllongtab{
\begin{longtable}{lrcrrrrrrrrl}
\caption{Line data and abundances ...}\\
\hline
\hline
Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & N & e &  rad & $\delta$ & $\delta$ 
red & References \\
\hline
\endfirsthead
\caption{Continued.} \\
\hline
Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & B & C &  rad & $\delta$ & $\delta$ 
red & References \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
A & CH & 1 &3638 & 0.002 & $-$2.551 &  &  &  & $-$150 & 150 &  Jorgensen et al. (1996) \\                    
\end{longtable}
}% End onllongtab

% Or for landscape, large table:

\onllongtab{
\begin{landscape}
\begin{longtable}{lrcrrrrrrrrl}
...
\end{longtable}
\end{landscape}
}% End onllongtab

### 2023-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % according to the author-year natbib style
-
-%
 \documentclass{aa}  
-\usepackage{graphicx}
 \usepackage{rotating}
-\usepackage[varg]{txfonts}
-\usepackage{txfonts}
-\usepackage{color}
 \usepackage{natbib}
 \usepackage{amsmath}
+\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
+
+\usepackage{color}
 \usepackage{hyperref}
-\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
+\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}
 
@@
 \usepackage{showyourwork}
+
+% the three lines suppress the hyperref 'link empty' warnings
+% explanation at: https://tex.stackexchange.com/questions/345764/journal-class-shows-package-hyperref-warning-suppressing-link-with-empty-targe
+\makeatletter
+\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}
+\makeatother
 
@@
 Historically, the CN was believed to be created from photodissociation of HCN, which is present in abundances of the order of 1\% relative to water in cometary ices.
-High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner 2014}.
+High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner2014}.
 However, it is now known that in many comets a substantial fraction of CN is released from sub-micron dust grains in the inner coma of comets {\it e.g.} \cite{Fray2005}.
@@
 To supplement the HARPS observations, we use 160 epochs of UVES observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
-The details for these observations are explained in more detail in \cite{vansluijs2019}, and only briefly summarised here.
+%
+The details for these observations are explained in more detail in \cite{vansluijs2019}, and summarised here.
+%
 These observations were all obtained using the same instrument setup.
+%
 We used the standard 437+760 mode of UVES, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
-In this mode, the CD\#2 and CD\#4 crossdispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm.
+%
+In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm.
+%
 For the remainder of the paper, we will only focus on the data from the blue arm of UVES, as this covers the strong CN band-head seen in Solar system comets.
+%
 For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).
@@
 \subsection{Initial data processing}
-The data from both instruments was processed in very similar ways.
+The data from both instruments was processed in similar ways.
+%
 For both datasets, we used the 2d-unmerged echelle spectra, and we treated each order separately.
-Initially, we aligned all the spectra in the stellar rest-frame using a linear interpolation.
+%
+All the spectra were transformed into the stellar rest-frame using linear interpolation.
+
+The number of observations varies from night to night, from a few spectra to over a hundred.
+%
+An average of all the spectra in one night was made for all the nights of observations.
+
+The blaze function dominates the flux profile of the spectra.
+%
+One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function: this spectrum was binned in the spectral direction to remove both narrow absorption lines and the rotationally broadened stellar chromospheric lines, but preserve the shape of the blaze function.
+%
+A low order second or third order polynomial was fit to each echelle order, and this fit spectrum served as a blaze function estimate.
+
+For all the spectra in a given night:
+ - Divide the spectrum by the reference spectrum, which hs the fit of the low order polynomial to the best night spectrum.
+ - Combine all these spectrum within a single night all together, to form the final night spectrum (this still has the BLAZE function in it...)
+
+ For all the night spectra:
+
+ We median combine all the nights together.
+
+ Bin the spectrum and clip it, interpolate using a cubic spline.
+
+ Divide this interpolated cubic spline into each of the nightly spectra.
+
+THis removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.
+
+We then fit a second order polynomial to each individual night and divide this out, resulting in a flattened spectrum for each night.
 
@@
 \bibliographystyle{aa}
-\bibliography{febspec.bib}
+\bibliography{bib.bib}
 

### 2023-01-04 src/scripts/analyse_HARPS_spectra.py
Ernst day of commenting

@@ -1,0 +1,460 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jul 26 15:54:53 2022
+
+@author: demooij
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.io import fits
+import matplotlib as mpl
+
+mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
+
+from pylab import rcParams
+from scipy import interpolate
+from astropy import units as u
+from astropy import constants as const
+from astropy.stats import sigma_clip
+from astropy.stats.sigma_clipping import sigma_clipped_stats
+from scipy.interpolate import interp1d
+from numpy.polynomial import Polynomial as P
+from scipy import signal
+from scipy.optimize import curve_fit
+import scipy.stats as stats
+import time
+import gc
+
+rcParams['figure.figsize'] = 12, 8
+
+## this is to convolve an arbitrary spectrum in (wave, spec) with velocity broadening effects.
+## dv is in km/s (which here we're setting to c/R)
+def wavegrid(lmin,lmax,R):
+    '''lmin is the minimum wavelength, lmax is the maximum wavelength you want, R is the spectral resolution
+    returns a wavelength vector that is constant in velocity space.
+    then interpolate to this wavelength grid'''
+    dx=np.log(1.+1./R) ## the log10 gives you constant velocity spacing
+    x=np.arange(np.log(lmin),np.log(lmax),dx)
+    return np.exp(x)
+
+
+## Read in the model from a file and convert the crossesction to opacity for a given columndensity.
+def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
+    
+    ## set sampling for convolution to 0.25 km/s
+    res_interp=12e5
+    
+    c = np.load(fn)
+    w = np.load('CN/CN_wavelengths.npy') #np.arange(3850, 3885, 0.0001)
+    tau = N * c
+    prof = np.exp(-tau)
+    
+      
+    ## Sample the model at a constant resolution for convolution
[…]

### 2023-01-04 src/scripts/quickplot_HARPS.py

@@ -1,0 +1,32 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Dec 20 11:29:29 2022
+
+@author: demooij
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+data=np.loadtxt('results.txt')
+
+T=np.unique(data[:,0])
+N=np.unique(data[:,1])
+sig_sim=data[:,-1].reshape(2,1)
+plt.pcolormesh(N,T,sig_sim)
+plt.xscale("log")
+plt.yscale("log")
+plt.colorbar()
+plt.xlabel('N [$cm^{-2}$]')
+plt.ylabel('T [K]')
+plt.savefig('sigfull.png')
+
+
+plt.figure()
+plt.pcolormesh(N,T,sig_sim,vmin=-10,vmax=50)
+plt.xscale("log")
+plt.yscale("log")
+plt.colorbar()
+plt.xlabel('N [$cm^{-2}$]')
+plt.ylabel('T [K]')
+plt.savefig('sigfocus.png')

### 2023-01-04 src/scripts/read_e2ds_data_HARPS.py

@@ -1,0 +1,321 @@
+from astropy.io import fits
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+from scipy import interpolate
+from scipy import optimize
+import fnmatch
+
+# this takes about 18 minutes on desktop mac
+
+def get_wave(data,header):
+   '''gets the polynomial wavelength solution from the ESO keywords for a particular e2ds spectrum'''
+   wave=data*0.
+   no=data.shape[0]
+   npix=data.shape[1]
+   d=header['ESO DRS CAL TH DEG LL']
+   xx0=np.arange(npix)
+   xx=[]
+   for i in range(d+1):
+      xx.append(xx0**i)
+   xx=np.asarray(xx)
+
+   for o in range(no):
+      for i in range(d+1):
+         idx=i+o*(d+1)
+         par=header['ESO DRS CAL TH COEFF LL%d' % idx]
+         wave[o,:]=wave[o,:]+par*xx[i,:]
+   return wave
+
+
+def blaze_cor(spec,ref_spec,polyorder=2):
+   '''blaze variation correction on a stack of spectra
+   spec - spectrum to be corrected for blaze variation
+   ref_spec - the reference spectrum to which the blaze variation is normalized
+   polyorder - the polynomial order that is fit to the blaze variation '''
+
+   # take the ratio of the input to the reference spectrum
+   rat=spec/ref_spec
+
+   # mask out edges of the spectrum to prevent problems with smoothing later on
+   rat[0,0:200]=np.nan
+   rat[0,-400:]=np.nan
+   rat[:,0:50]=np.nan
+   rat[:,-50:]=np.nan
+
+   # get the number of spectral orders in the spectrum
+   nord=rat.shape[0]
+
+   # values used for fitting the polynomial in pixel space
+   x0=np.arange(4096.)
+   x1=x0.reshape(4096//256,256)
+
+   # reshape the output spectrum for binning
+   o_rat=rat.reshape(nord,4096//256,256)
+
+   # take median of each bin...
+   med=np.median(o_rat,axis=2)
+
+   # take the median absoluate deviation (MAD) for each bin
+   sig=np.nanmedian( np.abs(o_rat-med[:,:,np.newaxis]),axis=2)*1.5
+   # flag bad binned data more than 1.75 sigma
[…]

### 2023-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).
+Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI). HELLO WORLD!
 
@@
 \subsection{HARPS observations}
-We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and May 2018.
+We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and March 2020.
 Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years.
 Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
+For this analysis we used the E2DS files downloaded directly from the ESO archive.
 

### 2023-01-06 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -9,6 +9,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from astropy.io import fits
 import matplotlib as mpl
+import paths
 
 mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
 
@@ -45,8 +46,8 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
     ## set sampling for convolution to 0.25 km/s
     res_interp=12e5
     
-    c = np.load(fn)
-    w = np.load('CN/CN_wavelengths.npy') #np.arange(3850, 3885, 0.0001)
+    c = np.load(paths.data/fn)
+    w = np.load(paths.data/'CN/CN_wavelengths.npy') #np.arange(3850, 3885, 0.0001)
     tau = N * c
     prof = np.exp(-tau)
     
@@ -75,10 +76,10 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
 
 ##Read in data
 def read_data(order=[0,1,2,3,4,5,6,7]):
-    nspec = fits.getdata('2d_nspec.fits')
-    spec = fits.getdata('2d_spec.fits')
-    wlen = fits.getdata('2d_wavelength.fits')
-    bary = fits.getdata('2d_baryvel.fits')
+    nspec = fits.getdata(paths.data/'2d_nspec.fits')
+    spec = fits.getdata(paths.data/'2d_spec.fits')
+    wlen = fits.getdata(paths.data/'2d_wavelength.fits')
+    bary = fits.getdata(paths.data/'2d_baryvel.fits')
     return nspec,spec[:,order,:],wlen[order,:],bary
 
 
@@ -399,10 +400,10 @@ def fold_comet(v_ccf,ccf,sim_ccf,T_gas,N,binsize,idx_comets,v_comets):
 def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,f,binsize=81,binsize2=400,nskip=25,v_cutoff=50,v_comet=0.,idx_comet=0.):
     ## Define a range of column densities to use (mainly injection)
     N0=np.hstack([np.arange(1,10)*1e11,np.arange(1,10)*1e12,np.arange(1,6)*1e13])
-    #N0=np.hstack([np.arange(1,4)*1e13])
[…]

### 2023-01-06 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -13,7 +13,7 @@ import paths
 
 mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
 
-from pylab import rcParams
+#from pylab import rcParams
 from scipy import interpolate
 from astropy import units as u
 from astropy import constants as const

### 2023-01-06 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -26,8 +26,9 @@ from scipy.optimize import curve_fit
 import scipy.stats as stats
 import time
 import gc
+import matplotlib as mpl
 
-rcParams['figure.figsize'] = 12, 8
+mpl.rcParams['figure.figsize'] = 12, 8
 
 ## this is to convolve an arbitrary spectrum in (wave, spec) with velocity broadening effects.
 ## dv is in km/s (which here we're setting to c/R)

### 2023-01-06 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -404,7 +404,7 @@ def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,f,binsize=81,binsize2=400,nsk
     N0=np.hstack([np.arange(1,4)*1e13])
 
     T_gas0=np.asarray([10, 20, 50, 100, 200, 300, 1000, 2000])
-    T_gas0=np.asarray([10, 20,200])
+    T_gas0=np.asarray([10, 20,50,100])
     ntot = np.size(N0)*np.size(T_gas0)
     count = 1
     for T_gas in T_gas0:

### 2023-01-06 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -401,10 +401,10 @@ def fold_comet(v_ccf,ccf,sim_ccf,T_gas,N,binsize,idx_comets,v_comets):
 def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,f,binsize=81,binsize2=400,nskip=25,v_cutoff=50,v_comet=0.,idx_comet=0.):
     ## Define a range of column densities to use (mainly injection)
     N0=np.hstack([np.arange(1,10)*1e11,np.arange(1,10)*1e12,np.arange(1,6)*1e13])
-    N0=np.hstack([np.arange(1,4)*1e13])
+    #N0=np.hstack([np.arange(1,4)*1e13])
 
     T_gas0=np.asarray([10, 20, 50, 100, 200, 300, 1000, 2000])
-    T_gas0=np.asarray([10, 20,50,100])
+    #T_gas0=np.asarray([10, 20,50,100])
     ntot = np.size(N0)*np.size(T_gas0)
     count = 1
     for T_gas in T_gas0:

### 2023-01-07 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -400,7 +400,7 @@ def fold_comet(v_ccf,ccf,sim_ccf,T_gas,N,binsize,idx_comets,v_comets):
 ## run ccf for a range of temperatures
 def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,f,binsize=81,binsize2=400,nskip=25,v_cutoff=50,v_comet=0.,idx_comet=0.):
     ## Define a range of column densities to use (mainly injection)
-    N0=np.hstack([np.arange(1,10)*1e11,np.arange(1,10)*1e12,np.arange(1,6)*1e13])
+    N0=np.hstack([np.arange(1,10)*1e11,np.arange(1,10)*1e12,np.arange(1,5)*1e13])
     #N0=np.hstack([np.arange(1,4)*1e13])
 
     T_gas0=np.asarray([10, 20, 50, 100, 200, 300, 1000, 2000])

### 2023-01-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\newcommand{\kms}{km s$^{-1}$}
+\newcommand{\bpb}{Beta Pictoris b}
+\newcommand{\bp}{Beta Pictoris}
+
 \usepackage{color}
@@
 \hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}
+
+\usepackage[nolist,nohyperlinks]{acronym}
+\newacro{harps}[HARPS]{High Accuracy Radial Velocity Planet Searcher}
+\newacro{uves}[UVES]{Ultra-violet Visible Echelle Spectrograph}
+\newacro{feb}[FEBs]{Falling Evaporating Bodies}
 
@@
 
+% text highlighting
+\usepackage{soul}
+\sethlcolor{yellow}
+
+\usepackage[version=4]{mhchem}
 % the three lines suppress the hyperref 'link empty' warnings
@@
 
-   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards Beta Pictoris}
+   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}}
 
@@
           \and
-          A. Fitzsimmons \inst{6}
+          A. Fitzsimmons \inst{1}
           }
 
-   \institute{Institute for Astronomy (IfA), University of Vienna,
-              T\"urkenschanzstrasse 17, A-1180 Vienna\\
-              \email{wuchterl@amok.ast.univie.ac.at}
+   \institute{Leiden Observatory, Leiden University, P.O. Box 9513, 2300 RA Leiden, The Netherlands\\
+              \email{kenworthy@strw.leidenuniv.nl}
          \and
-             DCU, ...\\
+             Astrophysics Research Centre, School of Mathematics and Physics, Queen’s University Belfast, BT7 1NN Belfast, UK
         \and
-             ESO (European Southern Observatory) - Alonso de Cordova 3107, Vitacura, Santiago, Chile\\
+             Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, UK
         \and
-        Department of Astronomy, AlbaNova University Center, Stockholm University, 106 91 Stockholm, Sweden, \email{alexis@astro.su.se}\\
+        Institutionen f\"{o}r astronomi, Stockholms universitet, AlbaNova universitetscentrum, 106 91, Stockholm, Sweden
         \and
-        Paris
-        \and
-            Astrophysics Research Centre, School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, UK
-             }
+        LESIA, Observatoire de Paris, Université PSL, CNRS, 5 Place Jules Janssen, 92190 Meudon, France}
 
@@
   % {} leave it empty if necessary  
-   {Beta Pic has FEBs which are seen as variable transient absorption features towards Beta Pictoris.}
+   {Beta Pic has \ac{feb} which are seen as variable transient absorption features towards \bp{}.}
   % aims heading (mandatory)
-   {To detect cyanogen (CN) in the FEB spectrum, confirming that they are similar to comets in the Solar System.}
+   {To detect cyanogen (\ce{CN}) in the \ac{feb} spectrum, confirming that they are similar to comets in the Solar System.}
   % methods heading (mandatory)
-   {We combine the HARPS spectra from the past 20 years to make a high signal to noise ratio spectrum and look for the CN band head.
-We also combine UVES data to confirm our non-detections/detections.}
+   {We combine the \ac{harps} spectra from the past 20 years to make a high signal to noise ratio spectrum and look for the \ce{CN} band head.
+We also combine \ac{uves} data to confirm our non-detections/detections.}
   % results heading (mandatory)
-   {No CN is seen to a level of XXX ppt, indicating that there is less CN in these FEBs than Solar system comets.}
+   {No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.}
   % conclusions heading (optional), leave it empty if necessary 
-   {FEBs are not Solar System comets in composition.}
+   {\ac{feb} are not Solar System comets in composition.}
 
@@
 
-Comets and exocomets are Cool!
+%Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).
 
-Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI). HELLO WORLD!
+To the contrary of what is observed in the case of \ac{feb}, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
 
-To the contrary of what is observed in the case of FEBs, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
+Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
+%
+%The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
+%
+%For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comet approached the Sun.
+%
+%At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum, but at 0.15 au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ce{[\ion{O}{i}], \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
 
-%Spectroscopy of Solar system comets when they are very close to the Sun is rare due to observational difficulties.
-The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
-For this comets, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
-At distances greater than 0.4~au, CH, CN, C$_2$, and C$_3$ emission bands dominated the spectrum.
-However, at 0.15 au from the Sun, the only molecular emission detected was CN, while numerous atomic lines were visible ([OI], NaI, KI, CaII, CrI, MnI, FeI, NiI, CuI, VI) (\citealp{Dufay65}; \citealp{Thackeray1966}; \citealp{Preston1967}; \citealp{Slaughter1969}).
+%While the above neutral/ionic signatures in FEBs are well established, it is important to note that detection of these species in Solar system comets is rare.
+%
+\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
+%
+For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
+%
+At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum.
+%
+However, at 0.15~au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ion{[O]}{i}, \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
+%
+Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.
 
-While the above neutral/ionic signatures in FEBs are well established, it is important to note that detection of these species in Solar system comets is rare.
-Ca~II and Fe~I have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
-For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
-At distances greater than 0.4~au, CH, CN, C$_2$, and C$_3$ emission bands dominated the spectrum.
-However, at 0.15 au from the Sun, the only molecular emission detected was CN, while numerous atomic lines were visible ([OI], NaI, KI, CaII, CrI, MnI, FeI, NiI, CuI, VI) (\citealp{Dufay65}; \citealp{Thackeray1966}; \citealp{Preston1967}; \citealp{Slaughter1969}).
-Additionally, a tail of FE~I atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.
+On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines [REFs].
+%
+The high efficiency of the \ion{Na}{i} D transition makes it easily detectable, even for relatively low column density.
+%
+A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
 
-On the other hand, Na~I D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines [REFs].
-The high efficiency of the NaI D transition makes it easily detectable, even for relatively low column density.
-A notable discovery was a spectacular tail of Na~I associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
-
-These characteristics imply that Ca~II and Fe~I are predominantly locked up within cometary dust gains, and only observed when a comet is close enough to the Sun to allow their sublimation.
+These characteristics imply that \ion{Ca}{ii} and \ion{Fe}{i} are predominantly locked up within cometary dust gains, and only observed when a comet is close enough to the Sun to allow their sublimation.
+%
 This occurs at $r\leq 0.03-0.06$ au for a dust grain with Bond albedo $\sim0.01$ and a sublimation temperature of $T\simeq 1600$K, depending on the thermal model assumed.
-On the other hand, the origin of the NaI tail observed in numerous comets at larger distances from the Sun is still not very well understood [Cremonese+2002].
-Release from dust grains as well as molecular processes have been suggested as possible sources of NaI in the coma and tail of comets annd explain its presence at large solar distances \citep{Cremonese1997}.
+%
+On the other hand, the origin of the \ion{Na}{i} tail observed in numerous comets at larger distances from the Sun is still not very well understood \citep{Cremonese02}.
+%
+Release from dust grains as well as molecular processes have been suggested as possible sources of \ion{Na}{i} in the coma and tail of comets annd explain its presence at large solar distances \citep{Cremonese1997}.
 %Na appears to be weakly bound to the dust grains and released at larger solar distances.
 
-For the majority of Solar system comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines [{\it e.g.} \citep{hyland2019}].
+For the majority of Solar system comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines \citep[e.g.
+][]{hyland2019}.
+%
 Most of the neutral and ionic molecular emission results from resonance fluorescence with solar photons.
-Some species, such as H$_2$O$^+$ and  CO$^+$ result from ionization of parent molecules (i.e.
+Some species, such as \ce{H2O+} and \ce{CO+} result from ionization of parent molecules (i.e.
 molecules released directly by the sublimation of nuclear ices), all other molecules observed are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma.
-Another process also observed in optical spectrum of comets is prompt atomic emission  ([OI], [CI], and [NI]).
+%
+Another process also observed in optical spectrum of comets is prompt atomic emission  ([\ion{O}{i}], [\ion{C}{i}], and [\ion{N}{i}]).
+%
 Those forbidden transitions are the result of atoms produced in an excited state by the photodissociation of parent molecules in the coma.
-%Only the Na~I emission is currently thought to be generated by release mainly from dust grains ejected by the comet.
 
-Of all cometary gas emission, the highest signal to noise normally occurs with the CN (0-0) band at $\lambda\simeq 3880$\AA.
-It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun {\it e.g.}  \cite{Fitzsimmons1996}.
-The relative abundance in the coma of most comets of CN/OH$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1 au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae.
-Historically, the CN was believed to be created from photodissociation of HCN, which is present in abundances of the order of 1\% relative to water in cometary ices.
-High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner2014}.
-However, it is now known that in many comets a substantial fraction of CN is released from sub-micron dust grains in the inner coma of comets {\it e.g.} \cite{Fray2005}.
+Of all cometary gas emission, the highest signal to noise normally occurs with the \ce{CN} (0-0) band at $\lambda\simeq 3880$\AA.
+%
+It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun \citep[e.g.
+][]{Fitzsimmons1996}.
+%
+The relative abundance in the coma of most comets of \ce{CN/OH}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae.
+%
+Historically, the \ce{CN} was believed to be created from photodissociation of \ce{HCN}, which is present in abundances of the order of 1\% relative to water in cometary ices.
+%
+High-spatial resolution sub-mm mapping of \ce{HCN} distributions supports a nuclear source in some comets \citep{Cordiner2014}.
+%
+However, it is now known that in many comets a substantial fraction of \ce{CN} is released from sub-micron dust grains in the inner coma of comets \citep[e.g. ][]{Fray2005}.
 
-The C$_2$ (0-0) band at $\lambda\simeq 5160$\AA \ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
-The OH (0-0) band at $\lambda\simeq 3080$ \AA \ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
-Strong CO$^+$ emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) [REFS]).
-However this is normally significantly weaker than the observed CN emission, with only ???
-comets
+The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA \ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
+%
+The \ce{OH} (0-0) band at $\lambda\simeq 3080$ \AA \ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
+%
+Strong \ce{CO+} emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) \hl{REFS}).
+%
+However this is normally significantly weaker than the observed \ce{CN} emission, with only \hl{number of comets} comets.
 
-Given the ubiquitous signature of CN emission in Solar system comets, we have embarked on an archival search for this species in the FEBs around Beta Pic.
-Detection of this species would provide a solid link between cometary bodies in our Solar system and the Beta Pic system.
+Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the \ac{feb} around Beta Pic.
+%
+Detection of this species would provide a solid link between cometary bodies in our Solar system and the \bp{} system.
 
 \section{Data description and analysis}
-For the study in this paper, we use all the available data from the High Accuracy Radial Velocity Planet Searcher (HARPS) and the ESO 3.6m telescope in Chile.
-In addition, we complement this with observations with the Ultra-violet Visible Echelle Spectrograph (UVES) at the Very Large Telescope in Chile.
+
+For the study in this paper, we use all the available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
+%
+In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
 
 \subsection{HARPS observations}
-We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and March 2020.
+
+We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and March 2020.
+%
 Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years.
+%
 Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
+%
 For this analysis we used the E2DS files downloaded directly from the ESO archive.
@@
 \subsection{UVES observations}
-To supplement the HARPS observations, we use 160 epochs of UVES observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
+
+To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
 %
@@
 %
-We used the standard 437+760 mode of UVES, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
+We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
 %
@@
 %
-For the remainder of the paper, we will only focus on the data from the blue arm of UVES, as this covers the strong CN band-head seen in Solar system comets.
+For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} band-head seen in Solar system comets.
 %
@@
 
-The data were reduced using the ESO UVES pipeline version 5.7.0 through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+The data were reduced using the ESO \ac{uves} pipeline version 5.7.0 through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
 
@@
 The ratio was then binned, removing outliers, and a polynomial was fit to the data.
-For UVES we used a Nth degree polynomial, while for HARPS we used a 2nd degree polynomial.
+%
+For \ac{uves} we used a Nth degree polynomial, while for \ac{harps} we used a 2nd degree polynomial.
+%
 This polynomial was then divided from the spectrum under consideration.
@@
 The blaze-corrected spectra taken within a night were averaged together [Should we use a weighted average?].
-We note that for HARPS, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.
+%
+We note that for \ac{harps}, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.
 
 \section{Searches for cometary species}
-After the initial data analysis, we proceed to with our search for lines from CN.
-Although we are interested in lines from the exocomets, we first coadd the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar CN absorption.
-These coadded spectra for HARPS and UVES are shown in Fig.~\ref{fig:coadd_restframe}.
-No obvious feature jumps out, and we can rule out circumstellar CN down to NNNN.
 
-Since the exocomets have a clear radial velocity with respect to $\beta$ Pic, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the Ca II H \& K lines, as well as the MM epochs with the weakest cometary features.
-The selection was done by .......
+After the initial data analysis, we proceed to with our search for lines from \ce{CN}.
+%
+Although we are interested in lines from the exocomets, we first coadd the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
+%
+These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.
+%
+No obvious feature jumps out, and we can rule out circumstellar \ce{CN} down to \hl{NNNN}.
+
+Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H \& K lines, as well as the MM epochs with the weakest cometary features.
+%
+The selection was done by
+
 The spectra with only weak exocometary features were co-averaged in the stellar restframe in order to create a stellar master spectrum.
@@
 The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
-The combined exocomet aligned spectra for both the CA H\&K lines and CN band are shown in Fig.~\ref{fig:coadd_exocomets}.
+The combined exocomet aligned spectra for both the CA H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}.
 As can be seen no signal is visibly present.
@@
 
-\subsection{CN}
+\subsection{\ce{CN}}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/HARPS_CN_grid.pdf}
+        \caption{Confidence intervals for the signal to noise of \ce{CN} spectra using \ac{harps} spectra of \bp{}.}
+        \label{fig:HARPS_CN_grid}
+        \script{plot_HARPS_CN_grid.py}
+    \end{centering}
+\end{figure}
 

### 2023-01-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+The formation and evolution of planets and their attendant moons is thought to occur in the first few ten million years of the stellar system \hl{REF}.
+%
+Comets deliver volatiles across menay different distances within the Solar system, from the outermost reaches of the Oort cloud in to the terrestrial planets.
+%
+It is therefore important to understand the distribution, nature and chemical composition of exocomets in other planet forming systems.
+
+One of the closest young systems is Beta Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
+
+Beta Pictoris is a young, early type star whose stellar chromosphreic lines show rotational broadening of 200 km/s \hl{REF}.
+%
+Additional, much narrower absorption features are seen in the Calcium H and K lines.
+%
+These features appear and disappear on several hour long timescales, and show a different range of morphologies \hl{[REF]}.
+%
+Intensive spectroscopic monitoring over several hours show changes of radial velocity of these components consistent with elliptical orbits.
+%
+The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of metals that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component \hl{[REF REF]}.
+
+From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the Kepler satellite [REF] and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19}.
+%
+Observations of Beta Pictoris in subsequent TESS sector revealed over two dozen transits whost depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
+
 %Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).
@@
 %At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum, but at 0.15 au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ce{[\ion{O}{i}], \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
-
-%While the above neutral/ionic signatures in FEBs are well established, it is important to note that detection of these species in Solar system comets is rare.
-%
-\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
+%%\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
 %
@@
 
-On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines [REFs].
+On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines \hl{REFs}.
 %

### 2023-02-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-For the study in this paper, we use all the available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
+For the study in this paper, we use all the publicly available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
 %
-In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
+In addition, we complement this with observations with the \ac{UVES} at the Very Large Telescope in Chile.
 
@@
 
-We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and March 2020.
+We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and \textcolor{red}{March 2020}.
 %
@@
 %
-Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
+Similarly, the number of observations per epoch spans a wide range, between \textcolor{red}{1 and 356} exposures, while the exposure times vary between \textcolor{red}{12 and 900} seconds.
+This results in a SNR range per exposure between \textcolor{red}{NNNN and MMMM}, and a nightly SNR between \textcolor{red}{NNNN and MMMM}.
 %
-For this analysis we used the E2DS files downloaded directly from the ESO archive.
+To avoid potential edge effects from order merging,  we used the E2DS files downloaded directly from the ESO archive for our analysis.
+
+\textcolor{red}{Q: Do we want to put an observing log in the appendix?}
 
@@
 %
-The details for these observations are explained in more detail in \cite{vansluijs2019}, and summarised here.
+The details for these observations are given in \cite{vansluijs2019}, and summarised here.
 %
@@
 %
-For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} band-head seen in Solar system comets.
+For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
 %
@@
 
-The data were reduced using the ESO \ac{uves} pipeline version 5.7.0 through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+The data were reduced using the ESO \ac{UVES} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+The flat-field was applied on a pixel-by-pixel basis.\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
+Optimal extraction was performed, using an empirical profile}
 
 \subsection{Initial data processing}
-The data from both instruments was processed in similar ways.
+Starting from the 2d spectra, the data from both instruments was processed in similar ways.
 %
-For both datasets, we used the 2d-unmerged echelle spectra, and we treated each order separately.
+Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the Ca II H \& K lines, which are used to identify the exocomets.
 %
-All the spectra were transformed into the stellar rest-frame using linear interpolation.
+All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.
 
-The number of observations varies from night to night, from a few spectra to over a hundred.
+The number of observations varies from night to night, from a \textcolor{red}{single} spectrum to over \textcolor{red}{three hundred} spectra.
 %
-An average of all the spectra in one night was made for all the nights of observations.
+An average of all the spectra in one night was made for each of the nights of observations, after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit losses, atmospheric absorption etc.), as outlined below.
+Note that after this correction, the HARPS data still have the overall instrumental blaze-profile, while the 2d-spectra from UVES were already corrected for this.
 
-The blaze function dominates the flux profile of the spectra.
+\subsubsection{Effective Blaze function correction}
+
+One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function (the night of \textcolor{red}{DATE} for HARPS and \textcolor{red}{DATE} for UVES).
+The individual spectra in this night were averaged together to further boost the signal-to-noise ratio.
+Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
+This ratio spectrum was subsequently binned using a bin-width of \textcolor{red}{101} pixels using a robust algorithm to remove outliers within each bin.
+This binned ratio was than fit using a \textcolor{red}{second} order polynomial.
+The original spectrum was finally divided by this polynomial to correct for the changes.
+
+%his spectrum was binned in the spectral direction to remove both narrow absorption lines and the rotationally broadened stellar chromospheric lines, but preserve the shape of the blaze function.
 %
-One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function: this spectrum was binned in the spectral direction to remove both narrow absorption lines and the rotationally broadened stellar chromospheric lines, but preserve the shape of the blaze function.
-%
-A low order second or third order polynomial was fit to each echelle order, and this fit spectrum served as a blaze function estimate.
 
-For all the spectra in a given night:
- - Divide the spectrum by the reference spectrum, which hs the fit of the low order polynomial to the best night spectrum.
- - Combine all these spectrum within a single night all together, to form the final night spectrum (this still has the BLAZE function in it...)
-
+\subsubsection{Combining the spectra}
+After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits. This could potentially re
  For all the night spectra:

### 2023-02-06 src/scripts/plot_two_CN_temps.py
[showyourwork] overleaf sync

@@ -1,0 +1,25 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+
+
+
+
+wlen=np.load(paths.data/'CN/CN_wavelengths.npy')
+
+t1=np.load(paths.data/'CN/CN_0100K.npy')
+t2=np.load(paths.data/'CN/CN_1000K.npy')
+
+fig, ax = plt.subplots(1,1,figsize=(8,6))
+ax.set_yscale("log")
+
+ax.set_xlim(382,386)
+ax.set_ylim(1e-31,1e-15)
+
+ax.set_xlabel('Wavelength [$nm$]',fontsize=16)
+ax.set_ylabel('Transmission',fontsize=16)
+
+ax.plot(wlen/10,t1)
+ax.plot(wlen/10,t2)
+plt.show()
+plt.savefig(paths.figures/'two_CN_temps.pdf', bbox_inches='tight')

### 2023-02-06 src/scripts/plot_two_CN_temps.py
[showyourwork] overleaf sync

@@ -3,8 +3,6 @@ import numpy as np
 import paths
 
 
-
-
 wlen=np.load(paths.data/'CN/CN_wavelengths.npy')
 
 t1=np.load(paths.data/'CN/CN_0100K.npy')
@@ -21,5 +19,5 @@ ax.set_ylabel('Transmission',fontsize=16)
 
 ax.plot(wlen/10,t1)
 ax.plot(wlen/10,t2)
-plt.show()
-plt.savefig(paths.figures/'two_CN_temps.pdf', bbox_inches='tight')
+#plt.show()
+plt.savefig(paths.figures / 'two_CN_temps.pdf', bbox_inches='tight')

### 2023-02-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 [Do we want to do a simple CCF to see if we can combine the individual lines?]
+
+We have theoretical specrtra of CN shown in Figure~\ref{fig:CN_theory}.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
+        \caption{Theoretical cross section spectra of CN for 100K and 1000K.}
+        \label{fig:CN_theory}
+        \script{plot_two_CN_temps.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/ccf.pdf}
+        \caption{Cross correlation for different number densities of CN.}
+        \label{fig:ccf}
+        \script{plot_ccf.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
+        \caption{Cross correlation for different number densities of CN averaged over many spectra.}
+        \label{fig:ccf}
+        \script{plot_ccf_mean.py}
+    \end{centering}
+\end{figure}
 

### 2024-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 %
-In addition, we complement this with observations with the \ac{UVES} at the Very Large Telescope in Chile.
+In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
 
@@
 %
-In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm.
+In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA to $\sim 5000$ \AA in the blue arm, and $\sim 5650$ \AA to $\sim 9560$ \AA in the red arm.
 %
@@
 
-The data were reduced using the ESO \ac{UVES} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+The data were reduced using the ESO \ac{uves} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
 The flat-field was applied on a pixel-by-pixel basis.\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
@@
 
-We have theoretical specrtra of CN shown in Figure~\ref{fig:CN_theory}.
+We have theoretical spectra of CN shown in Figure~\ref{fig:CN_theory}.
 
@@
         \caption{Cross correlation for different number densities of CN averaged over many spectra.}
-        \label{fig:ccf}
+        \label{fig:ccf_mean}
         \script{plot_ccf_mean.py}

### 2024-07-17 src/scripts/analyse_HARPS_spectra.py
comments added

@@ -11,6 +11,8 @@ from astropy.io import fits
 import matplotlib as mpl
 import paths
 
+mpl.use('macosx')
+mpl.rcParams['figure.figsize'] = 12, 8
 mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
 
 #from pylab import rcParams
@@ -26,11 +28,8 @@ from scipy.optimize import curve_fit
 import scipy.stats as stats
 import time
 import gc
-import matplotlib as mpl
 
-mpl.rcParams['figure.figsize'] = 12, 8
-
-## this is to convolve an arbitrary spectrum in (wave, spec) with velocity broadening effects.
+## this is to convolve an arbitrary spectrum in (wave, spec) with velocity broadening effects. 
 ## dv is in km/s (which here we're setting to c/R)
 def wavegrid(lmin,lmax,R):
     '''lmin is the minimum wavelength, lmax is the maximum wavelength you want, R is the spectral resolution
@@ -60,8 +59,8 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
 
     ## generate a Gaussian kernel with the FWHM at the instrumental resolution & convolve model
     ## *** TBD: Allow other line broadening (e.g. based on Ca lines or even for different resolutions) ***
-    FWHM_kernel=3e5/1.10e5
-    x_kernel=np.arange(-25.,25.001,(3e5/res_interp))
+    print(FWHM_kernel)
+    x_kernel=np.arange(-30.,30.001,(3e5/res_interp))
     kernel=np.exp( - ((x_kernel)**2)/2./(FWHM_kernel/2.35)**2)
     kernel=kernel/np.sum(kernel)
     mdl_conv=np.convolve(mdl,kernel,mode='same')
@@ -70,21 +69,48 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
     ## set up interpolation object for the model to use in the CCF code
     imdl_conv=interp1d(w_mdl[idx],mdl_conv[idx],kind='linear',bounds_error=False,fill_value=1.)
 
-    
     return w,prof,imdl_conv
 
 
 
 ##Read in data
 def read_data(order=[0,1,2,3,4,5,6,7]):
+    vsys=20.    #Systemic velocity of beta Pic
     nspec = fits.getdata(paths.data/'2d_nspec.fits')
[…]

### 2024-07-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \textcolor{red}{Q: Do we want to put an observing log in the appendix?}
-
+\textcolor{red}{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
 \subsection{UVES observations}
@@
 %
-In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA to $\sim 5000$ \AA in the blue arm, and $\sim 5650$ \AA to $\sim 9560$ \AA in the red arm.
+In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA{} to $\sim 5000$ \AA{} in the blue arm, and $\sim 5650$ \AA{} to $\sim 9560$ \AA{} in the red arm.
 %
@@
 %
-Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the Ca II H \& K lines, which are used to identify the exocomets.
+Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the \ion{Ca}{ii} H \& K lines, which are used to identify the exocomets.
 %
@@
 \subsubsection{Combining the spectra}
-After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits. This could potentially re
- For all the night spectra:
+After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
 
- We median combine all the nights together.
+For the spectra within a given night:
 
- Bin the spectrum and clip it, interpolate using a cubic spline.
+\begin{itemize}
+\item We median combine all the nights together.
 
- Divide this interpolated cubic spline into each of the nightly spectra.
+\item Bin the spectrum and clip it, interpolate using a cubic spline.
 
-THis removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.
+\item Divide this interpolated cubic spline into each of the nightly spectra.
+
+\end{itemize}
+
+This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.
 
@@
 
-\subsection{Other Species? CO$^+$, C$_2$?}
+%\subsection{Other Species? CO$^+$, C$_2$?}
 

### 2024-07-17 src/scripts/analyse_HARPS_spectra.py
[showyourwork] overleaf sync

@@ -416,7 +416,7 @@ def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,pixels,f,binsize=81,binsize2=
                plt.figure()
                plt.plot(v_ccf,ccf[-1,3,:])
                plt.plot(v_ccf,sim_ccf[-1,3,:])
-               plt.savefig("plots/orig_ccf_{0:04d}_{1:.2e}_{2:}.png".format(T_gas,N,fappend))
+               plt.savefig(path.figures/"orig_ccf_{0:04d}_{1:.2e}_{2:}.png".format(T_gas,N,fappend))
                plt.close('all')
 
             # align everything up in the comet rest frame
@@ -437,12 +437,12 @@ def run_ccf_ord_multi_temp(wlens,data_for_ccf,spec,pixels,f,binsize=81,binsize2=
                plt.figure()
                plt.plot(v_phase,phase[-1,3,:])
                plt.plot(v_phase,sim_phase[-1,3,:])
-               plt.savefig("plots/phase_{0:04d}_{1:.2e}_{2:.1f}_{3:}.png".format(T_gas,N,broadening,fappend))
+               plt.savefig(path.figures/"phase_{0:04d}_{1:.2e}_{2:.1f}_{3:}.png".format(T_gas,N,broadening,fappend))
                plt.close('all')
                plt.figure()
                plt.plot(v_ccf,ccf[-1,3,:])
                plt.plot(v_ccf,sim_ccf[-1,3,:])
-               plt.savefig("plots/ccf_{0:04d}_{1:.2e}_{2:.1f}_{3:}.png".format(T_gas,N,broadening,fappend))
+               plt.savefig(path.figures/"ccf_{0:04d}_{1:.2e}_{2:.1f}_{3:}.png".format(T_gas,N,broadening,fappend))
                plt.close('all')
                
                fit_cube[i,j,k,:,:]=fit.copy()
@@ -537,7 +537,7 @@ for ord in range(6):
 # CHECK POINT to see that this looks normal. REMOVE in final version    
 data_for_ccf=spec_cor[:,0:6,:]
 hdu=fits.PrimaryHDU(data_for_ccf)
-hdu.writeto('tmp.fits',overwrite=True)
+hdu.writeto(paths.data/'tmp.fits',overwrite=True)
 
 # Do the analysis for the strongest comets selected using find_comets()
[…]

### 2024-07-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.
+This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the slit aperture.
 
@@
 %
-Although we are interested in lines from the exocomets, we first coadd the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
+Although we are interested in lines from the exocomets, we first co-add the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
 %
@@
 %
-The selection was done by
-
-The spectra with only weak exocometary features were co-averaged in the stellar restframe in order to create a stellar master spectrum.
+The spectra with only weak exocometary features were co-averaged in the stellar rest frame in order to create a stellar master spectrum.
 This master-spectrum was divided out of all the remaining spectra in order to create relative spectra.
+%
 The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
-The combined exocomet aligned spectra for both the CA H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}.
-As can be seen no signal is visibly present.
+%
+The combined exocomet aligned spectra for both the \ce{Ca} H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present.
+%
 [Do we need to add a correction to account for any radiation pressure, if so, is there a way to estimate that?]
@@
         \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
-        \caption{Theoretical cross section spectra of CN for 100K and 1000K.}
+        \caption{Model spectrum for CN.}
         \label{fig:CN_theory}
@@
 %
-      Part of this work was supported by the German
-      \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project
-      number Ts~17/2--1.
+Part of this work was supported by the German \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project number Ts~17/2--1.
 %
@@
 %      
-An online repository with materials used in this work is available at \url{https://github.com/sebastian-zieba/betaPic_comet}
+An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/}
 \end{acknowledgements}

### 2024-07-18 src/scripts/analyse_HARPS_spectra.py

@@ -113,61 +113,6 @@ def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=4):
 
 
 
-## Estimate blaze
-def simple_blaze(wlen,master_blaze,nskip,nbins,binsize):
-    ww0=wlen[nskip:nskip+nbins*binsize].reshape(nbins,binsize).copy()
-    co=master_blaze[nskip:nskip+nbins*binsize].reshape(nbins,binsize).copy()
-
-    mf=np.nanmean(co,axis=1)
-    ww=np.nanmean(ww0,axis=1)
-
-    for it in range(nbins):
-        f_tmp=co[it,:]
-        l=np.polyfit(ww0[it,:],co[it,:]-mf[it],1)
-        res=co[it,:]-mf[it] - np.polyval(l,ww0[it,:])
-        sig=np.median(np.abs(res-np.median(res)))
-
-        idx=np.abs(res/sig)>4.
-        if np.sum(idx)>0:
-            f_tmp[idx]=np.nan
-        co[it,:]=f_tmp.copy()
-
-    mf=np.nanmean(co,axis=1)
-    ww=np.nanmean(ww0,axis=1)
-
-    flux_int=interpolate.interp1d(ww,mf,kind='cubic',fill_value='extrapolate',bounds_error=False)
-    interp_flux = flux_int(wlen)
-
-    return interp_flux
-
-
-
-## Higher order blaze variation corrections
-def blaze_var_cor(wlen, cor,nskip,nbins,binsize,n_frm,poly_ord):
-    for frm in range(n_frm):
-        ww0=wlen[nskip:nskip+nbins*binsize].reshape(nbins,binsize).copy()
-        co=cor[frm,nskip:nskip+nbins*binsize].reshape(nbins,binsize).copy()
-        mf=np.nanmean(co,axis=1)
-        ww=np.nanmean(ww0,axis=1)
-
-        for it in range(nbins):
-            f_tmp=co[it,:]
-            res=co[it,:]-mf[it]
-            sig=np.median(np.abs(res-np.median(res)))
-            idx=np.abs(res/sig)>4.
-            if np.sum(idx)>0:
-                f_tmp[idx]=np.nan
-            co[it,:]=f_tmp.copy()
-
-        mf=np.nanmean(co,axis=1)
-        ww=np.nanmean(ww0,axis=1)
-
-        l=np.polyfit(ww,mf,poly_ord)
-        cor[frm,:]=cor[frm,:]/np.polyval(l,wlen)
-
-    return cor
[…]

### 2024-07-18 src/scripts/plot_FEBs.py
added CN_ACF and FEB plots

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+from astropy.io import fits
+import numpy as np
+import paths
+
+vgrid=fits.getdata(paths.data/'FEB_vgrid.fits')
+orig_spec=fits.getdata(paths.data/'FEB_spec_orig.fits')
+FEB_spec=fits.getdata(paths.data/'FEB_spec.fits')
+FEB_idx=fits.getdata(paths.data/'FEB_idx.fits')
+NO_FEB_idx=fits.getdata(paths.data/'NO_FEB_idx.fits')
+FEB_depths=fits.getdata(paths.data/'FEB_depths.fits')
+FEB_vel=fits.getdata(paths.data/'FEB_velocities.fits')
+
+
+spec_FEB=FEB_spec[:,FEB_idx]
+spec_NO_FEB=FEB_spec[:,NO_FEB_idx]
+
+
+
+v_idx=(np.abs(vgrid)>8)*(np.abs(vgrid)<=200)
+
+f,ax=plt.subplots(2,1,sharex=True)
+ax[0].plot(vgrid,(orig_spec[:,FEB_idx])[:,1])
+ax[0].plot(vgrid,np.mean(orig_spec[:,NO_FEB_idx],axis=1))
+ax[1].plot(vgrid[v_idx],(spec_FEB[v_idx,:])[:,1])
+ax[1].vlines((FEB_vel[FEB_idx])[1],0,2)
+ax[1].plot(vgrid[v_idx],np.mean(spec_NO_FEB[v_idx,:],axis=1))
+ax[0].set_xlim(-200,200)
+ax[0].set_ylim(0,1.1)
+plt.show()
+
+
+f,ax=plt.subplots()
+ax.plot(FEB_vel,FEB_depths,'k.')
+plt.show()

### 2024-09-06 src/scripts/analyse_HARPS_spectra.py
six panel plots

@@ -1,4 +1,4 @@
-# -*- coding: utf-8 -*-
+#-*- coding: utf-8 -*-
 """
 Created on Tue Jul 26 15:54:53 2022
 
@@ -11,10 +11,6 @@ from astropy.io import fits
 import matplotlib as mpl
 import paths
 
-mpl.use('macosx')
-mpl.rcParams['figure.figsize'] = 12, 8
-mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
-
 #from pylab import rcParams
 from scipy import interpolate
 from astropy import units as u
@@ -23,11 +19,12 @@ from astropy.stats import sigma_clip
 from astropy.stats.sigma_clipping import sigma_clipped_stats
 from scipy.interpolate import interp1d
 from numpy.polynomial import Polynomial as P
-from scipy import signal
 from scipy.optimize import curve_fit
 import scipy.stats as stats
 import time
 import gc
+
+
 
 ## this is to convolve an arbitrary spectrum in (wave, spec) with velocity broadening effects. 
 ## dv is in km/s (which here we're setting to c/R)
@@ -58,9 +55,8 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
     mdl=prof_i(w_mdl)
 
     ## generate a Gaussian kernel with the FWHM at the instrumental resolution & convolve model
-    ## *** TBD: Allow other line broadening (e.g. based on Ca lines or even for different resolutions) ***
     print(FWHM_kernel)
-    x_kernel=np.arange(-30.,30.001,(3e5/res_interp))
+    x_kernel=np.arange(-90.,90.001,(3e5/res_interp))
     kernel=np.exp( - ((x_kernel)**2)/2./(FWHM_kernel/2.35)**2)
     kernel=kernel/np.sum(kernel)
     mdl_conv=np.convolve(mdl,kernel,mode='same')
@@ -87,23 +83,98 @@ def read_data(order=[0,1,2,3,4,5,6,7]):
 ## Estimate residual blaze
 def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=4):
     # order start and order end (the pixel point where there is flux in the order)
-    # for the first six orders
-    o_start=np.array([ 225,  15,  26,  26,  26,  26])
[…]

### 2024-09-06 src/scripts/make_CN_ACF_plot.py

@@ -41,7 +41,7 @@ order_end  =4060
 dv=np.linspace(-300,300,601)
 col=['r','g','b','c','y','m','k','orange']
 T_gas0=np.asarray([10, 20, 50, 100, 200, 300, 1000, 2000])
-f,ax=plt.subplots(1,2)
+f,ax=plt.subplots(1,2,sharex=True)
 
 ##: left panel: un-normalised ACF, right panel: normalised ACF
 for i,T in enumerate(T_gas0):
@@ -52,5 +52,6 @@ for i,T in enumerate(T_gas0):
     ax[1].plot(dv,ccf[0,:]/np.max(ccf[0,:]),col[i],label='T={0:}K'.format(T))
 ax[0].legend()
 f.tight_layout()
-f.savefig(paths.figures/'ccf_self.png')
+f.savefig(paths.figures/'ccf_self.png') 
 
+plt.show()

### 2024-09-06 src/scripts/plot_FEBs.py

@@ -2,6 +2,8 @@ import matplotlib.pyplot as plt
 from astropy.io import fits
 import numpy as np
 import paths
+import matplotlib as mpl
+mpl.use('macosx')
 
 vgrid=fits.getdata(paths.data/'FEB_vgrid.fits')
 orig_spec=fits.getdata(paths.data/'FEB_spec_orig.fits')

### 2024-09-06 src/scripts/plot_HARPS_CN_grid.py

@@ -8,7 +8,190 @@ Created on Tue Dec 20 11:29:29 2022
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
+from astropy.io import fits
+import matplotlib as mpl
 
+mpl.use('macosx')
+
+
+T0=fits.getdata(paths.data/'T_gas.fits')
+N0=fits.getdata(paths.data/'Nf.fits')
+w=fits.getdata(paths.data/'broadening.fits')
+
+midpts_T=(T0[1:]+T0[:-1])/2.
+x=np.arange(midpts_T.shape[0])+1
+#T=10**np.polyval(np.polyfit(x,np.log10(midpts_T),1),np.arange(T0.shape[0]+1))
+T=np.hstack((0.,midpts_T,1.5*T0[-1]))
+
+midpts_N=(N0[1:]+N0[:-1])/2.
+x=np.arange(midpts_N.shape[0])+1
+N=10**np.polyval(np.polyfit(x,np.log10(midpts_N),1),np.arange(N0.shape[0]+1))
+
+
+
+fit=fits.getdata(paths.data/'fit_cube_comet.fits')
+sig0=fits.getdata(paths.data/'fit_err_cube_comet.fits')
+
+mean=fit[:,:,:,-1,:]
+sig=sig0[:,:,:,-1,:]#np.std(fit[:,:,:,:-1,:],axis=-2)/np.sqrt(fit.shape[-2])
+SN=mean/sig
+print(SN.shape,T.shape,N.shape,w.shape)
+
+f,ax=plt.subplots(1,6,figsize=(16,6),gridspec_kw={"width_ratios":[1,1,1,1,1,0.1]})
+vmin=np.min(SN[:,:,:,0])
+vmax=np.max(SN[:,:,:,0])
+for i in range(5):
+    im=ax[i].pcolormesh(N,T,SN[:,:,i,0],vmin=vmin,vmax=vmax,shading='flat')
+    ax[i].set_xscale('log')
+f.colorbar(im,cax=ax[-1])
+
+ax[0].set_ylabel('T [K]',fontsize=12)
+for i in range(5):
+    ax[i].set_xlabel('N$\cdot$f [cm$^{-2}$]',fontsize=12)
+    
+f.tight_layout()
+
+
+
+
+##run for simulation
+
[…]

### 2024-09-06 src/scripts/plot_ccf_mean.py

@@ -1,24 +1,94 @@
 import matplotlib.pyplot as plt
 import numpy as np
 import paths
-from astropy.table import Table
+from astropy.io import fits
 
-t=Table.read(paths.data/'ccf_data1_mean.ecsv',format='ascii.ecsv')
+N0=fits.getdata(paths.data/"Nf.fits")
+T_gas0=fits.getdata(paths.data/"T_gas.fits")
+broadening0=fits.getdata(paths.data/"broadening.fits")
+FEB_idx=fits.getdata(paths.data/"FEB_idx.fits")
+
+
+##Find indices for 30K and 2000K
+idx1=np.nonzero(T_gas0 == 30)
+idx2=np.nonzero(T_gas0 == 2000)
+
+##Find index for N = 10^12 cm^-2
+idxN11=np.nonzero(N0 == 1e11)
+idxN13=np.nonzero(N0 == 1e13)
+idxN15=np.nonzero(N0 == 1e15)
+
+##Index for v_broad=10km/s
+idxW=np.nonzero(broadening0 == 10.)
+print(idx1,idxN11,idxW)
+
+v_ccf=fits.getdata(paths.data/"v_phasefold.fits")
+ccf=fits.getdata(paths.data/"phase_cube.fits")
+inj_ccf=fits.getdata(paths.data/"sim_phase_cube.fits")
+ccf=ccf[:,:,:,FEB_idx,:]-np.median(ccf,axis=-1)[:,:,:,FEB_idx,np.newaxis]
+inj_ccf=inj_ccf[:,:,:,FEB_idx,:]-np.median(inj_ccf,axis=-1)[:,:,:,FEB_idx,np.newaxis]
+    
+
+
+
+idx_outside=(np.abs(v_ccf)>25)*(np.abs(v_ccf<50))
 
 fig, ax = plt.subplots(1,1,figsize=(8,6))
-
-ax.set_xlim(-50,50)
-ax.set_ylim(0,30)
+ax.set_xlim(-150,150)
 
 ax.set_xlabel('Velocity [$km/s$]',fontsize=16)
 ax.set_ylabel('CCF [a.u.]',fontsize=16)
 
-ax.plot(t['vel'],t['N11'],label="N=$10^{11}$")
-ax.plot(t['vel'],t['N12'],label="N=$10^{12}$")
[…]

### 2024-09-06 src/tex/ms.tex
[showyourwork] overleaf sync
ccf plots and cleanup

@@
-%                                                                 aa.dem
-% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
-% demonstration file
-%                                                       (c) EDP Sciences
-%-----------------------------------------------------------------------
-%
-%\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[rnote]{aa} % for the research notes
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-% according to the author-year natbib style
 \documentclass{aa}  
@@
 %
-Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years.
+Although these observations cover a large baseline, the time between visits varies between 1 day and $\sim$2.2 years.
 %
@@
 \textcolor{red}{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
+
 \subsection{UVES observations}
@@
 The data were reduced using the ESO \ac{uves} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
-The flat-field was applied on a pixel-by-pixel basis.\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
+The flat-field was applied on a pixel-by-pixel basis.
+\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
 Optimal extraction was performed, using an empirical profile}
@@
 %
-Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the \ion{Ca}{ii} H \& K lines, which are used to identify the exocomets.
+Each order was treated separately, with the main focus on orders \textcolor{red}{4 and 8} for HARPS and \textcolor{red}{4, and 7} for UVES as those orders contain the main CN bandhead as well as the \ion{Ca}{ii} H line, which are used to identify the exocomets.
 %
 All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.
+For UVES, the \ce{Fe} \textcolor{red}{NNNN~$\AA$} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
+To measure these, a Gaussian was fit to the line, and the velocity offset from the restframe position determined.
 
-The number of observations varies from night to night, from a \textcolor{red}{single} spectrum to over \textcolor{red}{three hundred} spectra.
 %
-An average of all the spectra in one night was made for each of the nights of observations, after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit losses, atmospheric absorption etc.), as outlined below.
+After all the spectra were all transformed into the stellar restframe, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
+This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption etc.), as outlined below.
 Note that after this correction, the HARPS data still have the overall instrumental blaze-profile, while the 2d-spectra from UVES were already corrected for this.
 
-\subsubsection{Effective Blaze function correction}
+\subsubsection{Effective Blaze function correction}\label{sect:blaze}
 
@@
 
-%his spectrum was binned in the spectral direction to remove both narrow absorption lines and the rotationally broadened stellar chromospheric lines, but preserve the shape of the blaze function.
+Note that for HARPS, the change of fiber in \textcolor{red}{June 2015 (JD$\sim$2457180)} resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.
+
+\subsubsection{Combining the spectra and flattening them}\label{sect:comb}
+After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders \textcolor{red}{NN and MM, and OO and PP} for HARPS and UVES respectively.
+
+%For the spectra within a given night:
 %
+%\begin{itemize}
+%\item We median combine all the nights together.%
+%
+%\item Bin the spectrum and clip it, interpolate using a cubic spline.
+%
+%\item Divide this interpolated cubic spline into each of the nightly spectra.
+%
+%\end{itemize}
 
-\subsubsection{Combining the spectra}
-After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
+\subsubsection{Removing the stellar spectrum}\label{sect:starcor}
+The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and, for HARPS, shape of the blaze profile, are still present and need to be removed.
 
-For the spectra within a given night:
+For both HARPS and UVES we first perform a second iteration of blaze corrections using a  stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see \textcolor{red}{Sect.~\ref{sect:FEBident}}.
+For HARPS this is done separately pre- and post-fiber change.
+The correction is done similar to Sect.~\ref{sect:blaze}, however for both UVES and HARPS a \textcolor{red}{4th order} polynomial was used.
 
-\begin{itemize}
-\item We median combine all the nights together.
+After this post-processing the overall (residual) blaze profile and stellar spectrum still need to be removed.
+Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in e.g., the \ce{Fe} and \ion{Ca}{II} lines).
+This is done by combining the nightly spectra without significant cometary activity (see Sect.~\ref{sect:FEBid}) and binning this stacked spectrum in wavelength in bins of 21 pixels.
+Before binning, the spectrum in each bin was MAD (median absolute deviation) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
+The clipped average of the fluxes within each bin was used.
+Subsequently, the overall spectrum of the star and (residual) blaze was determined by cubic interpolation across the binned points, and divided out of the spectrum for each night.
+As before, for HARPS this was done separately pre- and post-fiber change.
 
-\item Bin the spectrum and clip it, interpolate using a cubic spline.
-
-\item Divide this interpolated cubic spline into each of the nightly spectra.
-
-\end{itemize}
-
-This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the slit aperture.
-
-We then fit a second order polynomial to each individual night and divide this out, resulting in a flattened spectrum for each night.
-
-Subsequently, we applied a correction for variations in the instrumental blaze by selecting a reference spectrum and dividing all the spectra by this reference.
+%Subsequently, we applied a correction for variations in the instrumental blaze by selecting a reference spectrum and dividing all the spectra by this reference.
 The ratio was then binned, removing outliers, and a polynomial was fit to the data.
 %
-For \ac{uves} we used a Nth degree polynomial, while for \ac{harps} we used a 2nd degree polynomial.
+%For \ac{uves} we used a Nth degree polynomial, while for \ac{harps} we used a 2nd degree polynomial.
 %
-This polynomial was then divided from the spectrum under consideration.
+%This polynomial was then divided from the spectrum under consideration.
 We note that the blaze correction will also remove non-instrumental effects, including variations in atmospheric transmission and seeing.
 
-The blaze-corrected spectra taken within a night were averaged together [Should we use a weighted average?].
+%The blaze-corrected spectra taken within a night were averaged together [Should we use a weighted average?].
 %
-We note that for \ac{harps}, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.
+%We note that for \ac{harps}, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.
 
-\section{Searches for cometary species}
+\section{Searches for \ce{CN}}\label{sect:CNsearch}
 
@@
 %
-These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.
+\textcolor{red}{These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.}
 %
-No obvious feature jumps out, and we can rule out circumstellar \ce{CN} down to \hl{NNNN}.
+No obvious feature from the \ce{CN} band jumps out, and we need to combine the signal from the lines within the \ce{CN} band to improve the detection limits.
 
-Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H \& K lines, as well as the MM epochs with the weakest cometary features.
+Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
+
+TODO FIGURE: Just spectrum coadded in stellar rest frame same for comet rest frame in the CN band wavelength range, with the CN band overplotted.
+
+\subsection{Identifying exocomets from \ion{Ca}{ii} H line}\label{sect:FEBid}
+The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968.
+\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central \textcolor{red}{NN} km\,s$^{-1}$.
+The deepest absorption feature in each observing night was selected, and the location and depth stored.
+For the comet sample we selected features deeper than \textcolor{red}{60\% and 40\%} for HARPS and UVES, respectively, while spectra with features below 15\% for both HARPS and UVES were flagged as 'low activity'.
+\textcolor{red}{An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in \hl{Figure}.
+The distribution of feature location and depth is shown in \hl{Figure}}
+
+plotFEbs for the above first two figures!
+
+The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in \hl{Figure}.
+As with the circumstellar \ce{CN}, there are no obvious lines from CN visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any CN present.
 %
-The spectra with only weak exocometary features were co-averaged in the stellar rest frame in order to create a stellar master spectrum.
+%The spectra with only weak exocometary features were co-averaged in the stellar rest frame in order to create a stellar master spectrum.
 This master-spectrum was divided out of all the remaining spectra in order to create relative spectra.
 %
-The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
+%The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
 %
-The combined exocomet aligned spectra for both the \ce{Ca} H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present.
+%The combined exocomet aligned spectra for both the \ce{Ca} H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present.
 %
-[Do we need to add a correction to account for any radiation pressure, if so, is there a way to estimate that?]
 
-[Do we want to do a simple CCF to see if we can combine the individual lines?]
+\subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}
+To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
+Cross-sections for \ce{CN} were obtained from ExoMol \textcolor{red}{REFERENCES HERE} and the cross-sections were calculated using \textcolor{red}{NEED SOME DETAILS...}.
+We made models for a wide range of temperatures (T$=$\{10, 20, 30, 50, 100, 200, 300, 500, 1000, 2000, 3000\} K) and column densities\footnote{Note that technically, for optically thin lines, this assumes a filling factor $f=1$.
+Since $f$ is unknown, we actually measure N$f$} (N=\{$10^{11} \ldots 10^{15}$\} cm$^{-2}$.
+Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} km\,s$^{-1}$.
+A value of 2.9 km\,s$^{-1}$ corresponds approximately to the instrumental resolution of HARPS.
+The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.
 
-We have theoretical spectra of CN shown in Figure~\ref{fig:CN_theory}.
+Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf} do not show any clear signals, and we therefore proceed to estimate our detection limits.
 
@@
     \begin{centering}
-        \includegraphics[width=\columnwidth]{figures/ccf.pdf}
-        \caption{Cross correlation for different number densities of CN.}
-        \label{fig:ccf}
-        \script{plot_ccf.py}
-    \end{centering}
-\end{figure}
-
-\begin{figure}
-    \begin{centering}
         \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
@@
 
-\subsection{\ce{CN}}
+% \begin{figure}
+%     \begin{centering}
+%         \includegraphics[width=\columnwidth]{figures/asdf.png}
+%         \caption{Test picture}
+%         \label{fig:test}
+%     \end{centering}
+% \end{figure}
 
-\begin{figure}
-    \begin{centering}
-        \includegraphics[width=\columnwidth]{figures/HARPS_CN_grid.pdf}
-        \caption{Confidence intervals for the signal to noise of \ce{CN} spectra using \ac{harps} spectra of \bp{}.}
-        \label{fig:HARPS_CN_grid}
-        \script{plot_HARPS_CN_grid.py}
-    \end{centering}
-\end{figure}
+% \begin{figure}
+%     \begin{centering}
+%         \includegraphics[width=\columnwidth]{figures/HARPS_CN_grid.pdf}
+%         \caption{Confidence intervals for the signal to noise of \ce{CN} spectra using \ac{harps} spectra of \bp{}.}
+%         \label{fig:HARPS_CN_grid}
+%         \script{plot_HARPS_CN_grid.py}
+%     \end{centering}
+% \end{figure}
 
 %\subsection{Other Species? CO$^+$, C$_2$?}
+
+\subsection{Estimating the \ce{CN} column density limits}\label{sect:CNlim}
+To estimate the limits on the \ce{CN} detection, we perform injection and recovery tests.
+We injected models for different temperatures, column densities and velocity broadening into the nightly stacked spectra (Sect.~\ref{sect:comb}, and then processed them in the same way as the original data (i.e., correct for residual blaze variations, removal of the stellar envelope and cross-correlation).
+This was done for all spectra with the injected signal in the stellar restframe as well as for the sample of spectra with strong cometary activity in the restframe of the strongest exocometary feature per night.
+
+The individual CCFs show some overall slopes and offsets, and we fit each individual CCF with a combination of a second-order polynomial baseline and a Gaussian with the position fixed to 0 km\,s$^{-1}$ in its restframe.
+The fit has five free parameters: the amplitude of the peak, the width of the peak, and the offset, slope, and intercept of the baseline.
+To avoid the aliasing peaks of the \ce{CN} band (see \hl{Figure}), we only fit the central $\pm$35 km\,s$^{-1}$ of the CCF.
+Fitting is done using the curve\_fit function from SciPy \hl{REFERENCE}.
+We correct each of the individual CCFs for the baseline and then stack the corrected CCFs to obtain our master CCF that we use for determining the upper limit.
+The noise on each point in the master CCF is determined by taking the standard deviation in time for each pixel and dividing that by the square root of the number of points.
+
+This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from curve\_fit assuming no covariance between the parameters.
+The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in \hl{Figure} for the circumstellar gas and in \hl{Figure} for the strongest exocomet features.
 

### 2024-09-06 src/scripts/plot_ccf_mean.py

@@ -10,21 +10,21 @@ FEB_idx=fits.getdata(paths.data/"FEB_idx.fits")
 
 
 ##Find indices for 30K and 2000K
-idx1=np.nonzero(T_gas0 == 30)
-idx2=np.nonzero(T_gas0 == 2000)
+idx1=np.nonzero(T_gas0 == 30)[0][0]
+idx2=np.nonzero(T_gas0 == 2000)[0][0]
 
 ##Find index for N = 10^12 cm^-2
-idxN11=np.nonzero(N0 == 1e11)
-idxN13=np.nonzero(N0 == 1e13)
-idxN15=np.nonzero(N0 == 1e15)
+idxN11=np.nonzero(np.floor(np.log10(N0)) == 11)[0][0]
+idxN13=np.nonzero(np.floor(np.log10(N0)) == 13)[0][0]
+idxN15=np.nonzero(np.floor(np.log10(N0)) == 15)[0][0]
 
 ##Index for v_broad=10km/s
-idxW=np.nonzero(broadening0 == 10.)
+idxW=np.nonzero(broadening0 == 10.)[0][0]
 print(idx1,idxN11,idxW)
 
 v_ccf=fits.getdata(paths.data/"v_phasefold.fits")
-ccf=fits.getdata(paths.data/"phase_cube.fits")
-inj_ccf=fits.getdata(paths.data/"sim_phase_cube.fits")
+ccf=fits.getdata(paths.data/"phase_cube_comet.fits")
+inj_ccf=fits.getdata(paths.data/"sim_phase_cube_comet.fits")
 ccf=ccf[:,:,:,FEB_idx,:]-np.median(ccf,axis=-1)[:,:,:,FEB_idx,np.newaxis]
 inj_ccf=inj_ccf[:,:,:,FEB_idx,:]-np.median(inj_ccf,axis=-1)[:,:,:,FEB_idx,np.newaxis]
     
@@ -40,10 +40,10 @@ ax.set_xlabel('Velocity [$km/s$]',fontsize=16)
 ax.set_ylabel('CCF [a.u.]',fontsize=16)
 
 
[…]

### 2024-09-06 src/tex/ms.tex
CN limit figures

@@
 \end{figure}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
+        \caption{CN measurement limits in the stellar rest frame for a CN line width of 2.7\kms{}. Contours show signal to noise upper limits.}
+        \label{fig:CN_stellar_frame}
+        \script{plot_HARPS_CN_stellar_frame.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure*}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/HARPS_CN_exocomet_frame.pdf}
+        \caption{CN measurement limits in the exocomet frame for a CN line width of 2.7, 10 and 20\kms{}. Contours show signal to noise upper limits.}
+        \label{fig:CN_exocomet_frame}
+        \script{plot_HARPS_CN_exocomet_frame.py}
+    \end{centering}
+\end{figure*}
 

### 2024-09-06 src/scripts/plot_HARPS_CN_exocomet_frame.py

@@ -1,0 +1,101 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+from astropy.io import fits
+import matplotlib as mpl
+
+mpl.use('macosx')
+
+
+T0=fits.getdata(paths.data/'T_gas.fits')
+N0=fits.getdata(paths.data/'Nf.fits')
+w=fits.getdata(paths.data/'broadening.fits')
+
+midpts_T=(T0[1:]+T0[:-1])/2.
+x=np.arange(midpts_T.shape[0])+1
+#T=10**np.polyval(np.polyfit(x,np.log10(midpts_T),1),np.arange(T0.shape[0]+1))
+T=np.hstack((0.,midpts_T,1.5*T0[-1]))
+
+midpts_N=(N0[1:]+N0[:-1])/2.
+x=np.arange(midpts_N.shape[0])+1
+N=10**np.polyval(np.polyfit(x,np.log10(midpts_N),1),np.arange(N0.shape[0]+1))
+
+
+
+# fit=fits.getdata(paths.data/'fit_cube_comet.fits')
+# sig0=fits.getdata(paths.data/'fit_err_cube_comet.fits')
+
+# mean=fit[:,:,:,-1,:]
+# sig=sig0[:,:,:,-1,:]#np.std(fit[:,:,:,:-1,:],axis=-2)/np.sqrt(fit.shape[-2])
+# SN=mean/sig
+# print(SN.shape,T.shape,N.shape,w.shape)
+
+# f,ax=plt.subplots(1,6,figsize=(16,6),gridspec_kw={"width_ratios":[1,1,1,1,1,0.1]})
+# vmin=np.min(SN[:,:,:,0])
+# vmax=np.max(SN[:,:,:,0])
+# for i in range(5):
+#     im=ax[i].pcolormesh(N,T,SN[:,:,i,0],vmin=vmin,vmax=vmax,shading='flat')
+#     ax[i].set_xscale('log')
+# f.colorbar(im,cax=ax[-1])
+
+# ax[0].set_ylabel('T [K]',fontsize=12)
+# for i in range(5):
+#     ax[i].set_xlabel('N$\cdot$f [cm$^{-2}$]',fontsize=12)
+    
+# f.tight_layout()
+
+
+
+
+##run for simulation
+
+# fit=fits.getdata(paths.data/'sim_fit_cube_comet.fits')
+
[…]

### 2024-09-06 src/scripts/plot_HARPS_CN_stellar_frame.py

@@ -1,0 +1,57 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+from astropy.io import fits
+import matplotlib as mpl
+
+mpl.use('macosx')
+
+T0=fits.getdata(paths.data/'T_gas.fits')
+N0=fits.getdata(paths.data/'Nf.fits')
+w=fits.getdata(paths.data/'broadening.fits')
+
+##run for simulation
+
+fit=fits.getdata(paths.data/'sim_fit_cube_stellar.fits')
+sig0=fits.getdata(paths.data/'sim_fit_err_cube_stellar.fits')
+
+mean=fit[:,:,:,-1,:]
+sig=sig0[:,:,:,-1,:]
+SN=mean/sig
+
+def fmt(x):
+    s = f"{x:.0f}"
+    return rf"{s} \sigma" if plt.rcParams["text.usetex"] else f"{s} $\sigma$"
+
+nplot = 2
+f,ax=plt.subplots(1,nplot,figsize=(8,6),gridspec_kw={"width_ratios":[1,0.08]})
+for i in range(nplot-1):
+    SNclip = SN[:,:,i,0]
+    SNclip[(SNclip<1)]=1
+    im=ax[i].pcolormesh(N0,T0,SN[:,:,i,0],
+        shading='auto',
+        vmin=1,vmax=600,norm='log')
+    ax[i].set_xscale('log')
+    ax[i].set_yscale('log')
+    (xx,yy) = np.meshgrid(T0,N0)
+    CS = ax[i].contour(N0, T0, SN[:,:,i,0], [5.7,20,50,200],
+        colors=['#AAAAAA', '#AA8888', '#AA4444','#AA2222'],
+        extend='both')
+
+    ax[i].clabel(CS, CS.levels, inline=True, fmt=fmt, fontsize=20)
+
+    ax[i].set_xlim([10**11.5,10**15.5])
+    ax[i].set_ylim([10**1,10**3.4])
+
+    #ax[i].scatter(yy,xx)
+    ax[i].tick_params(axis='both',labelsize=14)
+
+f.colorbar(im,cax=ax[-1])
+
+ax[0].set_ylabel('T [K]',fontsize=18)
+ax[0].set_xlabel(f'N$\cdot$f [$cm^{{-2}}$] width={w[0]:.1f} km/s',fontsize=18)
+    
+f.tight_layout()
+
+plt.savefig(paths.figures/'HARPS_CN_stellar_frame.pdf')
+#plt.show()

### 2024-09-06 src/tex/ms.tex
added CN_ACF plot

@@
 
-Note that for HARPS, the change of fiber in \textcolor{red}{June 2015 (JD$\sim$2457180)} resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.
+Note that for HARPS, the change of fiber in June 2015 (JD$\sim$2,457,180) resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.
 
@@
 %
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/CN_ACF.pdf}
+        \caption{CN autocorrelation function for different temperatures.}
+        \label{fig:CN_ACF}
+        \script{plot_CN_ACF.py}
+    \end{centering}
+\end{figure}
 
@@
 This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from curve\_fit assuming no covariance between the parameters.
-The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in \hl{Figure} for the circumstellar gas and in \hl{Figure} for the strongest exocomet features.
+The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in Figure~\ref{fig:CN_stellar_frame} for the circumstellar gas and in Figure~\ref{fig:CN_exocomet_frame} for the strongest exocomet features.
 

### 2024-09-06 src/scripts/plot_CN_ACF.py

@@ -1,10 +1,3 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jul 26 15:54:53 2022
-
-@author: demooij
-"""
-
 import numpy as np
 import matplotlib.pyplot as plt
 from astropy.io import fits
@@ -41,17 +34,31 @@ order_end  =4060
 dv=np.linspace(-300,300,601)
 col=['r','g','b','c','y','m','k','orange']
 T_gas0=np.asarray([10, 20, 50, 100, 200, 300, 1000, 2000])
-f,ax=plt.subplots(1,2,sharex=True)
+T_gas0=np.asarray([10, 50, 100,  300, 1000, 2000])
+f,ax=plt.subplots(2,1,sharex=True)
 
+
+colors = plt.cm.viridis(np.linspace(0,1,np.size(T_gas0)))
 ##: left panel: un-normalised ACF, right panel: normalised ACF
 for i,T in enumerate(T_gas0):
     w,prof,imdl=get_mdl('CN/CN_{0:04d}K.npy'.format(T),N=1e13)
     p2=imdl(wlen[order_start:order_end])
     ccf,ccf0=c_correlate(wlen[order_start:order_end],np.vstack((p2,p2)),imdl,dv=dv)
-    ax[0].plot(dv,ccf[0,:],col[i],label='T={0:}K'.format(T))
-    ax[1].plot(dv,ccf[0,:]/np.max(ccf[0,:]),col[i],label='T={0:}K'.format(T))
-ax[0].legend()
-f.tight_layout()
-f.savefig(paths.figures/'ccf_self.png') 
+    ax[0].plot(dv,ccf[0,:],color=colors[i],linewidth=3,label='T={0:}K'.format(T))
+    ax[1].plot(dv,ccf[0,:]/np.max(ccf[0,:]),color=colors[i],linewidth=3,label='T={0:}K'.format(T))
 
-plt.show()
+ax[0].tick_params(axis='both',labelsize=14)
+ax[1].tick_params(axis='both',labelsize=14)
+#f.tight_layout()
+
+ax[0].legend()
+
+ax[1].set_xlabel(f'Rest frame velocity [km/s]',fontsize=18)
+ax[1].set_ylabel(f'Peak normalised',fontsize=18)
+ax[0].set_ylabel(f'Strength',fontsize=18)
+
+ax[0].set_xlim(-150,150)
+
+f.savefig(paths.figures/'CN_ACF.pdf') 
+
+#plt.show()

### 2024-09-06 src/scripts/plot_FEBs.py

@@ -1,37 +1,0 @@
-import matplotlib.pyplot as plt
-from astropy.io import fits
-import numpy as np
-import paths
-import matplotlib as mpl
-mpl.use('macosx')
-
-vgrid=fits.getdata(paths.data/'FEB_vgrid.fits')
-orig_spec=fits.getdata(paths.data/'FEB_spec_orig.fits')
-FEB_spec=fits.getdata(paths.data/'FEB_spec.fits')
-FEB_idx=fits.getdata(paths.data/'FEB_idx.fits')
-NO_FEB_idx=fits.getdata(paths.data/'NO_FEB_idx.fits')
-FEB_depths=fits.getdata(paths.data/'FEB_depths.fits')
-FEB_vel=fits.getdata(paths.data/'FEB_velocities.fits')
-
-
-spec_FEB=FEB_spec[:,FEB_idx]
-spec_NO_FEB=FEB_spec[:,NO_FEB_idx]
-
-
-
-v_idx=(np.abs(vgrid)>8)*(np.abs(vgrid)<=200)
-
-f,ax=plt.subplots(2,1,sharex=True)
-ax[0].plot(vgrid,(orig_spec[:,FEB_idx])[:,1])
-ax[0].plot(vgrid,np.mean(orig_spec[:,NO_FEB_idx],axis=1))
-ax[1].plot(vgrid[v_idx],(spec_FEB[v_idx,:])[:,1])
-ax[1].vlines((FEB_vel[FEB_idx])[1],0,2)
-ax[1].plot(vgrid[v_idx],np.mean(spec_NO_FEB[v_idx,:],axis=1))
-ax[0].set_xlim(-200,200)
-ax[0].set_ylim(0,1.1)
-plt.show()
-
-
-f,ax=plt.subplots()
-ax.plot(FEB_vel,FEB_depths,'k.')
-plt.show()

### 2024-09-06 src/scripts/plot_FEB_velocity_depth.py
added FEB velocity

@@ -1,0 +1,31 @@
+import matplotlib.pyplot as plt
+from astropy.io import fits
+import numpy as np
+import paths
+import matplotlib as mpl
+mpl.use('macosx')
+
+FEB_spec=fits.getdata(paths.data/'FEB_spec.fits')
+FEB_idx=fits.getdata(paths.data/'FEB_idx.fits')
+NO_FEB_idx=fits.getdata(paths.data/'NO_FEB_idx.fits')
+FEB_depths=fits.getdata(paths.data/'FEB_depths.fits')
+FEB_vel=fits.getdata(paths.data/'FEB_velocities.fits')
+
+spec_FEB=FEB_spec[:,FEB_idx]
+spec_NO_FEB=FEB_spec[:,NO_FEB_idx]
+
+xlow=0.15
+xhig=0.60
+
+f,ax=plt.subplots(1,1,figsize=(8,4))
+
+ax.plot(FEB_vel,FEB_depths,'k.')
+ax.set_xlabel('Velocity [km/s]')
+ax.set_ylabel('Normalised continuum')
+ax.set_ylim(-0.1,1.1)
+ax.hlines(xlow,-300,300,linestyle='dashed')
+ax.hlines(xhig,-300,300,linestyle='dashed')
+ax.hlines(0,-300,300,linestyle='dotted')
+ax.set_xlim(-25,80)
+plt.savefig(paths.figures/'FEB_velocity_depth.pdf')
+#plt.show()

### 2024-10-03 src/tex/ms.tex
added FEB velocity
new plots

@@
 %
-Additional, much narrower absorption features are seen in the Calcium H and K lines.
-%
-These features appear and disappear on several hour long timescales, and show a different range of morphologies \hl{[REF]}.
+The Ca H and K lines show deep absorption to 0.1 of the continuum level.
+%
+A consistent and stable narrow absorption feature with a FWHM of a few km/s is explained by the presence of the circumstellar material.
+%
+There exist transient, irregular shaped absorption features in the spectra of the star.
+%
+These appear and disappear on hour long timescales, and show a different range of morphologies, predominantly seen at bluer wavelengths. \hl{[REF]}.
 %
@@
 %
-The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of metals that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component \hl{[REF REF]}.
-
-From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the Kepler satellite [REF] and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19}.
-%
-Observations of Beta Pictoris in subsequent TESS sector revealed over two dozen transits whost depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
+The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component \hl{[REF REF]}.
+
+From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \hl{REF} and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19}.
+%
+Observations of Beta Pictoris in subsequent TESS sector revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
 
@@
 
-Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the \ac{feb} around Beta Pic.
+Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the \ac{feb} around \bp{}.
 %
@@
 
-\section{Data description and analysis}
+We detail the observations in Section~\ref{sec:data}, along with the correction for the echelle blaze function and normalization of the spectra to a continuum.
+%
+Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Section~\ref{sect:CNsearch}, and the discussion and interpretaion is in Section~\ref{sec:discuss} with our conclusions in Section~\ref{sec:conclusion}.
+
+\section{Data description and analysis}\label{sec:data}
 
@@
 
-We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and \textcolor{red}{March 2020}.
+We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and \hl{March 2020}.
 %
@@
 %
-Similarly, the number of observations per epoch spans a wide range, between \textcolor{red}{1 and 356} exposures, while the exposure times vary between \textcolor{red}{12 and 900} seconds.
-This results in a SNR range per exposure between \textcolor{red}{NNNN and MMMM}, and a nightly SNR between \textcolor{red}{NNNN and MMMM}.
+Similarly, the number of observations per epoch spans a wide range, between \hl{1 and 356} exposures, while the exposure times vary between \hl{12 and 900} seconds.
+This results in a SNR range per exposure between \hl{NNNN and MMMM}, and a nightly SNR between \hl{NNNN and MMMM}.
 %
@@
 
-\textcolor{red}{Q: Do we want to put an observing log in the appendix?}
-\textcolor{red}{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
+% \hl{Q: Do we want to put an observing log in the appendix?}
+% \hl{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
 
@@
 
-The data were reduced using the ESO \ac{uves} pipeline version \textcolor{red}{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+The data were reduced using the ESO \ac{uves} pipeline version \hl{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
 The flat-field was applied on a pixel-by-pixel basis.
-\textcolor{red}{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
+\hl{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
 Optimal extraction was performed, using an empirical profile}
@@
 %
-Each order was treated separately, with the main focus on orders \textcolor{red}{4 and 8} for HARPS and \textcolor{red}{4, and 7} for UVES as those orders contain the main CN bandhead as well as the \ion{Ca}{ii} H line, which are used to identify the exocomets.
+Each order was treated separately, with the main focus on orders \hl{4 and 8} for HARPS and \hl{4, and 7} for UVES as those orders contain the main \ce{CN} bandhead as well as the \ion{Ca}{ii} H line, which are used to identify the exocomets.
 %
 All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.
-For UVES, the \ce{Fe} \textcolor{red}{NNNN~$\AA$} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
-To measure these, a Gaussian was fit to the line, and the velocity offset from the restframe position determined.
-
-%
-After all the spectra were all transformed into the stellar restframe, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
+For UVES, the \ce{Fe} \hl{NNNN angstrom} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
+To measure these, a Gaussian was fit to the line, and the velocity offset from the rest frame position determined.
+
+%
+After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
 This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption etc.), as outlined below.
@@
 
-\subsubsection{Effective Blaze function correction}\label{sect:blaze}
-
-One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function (the night of \textcolor{red}{DATE} for HARPS and \textcolor{red}{DATE} for UVES).
+\subsection{Effective Blaze function correction}\label{sect:blaze}
+
+One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function (the night of \hl{DATE} for HARPS and \hl{DATE} for UVES).
 The individual spectra in this night were averaged together to further boost the signal-to-noise ratio.
 Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
-This ratio spectrum was subsequently binned using a bin-width of \textcolor{red}{101} pixels using a robust algorithm to remove outliers within each bin.
-This binned ratio was than fit using a \textcolor{red}{second} order polynomial.
+This ratio spectrum was subsequently binned using a bin-width of \hl{101} pixels using a robust algorithm to remove outliers within each bin.
+This binned ratio was than fit using a \hl{second} order polynomial.
 The original spectrum was finally divided by this polynomial to correct for the changes.
@@
 
-\subsubsection{Combining the spectra and flattening them}\label{sect:comb}
+\subsection{Combining the spectra and flattening them}\label{sect:comb}
 After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
-Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders \textcolor{red}{NN and MM, and OO and PP} for HARPS and UVES respectively.
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders \hl{NN and MM, and OO and PP} for HARPS and UVES respectively.
 
@@
 
-\subsubsection{Removing the stellar spectrum}\label{sect:starcor}
+\subsection{Removing the stellar spectrum}\label{sect:starcor}
 The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and, for HARPS, shape of the blaze profile, are still present and need to be removed.
 
-For both HARPS and UVES we first perform a second iteration of blaze corrections using a  stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see \textcolor{red}{Sect.~\ref{sect:FEBident}}.
+For both HARPS and UVES we first perform a second iteration of blaze corrections using a  stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see \hl{Sect.}~\ref{sect:FEBident}.
 For HARPS this is done separately pre- and post-fiber change.
-The correction is done similar to Sect.~\ref{sect:blaze}, however for both UVES and HARPS a \textcolor{red}{4th order} polynomial was used.
+The correction is done similar to Sect.~\ref{sect:blaze}, however for both UVES and HARPS a \hl{4th order} polynomial was used.
 
@@
 %
-\textcolor{red}{These coadded spectra for \ac{harps} and \ac{uves} are shown in \hl{Figure}.}
+\hl{These coadded spectra for }\ac{harps} and \ac{uves} are shown in \hl{Figure}.
 %
@@
 
-Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the NN epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
-
-TODO FIGURE: Just spectrum coadded in stellar rest frame same for comet rest frame in the CN band wavelength range, with the CN band overplotted.
+Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the \hl{NN} epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
+
+\hl{TODO FIGURE: Just spectrum coadded} in stellar rest frame same for comet rest frame in the \ce{CN} band wavelength range, with the \ce{CN} band overplotted.
 
@@
 The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968.
-\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central \textcolor{red}{NN} km\,s$^{-1}$.
+\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central \hl{NN} km\,s$^{-1}$.
+%
 The deepest absorption feature in each observing night was selected, and the location and depth stored.
-For the comet sample we selected features deeper than \textcolor{red}{60\% and 40\%} for HARPS and UVES, respectively, while spectra with features below 15\% for both HARPS and UVES were flagged as 'low activity'.
-\textcolor{red}{An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in \hl{Figure}.
-The distribution of feature location and depth is shown in \hl{Figure}}
+%
+For the comet sample we selected features deeper than \hl{60\% and 40\%} for HARPS and UVES, respectively, while spectra with features below 15\% for both HARPS and UVES were flagged as `low activity'.
+%
+An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in Figure \hl{XXXX}.
+%
+The distribution of feature location and depth is shown in \hl{Figure}.
 
@@
 The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in \hl{Figure}.
-As with the circumstellar \ce{CN}, there are no obvious lines from CN visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any CN present.
+%
+As with the circumstellar \ce{CN}, there are no obvious lines from \ce{CN} visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any \ce{CN} present.
 %
@@
         \includegraphics[width=\columnwidth]{figures/CN_ACF.pdf}
-        \caption{CN autocorrelation function for different temperatures.}
+        \caption{\ce{CN} autocorrelation function for different temperatures.}
         \label{fig:CN_ACF}
@@
 \subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}
-To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
-Cross-sections for \ce{CN} were obtained from ExoMol \textcolor{red}{REFERENCES HERE} and the cross-sections were calculated using \textcolor{red}{NEED SOME DETAILS...}.
-We made models for a wide range of temperatures (T$=$\{10, 20, 30, 50, 100, 200, 300, 500, 1000, 2000, 3000\} K) and column densities\footnote{Note that technically, for optically thin lines, this assumes a filling factor $f=1$.
-Since $f$ is unknown, we actually measure N$f$} (N=\{$10^{11} \ldots 10^{15}$\} cm$^{-2}$.
-Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} km\,s$^{-1}$.
-A value of 2.9 km\,s$^{-1}$ corresponds approximately to the instrumental resolution of HARPS.
-The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.
-
-Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf} do not show any clear signals, and we therefore proceed to estimate our detection limits.
 
@@
         \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
-        \caption{Model spectrum for CN.}
+        \caption{Model absorption spectrum for \ce{CN} at two temperatures.}
         \label{fig:CN_theory}
@@
 
+To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
+%
+Cross-sections for \ce{CN} were obtained from ExoMol \hl{REFERENCES HERE} and the cross-sections were calculated using \hl{NEED SOME DETAILS...}. 
+%
+We made models for a wide range of temperatures (T$=$\{10, 20, 30, 50, 100, 200, 300, 500, 1000, 2000, 3000\} K) and column densities\footnote{Note that technically, for optically thin lines, this assumes a filling factor $f=1$.
+%
+Since $f$ is unknown, we actually measure N$f$} (N=\{$10^{11} \ldots 10^{15}$\} cm$^{-2}$.
+%
+Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} km\,s$^{-1}$.
+%
+A value of 2.9 km\,s$^{-1}$ corresponds approximately to the instrumental resolution of HARPS.
+%
+The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.
+
+Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf} do not show any clear signals, and we therefore proceed to estimate our detection limits.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/FEB_velocity_depth.pdf}
+        \caption{Peaks and radial velocities of exocomets identified in the stellar spectrum.
+        %
+        The peaks are normalised such that 1 represents total absorption in the spectrum.
+        %
+        Peaks closer than 10 km/s are masked out due to contamination from the circumstellar material.
+        %
+        Peak values above 0.6 are counted as exocomets and those below 0.15 as stellar only.}
+        \label{fig:FEB_velocity}
+        \script{plot_FEB_velocity_depth.py}
+    \end{centering}
+\end{figure}
+
 \begin{figure}
@@
         \includegraphics[width=\columnwidth]{figures/ccf_mean.pdf}
-        \caption{Cross correlation for different number densities of CN averaged over many spectra.}
+        \caption{Cross correlation for different number densities of \ce{CN} averaged over many spectra.}
         \label{fig:ccf_mean}
@@
         \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
-        \caption{CN measurement limits in the stellar rest frame for a CN line width of 2.7\kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7\kms{}. Contours show signal to noise upper limits.}
         \label{fig:CN_stellar_frame}
@@
         \includegraphics[width=\linewidth]{figures/HARPS_CN_exocomet_frame.pdf}
-        \caption{CN measurement limits in the exocomet frame for a CN line width of 2.7, 10 and 20\kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the exocomet frame for a \ce{CN} line width of 2.7, 10 and 20\kms{}. Contours show signal to noise upper limits.}
         \label{fig:CN_exocomet_frame}
@@
 \subsection{Estimating the \ce{CN} column density limits}\label{sect:CNlim}
+
 To estimate the limits on the \ce{CN} detection, we perform injection and recovery tests.
+%
 We injected models for different temperatures, column densities and velocity broadening into the nightly stacked spectra (Sect.~\ref{sect:comb}, and then processed them in the same way as the original data (i.e., correct for residual blaze variations, removal of the stellar envelope and cross-correlation).
-This was done for all spectra with the injected signal in the stellar restframe as well as for the sample of spectra with strong cometary activity in the restframe of the strongest exocometary feature per night.
-
-The individual CCFs show some overall slopes and offsets, and we fit each individual CCF with a combination of a second-order polynomial baseline and a Gaussian with the position fixed to 0 km\,s$^{-1}$ in its restframe.
+%
+This was done for all spectra with the injected signal in the stellar rest frame as well as for the sample of spectra with strong cometary activity in the rest frame of the strongest exocometary feature per night.
+
+The individual CCFs show some overall slopes and offsets, and we fit each individual CCF with a combination of a second-order polynomial baseline and a Gaussian with the position fixed to 0 \kms{} in its rest frame.
+%
 The fit has five free parameters: the amplitude of the peak, the width of the peak, and the offset, slope, and intercept of the baseline.
-To avoid the aliasing peaks of the \ce{CN} band (see \hl{Figure}), we only fit the central $\pm$35 km\,s$^{-1}$ of the CCF.
-Fitting is done using the curve\_fit function from SciPy \hl{REFERENCE}.
+%
+To avoid the aliasing peaks of the \ce{CN} band (see Figure~\ref{fig:CN_theory}), we only fit the central $\pm$35 \kms{} of the CCF.
+%
+Fitting is done using the curve\_fit function from SciPy \citep{2020SciPy-NMeth}.
+%
 We correct each of the individual CCFs for the baseline and then stack the corrected CCFs to obtain our master CCF that we use for determining the upper limit.
+%
 The noise on each point in the master CCF is determined by taking the standard deviation in time for each pixel and dividing that by the square root of the number of points.
 
-This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from curve\_fit assuming no covariance between the parameters.
+This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from {\tt curve\_fit} assuming no covariance between the parameters.
+%
 The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in Figure~\ref{fig:CN_stellar_frame} for the circumstellar gas and in Figure~\ref{fig:CN_exocomet_frame} for the strongest exocomet features.
 
-\section{Discussion}
-
-\section{Conclusions}
+\section{Discussion}\label{sec:discuss}
+
+%\subsection{Summary of \ce{CN} in comets}
+
+\ce{CN} is one of the brightest optically active species in cometary comae.
+%
+It is a minor component of the gas coma, with a production rate by number $\sim 1/500$th that of water.
+
+Most studies of Solar system comets simply observe the \ce{CN} molecules via optical fluorescence.
+%
+From measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
+%
+This means a flux from part of the coma can immediately be converted to a column density using a photon scattering efficiency for the molecular band.
+
+\ce{CN} in solar system comets comes from two sources.
+%
+Sublimation of nucleus near-surface ices releases \ce{HCN}, which then photo-dissociates into \ce{CN}.
+%
+This in turn eventually photo-dissociates into the component atoms.
+
+$$\ce{HCN} +\gamma \rightarrow \ce{H}+\ce{CN}$$
+$$\ce{CN} + \gamma \rightarrow \ce{C}+\ce{N}$$
+
+Since Halley in 1986, it has also been known that dust grains ejected from the nucleus also directly release \ce{CN} into the coma.
+%
+However, \ce{CN} production in comets is usually dominated by nuclear ice sublimation.
+
+The resulting \ce{CN} coma will have a true space density and apparent column density distribution centrally peaked at the comet nucleus.
+%
+For Solar system comets, column densities are often converted to an overall production rate $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model.
+%
+For this model there are only 3 parameters; the effective destruction scale length $l_p$ of the parents of \ce{CN} (\ce{HCN}+dust), the photodissociation scale length $l_{\ce{CN}}$ of \ce{CN}, and the gas outflow velocity $v$.
+%
+The Haser model is somewhat simplistic but it represents the data well.
+
+\subsection{Example comet - 1P/Halley}
+
+We take the observed activity of 1P/Halley in 1985/86 as an example for our estimates.
+%
+Although most comets we observe are far less active than Halley, there are quite a few comets with activity similar to it.
+%
+Given that we will be dominated by the most active comets at \bp{}, this seems reasonable as something that can be later scaled to the brightest comets such as Hale-Bopp.
+%
+When Halley was at $\sim 1$ au from the Sun, it was measured to have $Q_{\ce{CN}}\simeq 10^{27}$ molecules/sec using Haser models.
+%
+The assumed outflow velocity in the models was generally  $0.85 - 1$ \kms{} at this distance.
+
+For solar system comets, the normal Haser scale lengths used \citep{Cochran86,AHearn1995} are:
+
+$$lp=1.7\times10^4r_h^2\:{\rm km}$$
+
+$$l_{\ce{CN}}=2-3\times10^5r_h^2\:{\rm km}$$
+
+Both are assumed to scale with heliocentric distance $r_h^2$ as photodissociation or thermal desorption is assumed the main physical pathway for both the parent and \ce{CN}.
+
+The lifetime of \ce{HCN} for photodissociation into \ce{H}+\ce{CN} at 1~au has been calculated to be $(3.2-7.7)\times10^4$ sec, with lifetime of \ce{CN} dissociating into \ce{C}+\ce{N} being $(1.3-3.1)\times10^5$ sec \citep{Huebner92}, depending on solar activity levels.
+%
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ km/sec, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of 1 \kms{}.
+
+\subsection{1P/Halley at \bp{}}
+
+%\subsubsection{Total \ce{CN} Abundance}
+
+Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by Ly-$\alpha$ line flux.
+From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A7V stars is a factor of $\sim10$ higher than for G2V stars.
+%
+Hence the photodissociation lifetime of \ce{CN} will be 10 times smaller i.e. $\sim 2\times10^4$ sec at 1 au.
+
+In steady-state sublimation, the sublimation rate is proportional to the photon flux at the comet.
+For \bp{} $L=8.7L_\odot$, hence assuming dust desorption also scales this way, Halley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 8\times10^{27}$ molecules/sec.
+%
+The total number of \ce{CN} molecules in the coma at 1~au would therefore be
+
+$$N_{\ce{CN}}=Q_{\ce{CN}} \tau_{\ce{CN}}$$
+
+$$N_{\ce{CN}}\sim 8\times10^{27} \cdot  2\times10^4 \sim 2\times10^{32}\:{\rm molecules}$$
+
+%\subsubsection{\ce{CN} Cross-section}
+
+The outflow velocity of the parent of \ce{HCN} will depend on the nuclear surface temperature as $\sqrt{T}$.
+%
+Modelling shows that ice sublimation acts approximately as a thermostat for the nucleus surface temperature, implying that the \ce{HCN} will only slowly increase with decreasing temperature.
+%
+\citet{Biver99} found $v\propto r_h^{-0.4}$ from sub-mm measurements of Hale-Bopp, close to the expected relationship of $r_h^{-0.5}$.
+%
+Dust grains will also be travelling faster due to the larger gas pressure accelerating them.
+%
+The photodissociation velocity of \ce{CN} will obviously not change.
+
+Here we will make the simplifying assumption that gas outflow speeds are dominated by the photodissociation of \ce{CN} at $\sim 1$ \kms{}.
+%
+The size of of the \ce{CN} coma will be given by
+
+$$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$
+$$r\sim 1.0 \times 2\times 10^{4}\sim 2\times 10^{4}\:{\rm km}$$
+
+This is much smaller than a stellar radius, so we can assume all of the coma is projected into the stellar disk as seen from Earth.
+
+\bp{} has $R=1.8R_\odot\equiv 1.3\times 10^{11}$ cm.
+%
+Given that the coma is optically thin, and we do not resolve the star, the effective average column density towards \bp{} is
+
+$$n\sim\frac{N_{\ce{CN}}}{\pi R_*^2}$$
+
+$$n\sim\frac{2\times10^{32}}{\pi\cdot 1.7\times10^{22}}\sim 3\times10^{9}\:{\rm cm^{-2}}$$
+
+Hence comet Halley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{9}-10^{10}$ cm$^{-2}$.
+%
+This is about a factor of 100 smaller than our calculated upper limits.
+
+\subsection{Raising the \ce{CN} production rates}
+
+%\subsubsection{We need a bigger comet}
+There are several ways we can get larger \ce{CN} rates.
+%
+A larger comet gives more surface area for sublimation.
+%
+While Halley's nucleus is much bigger than most other comets, there have been larger.
+%
+Hale-Bopp in 1997 was one of the most intrinsically active comets on record.
+%
+This was because of its extremely large nucleus of radius $\sim 30$ km.
+%
+However most of the apparent brightness was due to dust emission, and its only had $Q_{\ce{CN}}\simeq 3\times10^{27}$ molecules/sec.
+%
+Given this, it is likely that comets may exist with gas production rates a factor of 10 higher.
+
+In this case, with all things considered we might anticipate the most active comets in the Solar system to have $Q_{\ce{CN}}\sim \times10^{28}$ molecules/sec, implying a commensurate increase of a factor 10 in $n_{\ce{CN}}$ at \bp{}.
+
+%\subsubsection{Turn on the taps}
+
+Most comets only have a fraction of their surface area undergoing mass-loss, due to the effect of a thermally insulating dust crust.
+%
+Halley itself only has $\sim 20$\% of the sunlit surface active.
+%
+Yet we know of some Jupiter-family comets that have $\sim 100$\% fractional active surface, and it is believed that many long-period comets also exhibit high activity.
+%
+Assuming this for \bp{} would increase $Q_{\ce{CN}}$ and $n$ by a factor $\sim 5$.
+
+%\subsubsection{Move it closer to \bp{}}
+
+The closer a comet is to its star, the greater the heating and corresponding production rate as $Q_{\ce{CN}}\propto r_h^{-2}$.
+%
+Studies of Halley and Hale-Bopp showed power laws close to this, but the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
+
+$$N_{\ce{CN}}=\frac{Q_{\ce{CN}}(1~\rm{au})}{r_h^2}\cdot  \tau_{\ce{CN}} (1~\rm{au}) r_h^2 =\:{\rm constant} $$
+
+Hence the total amount of \ce{CN} should be approximately independent of stellar distance.
+
+%\subsubsection{Stay up all night to get lucky}
+Comets have impulsive outbursts, where the amount of material ejected into the coma increases significantly over a few hours or less.
+%
+This varies from comet to comet; many do not appear to outburst, some have 1--few outbursts per orbit, some have many more.
+%
+The general causes are unclear, but there is evidence for several physical mechanisms that cause them.
+
+``Normal'' outbursts generally result in a brightness increases of 1--5 magnitudes, with smaller outbursts being more common.
+%
+As the apparent brightness is directly proportional to the amount of material (gas+dust) in the coma, if we assume the gas follows the dust, this implies short term increases in $N_{\ce{CN}}$ and $n$ of factors $\sim 2-100$.
+
+Large outbursts are often due to partial or total disruption of a comet, which often (but not always) occurs when a comet is closer to the Sun.
+%
+Hence there could be a correlation with faster moving \bp{} exocomets nearer their periastra producing greater measurable column densities of \ce{CN}.
+
+A reasonably active comet would give an effective \ce{CN} column density of $\sim 10^{9}-10^{10}$ cm$^{-2}$.
+%
+A larger or more active nucleus could increase that by a factor 10.
+%
+Even larger increases are possible with an outburst or comet disruption, but the limit is likely to be  $n\sim10^{12}$ cm$^{-2}$.
+
+\section{Conclusions}\label{sec:conclusion}
+
+We have combined over 1000 spectra of Beta Pictoris over a 20 year period, identified two groups, one with deep exocomet signals, and another to act as a stellar reference.
+%
+We produce a normalised spectrum towards Beta Pictoris with the stellar spectral features removed, and then aligned the spectra to the exocomet rest frames and perform a search for \ce{CN} using cross correlation.
+
+We do not detect \ce{CN} both in the stellar rest frame and in the exocomet rest frame.
+%
+Injection and recovery tests show that for the circumstellar \ce{CN} we are sensitive to $10^{12.5}$ cm$^{-2}$ below 80~K and below $10^{14}$cm$^{-2}$ up to 1800~K.
+%
+In the exocomet rest frames, sensitivity is somewhat similar.
+%
+Below 100K the sensitivity is $10^{12}$cm$^{-2}$ and above from 100 - 1800~K, is $10^{13}$cm$^{-2}$.
+%
+This is a factor of 10 to 100 too high to detect a single Hale-Bopp equivalent comet with a \ce{CN} halo.
+%
+%We detect no \ce{CN} absorption, but can place five sigma upper limits of 10e12 to 10e13 from 10 to 1800 K.
+%
+%Hale-Bopp in transit will be around $10^{10}$, so we are two orders of magnitude above this in our detection.
+%
+The assumptions are for steady state comets, so individual outbursts could build this number up, and multiple transiting exocomets can increase the absorption cross section.
+
+\bp{} is the brightest star with known exocomets seen both in transit and spectroscopy, and represents the best candidate for exocomet characterisation.
+%
+A more dedicated observing campaign over several years using dedicated spectrographs can reach the equivalent Solar system limits for \ce{CN}.
+%
+PLATO will carry out a dedicated long stare campaign that will observe the star with sub-millimagnitude photometry over 2 to 3 years.
+%
+This presents an excellent opportunity for coordinated spectroscopic campaigns where the exocomet population of Beta Pictoris can be characterised, with \ce{CN} and ideally other molecules known from Solar sysgem comets to be identified in another stellar system.
 
@@
 An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/}
+
 \end{acknowledgements}

### 2024-10-03 src/scripts/analyse_HARPS_spectra.py

@@ -71,7 +71,7 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
 
 ##Read in data
 def read_data(order=[0,1,2,3,4,5,6,7]):
-    vsys=20.    #Systemic velocity of beta Pic
+    vsys=20.    #Systemic velocity of beta Pic estimated from data
     nspec = fits.getdata(paths.data/'2d_nspec.fits')
     spec = fits.getdata(paths.data/'2d_spec.fits')
     wlen = fits.getdata(paths.data/'2d_wavelength.fits')/(1.+vsys/3e5)
@@ -81,7 +81,7 @@ def read_data(order=[0,1,2,3,4,5,6,7]):
 
 
 ## Estimate residual blaze
-def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=4):
+def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=6):
     # order start and order end (the pixel point where there is flux in the order)
     # for the first eight orders
     o_start=np.array([ 225,  15,  15,  15,  15,  15,  15,  15])
@@ -90,7 +90,7 @@ def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=4):
     # take the ratio of the spectrum to the mean spectrum...
     spec_cor=spec[:,ord,:]/star_spec[np.newaxis,ord,:]
     
-    binsize=400
+    binsize=150
     idx=(pixels>o_start[ord])*(pixels<o_end[ord])
     nbins=pixels.shape[0] // binsize
 
@@ -142,8 +142,7 @@ def remove_stellar_envelope(spec,ord):
     for i in range(spec0.shape[1]):
         tmp_array=spec0[:,i].copy()
         tmp_array.sort()
-        spec_star_only0[i]=np.mean(tmp_array[-15:-5])
-        
+        spec_star_only0[i]=np.median(tmp_array)#[-25:-15])
 
         
     #Now fit the overall envelope but leaving narrow features hopefully intact
@@ -173,6 +172,13 @@ def remove_stellar_envelope(spec,ord):
         spec_star_only=np.ones_like(spec_star_only0)
     spec_final_norm = spec0/spec_star_only[np.newaxis,:]
 
+    '''
+    if ord ==3:
+        plt.figure()
[…]

### 2024-10-03 src/scripts/plot_spec_mean.py

@@ -1,0 +1,77 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+from astropy.io import fits
+from analyse_HARPS_spectra import get_mdl
+
+wave=fits.getdata(paths.data/"wave_corrected_spectra.fits")
+stellar=fits.getdata(paths.data/"corrected_spectra_stellar.fits")
+comet=fits.getdata(paths.data/"corrected_spectra_comet.fits")
+FEB_idx=fits.getdata(paths.data/'FEB_idx.fits').astype(bool)
+w_CN,s_CN,i_CN=get_mdl(fn='CN/CN_0300K.npy',N=1e14,FWHM_kernel=3e5/1.1e5)
+
+
+
+
+fig, ax = plt.subplots(1,1,figsize=(8,6))
+
+ax.set_xlabel('Wavelength [$\AA$] (Stellar restframe)',fontsize=16)
+ax.set_ylabel('Normalised spectrum [a.u.]',fontsize=16)
+
+
+ax.plot(wave[3,215:3860],np.nanmean(stellar[:,3,215:3860],axis=0),label='stacked spectrum')
+ax.plot(w_CN,s_CN*0.98,label='Model spectrum CN at 300K (N=10$^{14}$)')
+ax.set_xlim( (3855,3886) )
+ax.set_ylim( (0.95,1.02) )
+ax.legend()
+plt.draw()
+
+plt.tight_layout()
+
+fig.savefig(paths.figures/'spec_stack_CN_stellar.pdf')
+
+
+
+
+fig, ax = plt.subplots(1,1,figsize=(8,6))
+
+ax.set_xlabel('Wavelength [$\AA$] (Comet restframe)',fontsize=16)
+ax.set_ylabel('Normalised spectrum [a.u.]',fontsize=16)
+
+
+ax.plot(wave[3,215:3860],np.nanmean(comet[FEB_idx,3,215:3860],axis=0),label='stacked spectrum')
+ax.plot(w_CN,s_CN*0.98,label='Model spectrum CN at 300K (N=10$^{14}$)')
+ax.set_xlim( (3855,3886) )
+ax.set_ylim( (0.95,1.02) )
+ax.legend()
+plt.draw()
+
+plt.tight_layout()
+
+fig.savefig(paths.figures/'spec_stack_CN_comet.pdf')
+
+
+
+fig, ax = plt.subplots(1,1,figsize=(8,6))
+
[…]

### 2025-01-01 src/scripts/analyse_HARPS_spectra.py
modified with 8 order spline

@@ -652,7 +652,7 @@ if __name__ == "__main__":
    star_spec=np.median(spec,axis=0)
 
    for ord in range(8):
-       cor[:,ord,:]=remove_resid_blaze(pixels,spec,star_spec,ord,poly_order=4)
+       cor[:,ord,:]=remove_resid_blaze(pixels,spec,star_spec,ord,poly_order=8)
 
    # we split the spectra into 'comets' and 'no comets'
    FEB_idx,star_idx,FEB_wave=find_comets(wlen,cor,ord_FEB=ord_FEB,use_all=True)

### 2025-01-01 src/tex/ms.tex
updated figs

@@
   % {} leave it empty if necessary  
-   {Beta Pic has \ac{feb} which are seen as variable transient absorption features towards \bp{}.}
+   {The young (23 Myr) nearby (19.4 pc) star Beta Pictoris hosts an edge-on debris disk with two gas giant exoplanets in orbit around it, along with a large retinue of exocomets.
+   %
+   For many years, transient absorption features have been detected in the rotationally broadened stellar lines of the star's chromosphere.
+   %
+   These \ac{feb} or exocomets, are seen as variable transient absorption features towards \bp{}.
+}
   % aims heading (mandatory)
-   {To detect cyanogen (\ce{CN}) in the \ac{feb} spectrum, confirming that they are similar to comets in the Solar System.}
+   {In the Solar system, the molecule cynaogen (\ce{CN}) and its associated ionic species are one of the most detectable molecules in the coma and tails of comets.
+   %
+   We perform a search for cyanogen  in the \ac{feb} spectra of \bp{} to detect or put an upper limit on this molecule's presence in a young planetary system.}
   % methods heading (mandatory)
-   {We combine the \ac{harps} spectra from the past 20 years to make a high signal to noise ratio spectrum and look for the \ce{CN} band head.
-We also combine \ac{uves} data to confirm our non-detections/detections.}
+   {By splitting over twenty year's worth of \ac{harps} spectra into ones with strong \ac{feb} features, and others with little to no \ac{feb} absorption.
+We shift and stack the spectra of FEBs on the deepest part of the CaII make a high signal to noise ratio spectrum and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
+   }
   % results heading (mandatory)
-   {No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.}
+   {We do not detect CN in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.%No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.
+   %
+   }
   % conclusions heading (optional), leave it empty if necessary 
-   {\ac{feb} are not Solar System comets in composition.}
+   %{\ac{feb} are not Solar System comets in composition.}
 
@@
 %
-Comets deliver volatiles across menay different distances within the Solar system, from the outermost reaches of the Oort cloud in to the terrestrial planets.
+Comets deliver volatiles across many different distances within the Solar system, from the outermost reaches of the Oort cloud in to the terrestrial planets.
 %
@@
 %
-%The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
+The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
 %
@@
 %
-Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007}.
-
-On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines \hl{REFs}.
+Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and Na and K were detected for comet C/2011 L4 \citep{Fulle13}.
+
+On the other hand, \ion{Na}{i} D-line emission has been observed in many comets within $r \sim 1$ au of the Sun, where either the emission was much brighter than the foreground sky emission, or the comet was observed at high spectral resolution enabling separation from the telluric lines \citep{Cremonese02,Schmidt16}.
 %
@@
 
-These characteristics imply that \ion{Ca}{ii} and \ion{Fe}{i} are predominantly locked up within cometary dust gains, and only observed when a comet is close enough to the Sun to allow their sublimation.
+The detection of these atoms only at small heliocentric distances imply that \ion{Ca}{ii} and \ion{Fe}{i} are predominantly locked up within cometary dust gains, and only observed when a comet is close enough to the Sun to allow their sublimation.
 %
@@
 Some species, such as \ce{H2O+} and \ce{CO+} result from ionization of parent molecules (i.e.
-molecules released directly by the sublimation of nuclear ices), all other molecules observed are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma.
+molecules released directly by the sublimation of nuclear ices), all other molecules observed at optical wavelengths are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma.
 %
@@
 %
-The relative abundance in the coma of most comets of \ce{CN/OH}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae.
+The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae.
 %
@@
 %
-In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
+%In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
 
@@
 
-We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and \hl{March 2020}.
+We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and March 2020.
 %
@@
 %
-Similarly, the number of observations per epoch spans a wide range, between \hl{1 and 356} exposures, while the exposure times vary between \hl{12 and 900} seconds.
-This results in a SNR range per exposure between \hl{NNNN and MMMM}, and a nightly SNR between \hl{NNNN and MMMM}.
+Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
+This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labeling in the fits header -- corresponding to 3780\,$\AA$ and 4075\,$\AA$) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
 %
@@
 
-\subsection{UVES observations}
-
-To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
-%
-The details for these observations are given in \cite{vansluijs2019}, and summarised here.
-%
-These observations were all obtained using the same instrument setup.
-%
-We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
-%
-In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA{} to $\sim 5000$ \AA{} in the blue arm, and $\sim 5650$ \AA{} to $\sim 9560$ \AA{} in the red arm.
-%
-For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
-%
-For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).
-
-The data were reduced using the ESO \ac{uves} pipeline version \hl{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
+%\subsection{UVES observations}
+
+%To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
+%
+%The details for these observations are given in \cite{vansluijs2019}, and summarised here.
+%
+%These observations were all obtained using the same instrument setup.
+%
+%We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
+%
+%In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA{} to $\sim 5000$ \AA{} in the blue arm, and $\sim 5650$ \AA{} to $\sim 9560$ \AA{} in the red arm.
+%
+%For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
+%
+%For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).
+
+%The data were reduced using the ESO \ac{uves} pipeline version \hl{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
 The flat-field was applied on a pixel-by-pixel basis.
@@
 \subsection{Initial data processing}
-Starting from the 2d spectra, the data from both instruments was processed in similar ways.
-%
-Each order was treated separately, with the main focus on orders \hl{4 and 8} for HARPS and \hl{4, and 7} for UVES as those orders contain the main \ce{CN} bandhead as well as the \ion{Ca}{ii} H line, which are used to identify the exocomets.
+The analysis was started from the 2d extracted spectra (E2DS files).%, the data from both instruments was processed in similar ways.
+%
+Each order was treated separately, with the main focus on orders 3 and 7 % for HARPS and \hl{4, and 7} for UVES 
+as these orders contain the main \ce{CN} bandhead as well as the \ion{Ca}{ii} H line, which is used to identify the exocomets.
 %
 All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.
-For UVES, the \ce{Fe} \hl{NNNN angstrom} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
+%For UVES, the \ce{Fe} \hl{NNNN angstrom} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
 To measure these, a Gaussian was fit to the line, and the velocity offset from the rest frame position determined.
@@
 After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
-This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption etc.), as outlined below.
-Note that after this correction, the HARPS data still have the overall instrumental blaze-profile, while the 2d-spectra from UVES were already corrected for this.
+This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption, etc.), as outlined below.
+Note that after this correction, the %HARPS
+data still have the overall instrumental blaze-profile included.%, while the 2d-spectra from UVES were already corrected for this.
 
@@
 
-One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function (the night of \hl{DATE} for HARPS and \hl{DATE} for UVES).
-The individual spectra in this night were averaged together to further boost the signal-to-noise ratio.
+The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES). 
+The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
 Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
-This ratio spectrum was subsequently binned using a bin-width of \hl{101} pixels using a robust algorithm to remove outliers within each bin.
-This binned ratio was than fit using a \hl{second} order polynomial.
+This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin.
+This binned ratio was then fitted using a second order polynomial.
 The original spectrum was finally divided by this polynomial to correct for the changes.
 
-Note that for HARPS, the change of fiber in June 2015 (JD$\sim$2,457,180) resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.
+Note that the change of fiber for HARPS in June 2015 (JD$\sim$2,457,180) resulted in an overall change in the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in Sect.~\ref{sect:starcor}.
 
@@
 After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
-Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders \hl{NN and MM, and OO and PP} for HARPS and UVES respectively.
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,$\AA - $4075$\AA$).%\hl{, and OO and PP} for HARPS and UVES respectively.
 
@@
 
-For both HARPS and UVES we first perform a second iteration of blaze corrections using a  stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see \hl{Sect.}~\ref{sect:FEBident}.
-For HARPS this is done separately pre- and post-fiber change.
-The correction is done similar to Sect.~\ref{sect:blaze}, however for both UVES and HARPS a \hl{4th order} polynomial was used.
+%For both HARPS and UVES w
+We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}. %For HARPS
+This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, %for both UVES and HARPS
+an 8th order polynomial was used.
 
@@
 Subsequently, the overall spectrum of the star and (residual) blaze was determined by cubic interpolation across the binned points, and divided out of the spectrum for each night.
-As before, for HARPS this was done separately pre- and post-fiber change.
+As before, this was done separately pre- and post-fiber change.
 
@@
 %
-\hl{These coadded spectra for }\ac{harps} and \ac{uves} are shown in \hl{Figure}.
+These coadded spectra %for \ac{harps} and \ac{uves} 
+are shown in Figure~\ref{fig:spec_CN_stellar_frame}.
 %
@@
 
-Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the \hl{NN} epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
-
-\hl{TODO FIGURE: Just spectrum coadded} in stellar rest frame same for comet rest frame in the \ce{CN} band wavelength range, with the \ce{CN} band overplotted.
+Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the 36 epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
 
@@
 The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968.
-\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central \hl{NN} km\,s$^{-1}$.
+\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
 %
@@
 %
-For the comet sample we selected features deeper than \hl{60\% and 40\%} for HARPS and UVES, respectively, while spectra with features below 15\% for both HARPS and UVES were flagged as `low activity'.
-%
-An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in Figure \hl{XXXX}.
-%
-The distribution of feature location and depth is shown in \hl{Figure}.
-
-plotFEbs for the above first two figures!
-
-The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in \hl{Figure}.
+For the comet sample we selected features deeper than 60\% %\hl{and 40\%} for HARPS and UVES, respectively, 
+while spectra with features below 15\% %for both HARPS and UVES 
+were flagged as `low activity'.
+%
+%An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in Figure \hl{XXXX}.
+%
+The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}.
+
+The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in Figure~\ref{fig:spec_CN_comet_frame}.
 %
@@
 %
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_stellar.pdf}
+        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+The large signal around 3860\,$\AA$ is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        \label{fig:spec_CN_stellar_frame}
+        \script{plot_spec_mean.py}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
+        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+The large signal around 3860\,$\AA$ is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        \label{fig:spec_CN_comet_frame}
+        \script{plot_spec_mean.py}
+    \end{centering}
+\end{figure}
+
+\subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
+        \caption{Model absorption spectrum for \ce{CN} at 30\,K (blue line) and 2000\,K (orange line). The  column densities are $N=10^{12}$\,cm$^{-2}$ and $N=10^{13}$\,cm$^{-2}$, respectively. }
+        \label{fig:CN_theory}
+        \script{plot_two_CN_temps.py}
+    \end{centering}
+\end{figure}
 
@@
         \includegraphics[width=\columnwidth]{figures/CN_ACF.pdf}
-        \caption{\ce{CN} autocorrelation function for different temperatures.}
+        \caption{\ce{CN} autocorrelation function for different temperatures. The aliasing at $\sim50$\,km\,s$^{-1}$ is clearly visible}
         \label{fig:CN_ACF}
@@
 
-\subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}
-
-\begin{figure}
-    \begin{centering}
-        \includegraphics[width=\columnwidth]{figures/two_CN_temps.pdf}
-        \caption{Model absorption spectrum for \ce{CN} at two temperatures.}
-        \label{fig:CN_theory}
-        \script{plot_two_CN_temps.py}
-    \end{centering}
-\end{figure}
-
 To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
@@
 
-Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf} do not show any clear signals, and we therefore proceed to estimate our detection limits.
+Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean} do not show any clear signals, and we therefore proceed to estimate our detection limits.
 
@@
 %
-To avoid the aliasing peaks of the \ce{CN} band (see Figure~\ref{fig:CN_theory}), we only fit the central $\pm$35 \kms{} of the CCF.
+To avoid the aliasing peaks of the \ce{CN} band (see Figure~\ref{fig:CN_ACF}), we only fit the central $\pm$35 \kms{} of the CCF.
 %
@@
 %\subsubsection{We need a bigger comet}
-There are several ways we can get larger \ce{CN} rates.
+There are several ways exocomets at \bp may exhibit larger \ce{CN} production rates.
 %
@@
 Part of this work was supported by the German \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project number Ts~17/2--1.
+
+AF acknowledges acknowledges support from STFC award ST/T00021X/1.
 %
@@
 %      
-An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/}
+An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/BetaPicCN}
 

### 2025-01-17 src/tex/ms.tex
almost there

@@
    {By splitting over twenty year's worth of \ac{harps} spectra into ones with strong \ac{feb} features, and others with little to no \ac{feb} absorption.
-We shift and stack the spectra of FEBs on the deepest part of the CaII make a high signal to noise ratio spectrum and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
+We shift and stack the spectra of FEBs on the deepest part of the Calcium feature make a high signal to noise ratio spectrum and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
    }
   % results heading (mandatory)
-   {We do not detect CN in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.%No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.
+   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.%No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.
    %
@@
 
-The formation and evolution of planets and their attendant moons is thought to occur in the first few ten million years of the stellar system \hl{REF}.
-%
-Comets deliver volatiles across many different distances within the Solar system, from the outermost reaches of the Oort cloud in to the terrestrial planets.
+The formation and evolution of planets and their attendant moons is thought to occur in the first several million years of a planetary system.
+%
+Within our Solar system, comets deliver volatiles from the outermost reaches of the Oort cloud \citep{Obrien2018}, past the gas giants and terrestrial planets, even as close as a few solar radii.
 %
@@
 
-One of the closest young systems is Beta Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
-
-Beta Pictoris is a young, early type star whose stellar chromosphreic lines show rotational broadening of 200 km/s \hl{REF}.
-%
-The Ca H and K lines show deep absorption to 0.1 of the continuum level.
-%
-A consistent and stable narrow absorption feature with a FWHM of a few km/s is explained by the presence of the circumstellar material.
-%
-There exist transient, irregular shaped absorption features in the spectra of the star.
-%
-These appear and disappear on hour long timescales, and show a different range of morphologies, predominantly seen at bluer wavelengths. \hl{[REF]}.
-%
-Intensive spectroscopic monitoring over several hours show changes of radial velocity of these components consistent with elliptical orbits.
-%
-The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component \hl{[REF REF]}.
-
-From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \hl{REF} and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19}.
-%
-Observations of Beta Pictoris in subsequent TESS sector revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
-
-%Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).
+One of the closest young planetary systems is Beta Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
+%
+Beta Pictoris is a young \citep[$\sim 25$ Myr; see ][ for discussions]{Lee24}, nearby \citep[$19.63\pm 0.06$ pc, ][]{Lindegren21} and early type star \citep[A6V; ][]{Gray06} which hosts an edge-on debris disk and at least two exoplanets, making it one of the most intensely studied young planetary systems.
+%
+The star is a rapid rotator \citep[$124\pm 3$\,\kms{}; ][]{Koen03} seen close to equator on, resulting in rotational broadening of the chromospheric lines.
+%
+Amongst these, the Ca H and K lines show deep absorption down to 0.1 of the continuum level.
+%
+Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few km/s, attributed to the presence of the circumstellar material.
+
+Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to Falling Evaporating Bodies moving towards the star \citep{Ferlet87}.
+%
+These features appear and disappear on the timescale of days, with some features lasting up to tens of days.
+%
+These features appear with red-shifted velocities from hundreds of kilometers per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blue-shifted side of the circumstellar line.
+%
+The widths of the lines range from a few up to tens of kilometers per second.
+ \hl{[REF]}.
+
+Intensive spectroscopic monitoring over several hours show changes of radial velocity of these components consistent with Keplerian elliptical orbits \citep{Kennedy18}.
+%
+The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component.
+
+From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19} and have been searched for in other stars with automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24}.
+%
+Observations of Beta Pictoris in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
 
 To the contrary of what is observed in the case of \ac{feb}, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
-
+%
 Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
@@
 %
-Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and Na and K were detected for comet C/2011 L4 \citep{Fulle13}.
+Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and Na and K were detected for comet C/2011 L4 \citep{Fulle13} at 0.46 au.
 
@@
 A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
+Recently, \cite{Hui2023} also demonstarted thet the activity of near-Earth asteroid Phaeton, with a perihelion of only 0.14 au, is associated with emission of sodium.
 
@@
 %
-Strong \ce{CO+} emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) \hl{REFS}).
-%
-However this is normally significantly weaker than the observed \ce{CN} emission, with only \hl{number of comets} comets.
+Strong \ce{CO+} emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) \citep{Biver2018}).
+%
+However this is normally significantly weaker than the observed \ce{CN} emission, with only less than 20 comets.
 
@@
 \subsection{Initial data processing}
-The analysis was started from the 2d extracted spectra (E2DS files).%, the data from both instruments was processed in similar ways.
+The analysis was started from the 2d extracted spectra (E2DS files). %, the data from both instruments was processed in similar ways.
 %
@@
 %For both HARPS and UVES w
-We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}. %For HARPS
+We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}). %For HARPS
 This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, %for both UVES and HARPS
@@
 %
-Cross-sections for \ce{CN} were obtained from ExoMol \hl{REFERENCES HERE} and the cross-sections were calculated using \hl{NEED SOME DETAILS...}. 
+Cross-sections for \ce{CN} were obtained from ExoMol \hl{REFERENCES HERE} \citep{Tennyson16,Brooke14,Bernath20,Syme20} and the cross-sections were calculated using \hl{NEED SOME DETAILS...}. 
 %
@@
 %
-We injected models for different temperatures, column densities and velocity broadening into the nightly stacked spectra (Sect.~\ref{sect:comb}, and then processed them in the same way as the original data (i.e., correct for residual blaze variations, removal of the stellar envelope and cross-correlation).
+We injected models for different temperatures, column densities and velocity broadening into the nightly stacked spectra (Sect.~\ref{sect:comb}), and then processed them in the same way as the original data (i.e., correct for residual blaze variations, removal of the stellar envelope and cross-correlation).
 %
@@
 %
-The Haser model is somewhat simplistic but it represents the data well.
+The Haser model is somewhat simplistic but it represents the data well for solar system comets observed at typical distances from the SUn (1-3 au).
 
@@
 
-The outflow velocity of the parent of \ce{HCN} will depend on the nuclear surface temperature as $\sqrt{T}$.
+The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature as $\sqrt{T}$.
 %

### 2025-01-24 src/tex/ms.tex
added EdM acks

@@
 \newcommand{\kms}{km s$^{-1}$}
-\newcommand{\bpb}{Beta Pictoris b}
-\newcommand{\bp}{Beta Pictoris}
+\newcommand{\bpb}{$\beta$\,Pic\,b}
+\newcommand{\bp}{$\beta$\,Pic}
 
@@
 
-   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}}
+   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards $\beta$~Pictoris}
 
@@
   % {} leave it empty if necessary  
-   {The young (23 Myr) nearby (19.4 pc) star Beta Pictoris hosts an edge-on debris disk with two gas giant exoplanets in orbit around it, along with a large retinue of exocomets.
-   %
-   For many years, transient absorption features have been detected in the rotationally broadened stellar lines of the star's chromosphere.
-   %
-   These \ac{feb} or exocomets, are seen as variable transient absorption features towards \bp{}.
+   {The young (23 Myr) nearby (19.4 pc) star $\beta$~Pictoris hosts an edge-on debris disk with two gas giant exoplanets in orbit around it.
+   %
+   Many transient absorption features have been detected in the rotationally broadened stellar lines of the star's chromosphere, and these are thought to be the coma of infalling exocomets crossing the line of sight towards Earth.
 }
@@
    %
-   We perform a search for cyanogen  in the \ac{feb} spectra of \bp{} to detect or put an upper limit on this molecule's presence in a young planetary system.}
+   We perform a search for cyanogen in the spectra of \bp{} to detect or put an upper limit on this molecule's presence in a young, highly active planetary system.}
   % methods heading (mandatory)
-   {By splitting over twenty year's worth of \ac{harps} spectra into ones with strong \ac{feb} features, and others with little to no \ac{feb} absorption.
-We shift and stack the spectra of FEBs on the deepest part of the Calcium feature make a high signal to noise ratio spectrum and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
+   {We divide twenty year's worth of \ac{harps} spectra into those with strong exocomet absorption features, and those with only stellar lines.
+   %
+   The high signal to noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal to noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
    }
@@
 
-One of the closest young planetary systems is Beta Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
-%
-Beta Pictoris is a young \citep[$\sim 25$ Myr; see ][ for discussions]{Lee24}, nearby \citep[$19.63\pm 0.06$ pc, ][]{Lindegren21} and early type star \citep[A6V; ][]{Gray06} which hosts an edge-on debris disk and at least two exoplanets, making it one of the most intensely studied young planetary systems.
+One of the closest young planetary systems is $\beta$~Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
+%
+\bp{} is a young \citep[$\sim 25$ Myr; see ][ for discussions]{Lee24}, nearby \citep[$19.63\pm 0.06$ pc, ][]{Lindegren21} and early type star \citep[A6V; ][]{Gray06} which hosts an edge-on debris disk and at least two exoplanets, making it one of the most intensely studied young planetary systems.
 %
@@
 %
-Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few km/s, attributed to the presence of the circumstellar material.
-
-Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to Falling Evaporating Bodies moving towards the star \citep{Ferlet87}.
-%
-These features appear and disappear on the timescale of days, with some features lasting up to tens of days.
-%
-These features appear with red-shifted velocities from hundreds of kilometers per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blue-shifted side of the circumstellar line.
-%
-The widths of the lines range from a few up to tens of kilometers per second.
- \hl{[REF]}.
-
-Intensive spectroscopic monitoring over several hours show changes of radial velocity of these components consistent with Keplerian elliptical orbits \citep{Kennedy18}.
-%
-The absorption is hypothesised to be due to the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing the Calcium atoms which are then seen as an additional absorption component.
-
-From the multiple detections of exocomets in spectroscopy towards Beta Pictoris, the broadband detection of exocomet tails transiting a star were seen initially detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and subsequently detected in TESS data towards Beta Pictoris \citep{Zieba19} and have been searched for in other stars with automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24}.
-%
-Observations of Beta Pictoris in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
+Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few km/s, attributed to the presence of the circumstellar material \citep{Hobbs85,VidalMadjar86}.
+
+Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to \ac{feb} moving towards the star \citep{Ferlet87}.
+%
+These features appear and disappear on the timescale of hours to days, with some features lasting up to tens of days and have red-shifted velocities from eighty kilometers per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blueward side \citep{LagrangeHenri92} with widths from a few up to tens of kilometers per second.
+%
+The absorption can be described by the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing Calcium ions which are then seen as an additional absorption component \citep{Beust91}.
+%
+Intensive spectroscopic monitoring over several hours show both multiple components transiting the disk of the star \citep{Beust96} and changes of radial velocity of several components are consistent with Keplerian elliptical orbits \citep{Kennedy18} implying at least two \citep{Kiefer14,Pollard24} or more \citep{Heller24} distinct kinematic families of FEBs.
+%
+At least one event is derived with the orbit parallel to the rotational axis of the star \citep{Tobin19}.
+%
+Given the kinematic and spectroscopic evidence, these have subsequently been labelled as ``exocomets''.
+
+From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted \citep{LecavelierdesEtangs97} and subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
+%
+Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
+%
+Automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24} for additional exocomet systems have been met with limited success.
 
@@
 %
-Strong \ce{CO+} emission bands have also been observed in a number of comets (the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$) \citep{Biver2018}).
+Strong \ce{CO+} emission bands have also been observed in a number of comets \citep[the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$; ][]{Biver2018}.
 %
@@
 %
-Cross-sections for \ce{CN} were obtained from ExoMol \hl{REFERENCES HERE} \citep{Tennyson16,Brooke14,Bernath20,Syme20} and the cross-sections were calculated using \hl{NEED SOME DETAILS...}. 
+Cross-sections for \ce{CN} were obtained from ExoMol\footnote{\url{https://www.exomol.com}} \citep{Tennyson12,Tennyson16,Brooke14} with molecular energy levels assumed to be in thermal equilibrium, i.e.\ Boltzmann distributed.
 %
@@
 %\subsubsection{We need a bigger comet}
-There are several ways exocomets at \bp  may exhibit larger \ce{CN} production rates.
+There are several ways exocomets at \bp{} may exhibit larger \ce{CN} production rates.
 %
@@
 
-We have combined over 1000 spectra of Beta Pictoris over a 20 year period, identified two groups, one with deep exocomet signals, and another to act as a stellar reference.
-%
-We produce a normalised spectrum towards Beta Pictoris with the stellar spectral features removed, and then aligned the spectra to the exocomet rest frames and perform a search for \ce{CN} using cross correlation.
+We have combined over 1000 spectra of \bp{} over a 20 year period, identified two groups, one with deep exocomet signals, and another to act as a stellar reference.
+%
+We produce a normalised spectrum towards \bp{} with the stellar spectral features removed, and then aligned the spectra to the exocomet rest frames and perform a search for \ce{CN} using cross correlation.
 
@@
 %
-This presents an excellent opportunity for coordinated spectroscopic campaigns where the exocomet population of Beta Pictoris can be characterised, with \ce{CN} and ideally other molecules known from Solar sysgem comets to be identified in another stellar system.
+This presents an excellent opportunity for coordinated spectroscopic campaigns where the exocomet population of \bp{} can be characterised, with \ce{CN} and ideally other molecules known from Solar system comets to be identified in another stellar system.
 
@@
 
-AF acknowledges acknowledges support from STFC award ST/T00021X/1.
+AF acknowledges support from STFC award ST/T00021X/1. EdM acknowledges support from STFC award ST/X00094X/1.
 %

### 2025-02-06 src/tex/ms.tex
finishing

@@
 \bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
+
+\newcommand{\angstrom}{\textup{\AA}}
 
@@
 \hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}
+
+%\newcommand\pdfmath[1]{\texorpdfstring{$#1$}{#1}}
 
@@
 \usepackage{showyourwork}
-
-% text highlighting
-\usepackage{soul}
-\sethlcolor{yellow}
 
@@
           \and
-          A. Fitzsimmons \inst{1}
+          A. Fitzsimmons \inst{2}
           }
@@
   % results heading (mandatory)
-   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.%No \ce{CN} is seen to a level of XXX ppt, indicating that there is less \ce{CN} in these \ac{feb} than Solar system comets.
-   %
+   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.
    }
@@
 %
-%For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comet approached the Sun.
-%
-%At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum, but at 0.15 au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ce{[\ion{O}{i}], \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
-%%\ion{Ca}{ii} and \ion{Fe}{i} have only been spectroscopically observed via emission lines in the sun-grazing comet C/1965~S1 Ikeya-Seki.
-%
 For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
@@
 A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
-Recently, \cite{Hui2023} also demonstarted thet the activity of near-Earth asteroid Phaeton, with a perihelion of only 0.14 au, is associated with emission of sodium.
+Recently, \cite{Hui2023} also demonstrated thet the activity of near-Earth asteroid Phaeton, with a perihelion of only 0.14 au, is associated with emission of sodium.
 
@@
 %
-It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun \citep[e.g.
-][]{Fitzsimmons1996}.
+It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the comae of comets observed at relatively large distances from the Sun \citep[e.g.
+][]{Bus1991,Fitzsimmons1996}.
 %
-The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae.
+The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas coma.
 %
@@
 However this is normally significantly weaker than the observed \ce{CN} emission, with only less than 20 comets.
-
+%
 Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the \ac{feb} around \bp{}.
@@
 For the study in this paper, we use all the publicly available data from the \ac{harps} and the ESO 3.6m telescope in Chile.
-%
-%In addition, we complement this with observations with the \ac{uves} at the Very Large Telescope in Chile.
 
@@
 Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
-This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labeling in the fits header -- corresponding to 3780\,$\AA$ and 4075\,$\AA$) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
+%
+This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\,\AA and 4075\,\AA) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
 %
@@
 
-% \hl{Q: Do we want to put an observing log in the appendix?}
-% \hl{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
-
-%\subsection{UVES observations}
-
-%To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
+\subsection{Initial data processing}
+The analysis was started from the 2d extracted spectra (E2DS files).
 %
-%The details for these observations are given in \cite{vansluijs2019}, and summarised here.
-%
-%These observations were all obtained using the same instrument setup.
-%
-%We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
-%
-%In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA{} to $\sim 5000$ \AA{} in the blue arm, and $\sim 5650$ \AA{} to $\sim 9560$ \AA{} in the red arm.
-%
-%For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
-%
-%For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).
-
-%The data were reduced using the ESO \ac{uves} pipeline version \hl{6.1.6} through ESO Reflex tool in order to provide as homogeneous a dataset as possible.
-The flat-field was applied on a pixel-by-pixel basis.
-\hl{The pipeline was set to output the intermediate products and the blaze-corrected spectra before merging were used for our analysis, as the order-merging could introduce systematics in the overlap region.
-Optimal extraction was performed, using an empirical profile}
-
-\subsection{Initial data processing}
-The analysis was started from the 2d extracted spectra (E2DS files). %, the data from both instruments was processed in similar ways.
-%
-Each order was treated separately, with the main focus on orders 3 and 7 % for HARPS and \hl{4, and 7} for UVES 
-as these orders contain the main \ce{CN} bandhead as well as the \ion{Ca}{ii} H line, which is used to identify the exocomets.
+Each order was treated separately, with the main focus on orders 3 and 7 as these orders contain the main \ce{CN} bandhead as well as the \ion{Ca}{ii} H line, which is used to identify the exocomets.
 %
@@
 \subsection{Combining the spectra and flattening them}\label{sect:comb}
+
 After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
-Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,$\AA - $4075$\AA$).%\hl{, and OO and PP} for HARPS and UVES respectively.
-
-%For the spectra within a given night:
 %
-%\begin{itemize}
-%\item We median combine all the nights together.%
-%
-%\item Bin the spectrum and clip it, interpolate using a cubic spline.
-%
-%\item Divide this interpolated cubic spline into each of the nightly spectra.
-%
-%\end{itemize}
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,\AA{} - 4075\AA).%\hl{, and OO and PP} for HARPS and UVES respectively.
 
@@
 After this post-processing the overall (residual) blaze profile and stellar spectrum still need to be removed.
+%
 Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in e.g., the \ce{Fe} and \ion{Ca}{II} lines).
+%
 This is done by combining the nightly spectra without significant cometary activity (see Sect.~\ref{sect:FEBid}) and binning this stacked spectrum in wavelength in bins of 21 pixels.
+%
 Before binning, the spectrum in each bin was MAD (median absolute deviation) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
+%
 The clipped average of the fluxes within each bin was used.
+%
 Subsequently, the overall spectrum of the star and (residual) blaze was determined by cubic interpolation across the binned points, and divided out of the spectrum for each night.
+%
 As before, this was done separately pre- and post-fiber change.
-
-%Subsequently, we applied a correction for variations in the instrumental blaze by selecting a reference spectrum and dividing all the spectra by this reference.
-The ratio was then binned, removing outliers, and a polynomial was fit to the data.
-%
-%For \ac{uves} we used a Nth degree polynomial, while for \ac{harps} we used a 2nd degree polynomial.
-%
-%This polynomial was then divided from the spectrum under consideration.
-We note that the blaze correction will also remove non-instrumental effects, including variations in atmospheric transmission and seeing.
-
-%The blaze-corrected spectra taken within a night were averaged together [Should we use a weighted average?].
-%
-%We note that for \ac{harps}, the 2d-unmerged spectra still contain the overal instrumental blaze-profile, which is (partially) corrected for by using a dedicated blaze-frame obtained from the archive, which removes most, but not all, of this profile.
 
@@
 No obvious feature from the \ce{CN} band jumps out, and we need to combine the signal from the lines within the \ce{CN} band to improve the detection limits.
-
+%
 Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the 36 epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.
@@
 \subsection{Identifying exocomets from \ion{Ca}{ii} H line}\label{sect:FEBid}
-The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968.
-\AA$) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
+The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
 %
@@
 %
-%An example of the \ion{Ca}{ii} H line for a night with a strong comet and for a night with a weak comet are shown in Figure \hl{XXXX}.
-%
 The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}.
@@
 As with the circumstellar \ce{CN}, there are no obvious lines from \ce{CN} visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any \ce{CN} present.
-%
-%The spectra with only weak exocometary features were co-averaged in the stellar rest frame in order to create a stellar master spectrum.
-This master-spectrum was divided out of all the remaining spectra in order to create relative spectra.
-%
-%The relative velocities of the exocomets were determined by ......., and the spectra were shifted to the rest-frames of these comments, before being combined.
-%
-%The combined exocomet aligned spectra for both the \ce{Ca} H\&K lines and \ce{CN} band are shown in Fig.~\ref{fig:coadd_exocomets}. As can be seen no signal is visibly present.
-%
 
@@
         \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
-The large signal around 3860\,$\AA$ is due to the residual from a circumstellar \ion{Fe}{I} line.}
+The large signal around 3860\,\AA is due to the residual from a circumstellar \ion{Fe}{I} line.}
         \label{fig:spec_CN_stellar_frame}
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
-        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
-The large signal around 3860\,$\AA$ is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        \caption{Plot of the stacked spectrum in the stellar rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+The large signal around 3860\,\AA is due to the residual from a circumstellar \ion{Fe}{I} line.}
         \label{fig:spec_CN_comet_frame}
@@
 %\subsection{Summary of \ce{CN} in comets}
-
-\ce{CN} is one of the brightest optically active species in cometary comae.
+%\ce{CN} is one of the brightest optically active species in cometary comae.
 %
-It is a minor component of the gas coma, with a production rate by number $\sim 1/500$th that of water.
-
-Most studies of Solar system comets simply observe the \ce{CN} molecules via optical fluorescence.
-%
+%It is a minor component of the gas coma, with a production rate by number $\sim 1/500$th that of water. 
+As discussed above in the introduction, most studies of Solar system comets observe the \ce{CN} molecules via optical fluorescence.
 From measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
-%
 This means a flux from part of the coma can immediately be converted to a column density using a photon scattering efficiency for the molecular band.
@@
 \ce{CN} in solar system comets comes from two sources.
-%
 Sublimation of nucleus near-surface ices releases \ce{HCN}, which then photo-dissociates into \ce{CN}.
-%
 This in turn eventually photo-dissociates into the component atoms.
@@
 
-Since Halley in 1986, it has also been known that dust grains ejected from the nucleus also directly release \ce{CN} into the coma.
-%
-However, \ce{CN} production in comets is usually dominated by nuclear ice sublimation.
+Since observations of Comet Halley \citep{AHearn1986}, it has also been known that dust grains ejected from the nucleus also directly release \ce{CN} into the coma.
+However, \ce{CN} production in comets is usually dominated by nuclear ice sublimation \citep{Fray2005}.
+The resulting \ce{CN} coma will have a true space density and apparent column density distribution centrally peaked at the comet nucleus in this case.
 
-The resulting \ce{CN} coma will have a true space density and apparent column density distribution centrally peaked at the comet nucleus.
-%
-For Solar system comets, column densities are often converted to an overall production rate $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model.
-%
-For this model there are only 3 parameters; the effective destruction scale length $l_p$ of the parents of \ce{CN} (\ce{HCN}+dust), the photodissociation scale length $l_{\ce{CN}}$ of \ce{CN}, and the gas outflow velocity $v$.
-%
-The Haser model is somewhat simplistic but it represents the data well for solar system comets observed at typical distances from the SUn (1-3 au).
+For Solar system comets, measured \ce{CN} column densities are often converted to an overall production rate by the comet of $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model \citep{Haser2020}
+This model gives the on-sky column density as a function of projected radial distance form the nucleus using only 3 parameters; the effective destruction scale length $l_p$ of the parents of \ce{CN} (\ce{HCN}+dust), the photodissociation scale length $l_{\ce{CN}}$ of \ce{CN}, and the gas outflow velocity $v$.
+The Haser model is somewhat simplistic but it represents the data well for solar system comets observed at typical distances from the Sun (1--3 au).
 
@@
 
-We take the observed activity of 1P/Halley in 1985/86 as an example for our estimates.
+We take the observed activity of 1P / Halley in 1985 / 1986 as a reference point for our estimates.
 %
-Although most comets we observe are far less active than Halley, there are quite a few comets with activity similar to it.
+Although most Solar system comets are observed to be are far less active than Halley, some Long-Period comets show activity in excess of Halley.
+Given that we will be dominated by the most active comets at \bp{}, this seems reasonable as something that can be later scaled to the most active comets such as Hale-Bopp \citep{Schleicher2024}.
 %
-Given that we will be dominated by the most active comets at \bp{}, this seems reasonable as something that can be later scaled to the brightest comets such as Hale-Bopp.
-%
-When Halley was at $\sim 1$ au from the Sun, it was measured to have $Q_{\ce{CN}}\simeq 10^{27}$ molecules/sec using Haser models.
+When Halley was at $\sim 1$ au from the Sun, it was measured to have $Q_{\ce{CN}}\simeq 10^{27}$ molecules/sec using Haser models \citep{AHearn1995}.
 %
@@
 
-For solar system comets, the normal Haser scale lengths used \citep{Cochran86,AHearn1995} are:
+For solar system comets, the normal Haser scale lengths used are \citep{Cochran86,AHearn1995} :
 
 $$lp=1.7\times10^4r_h^2\:{\rm km}$$
-
 $$l_{\ce{CN}}=2-3\times10^5r_h^2\:{\rm km}$$
@@
 %
-These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ km/sec, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of 1 \kms{}.
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ km/sec, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq1$ \kms{} \citep{Combi1980}.
 
@@
 Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by Ly-$\alpha$ line flux.
-From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A7V stars is a factor of $\sim10$ higher than for G2V stars.
+From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A6V/A7V stars is a factor of $\sim10$ higher than for G2V stars.
 %
-Hence the photodissociation lifetime of \ce{CN} will be 10 times smaller i.e. $\sim 2\times10^4$ sec at 1 au.
+Hence the photodissociation lifetime of \ce{CN}  at 1 au from \bp{} of an `exoHalley' will be approximately 10 times smaller i.e. $\sim 2\times10^4$ sec at 1 au.
 
-In steady-state sublimation, the sublimation rate is proportional to the photon flux at the comet.
-For \bp{} $L=8.7L_\odot$, hence assuming dust desorption also scales this way, Halley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 8\times10^{27}$ molecules/sec.
+In steady-state sublimation, the sublimation rate is proportional to the photon flux at the comet. For \bp{} $L=8.7L_\odot$, so assuming 
+all \ce{CN} production scales with stellar luminosity, exoHalley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 9\times10^{27}$ molecules/sec.
 %
-The total number of \ce{CN} molecules in the coma at 1~au would therefore be
+The total number of \ce{CN} molecules in the coma at 1~au at any given time would therefore be
 
 $$N_{\ce{CN}}=Q_{\ce{CN}} \tau_{\ce{CN}}$$
-
-$$N_{\ce{CN}}\sim 8\times10^{27} \cdot  2\times10^4 \sim 2\times10^{32}\:{\rm molecules}$$
+$$N_{\ce{CN}}\sim 9\times10^{27} \cdot  2\times10^4 \sim 2\times10^{32}\:{\rm molecules}$$
 
 %\subsubsection{\ce{CN} Cross-section}
-
-The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature as $\sqrt{T}$.
+The effective cross section of the coma will depend on how much is projected against the disk of \bp{}. The radius of the \ce{CN} coma will be given by
+$$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$.
+The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature, which will increase as a comet moves towards its parent star.
+\citet{Biver2002} found a nuclear gas outflow velocity $v\simeq1.0  r_h^{-0.4}$ \kms{} from sub-mm measurements of Comet Hale-Bopp, close to the canonical relationship of $r_h^{-0.5}$.
+\citet{Harris2002} notes lower activity similar to Halley results in smaller outflow velocities.
+%Dust grains will also be travelling faster due to the larger gas pressure accelerating them.
+The excess photodissociation velocity of \ce{CN} will not change.
+Therefore gas outflow speeds are expected to be $\sim 1-2$ \kms{} at 1 AU, and the \ce{CN} coma radius will be
 %
-Modelling shows that ice sublimation acts approximately as a thermostat for the nucleus surface temperature, implying that the \ce{HCN} will only slowly increase with decreasing temperature.
-%
-\citet{Biver99} found $v\propto r_h^{-0.4}$ from sub-mm measurements of Hale-Bopp, close to the expected relationship of $r_h^{-0.5}$.
-%
-Dust grains will also be travelling faster due to the larger gas pressure accelerating them.
-%
-The photodissociation velocity of \ce{CN} will obviously not change.
-
-Here we will make the simplifying assumption that gas outflow speeds are dominated by the photodissociation of \ce{CN} at $\sim 1$ \kms{}.
-%
-The size of of the \ce{CN} coma will be given by
-
-$$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$
-$$r\sim 1.0 \times 2\times 10^{4}\sim 2\times 10^{4}\:{\rm km}$$
-
-This is much smaller than a stellar radius, so we can assume all of the coma is projected into the stellar disk as seen from Earth.
+$$r\sim (1-2) \times 2\times 10^{4} \leq 4\times 10^{4}\:{\rm km}$$
+This is much smaller than a stellar radius, so we can assume for an exoHalley that all of the coma is projected into the stellar disk as seen from Earth.
 
@@
 $$n\sim\frac{2\times10^{32}}{\pi\cdot 1.7\times10^{22}}\sim 3\times10^{9}\:{\rm cm^{-2}}$$
-
-Hence comet Halley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{9}-10^{10}$ cm$^{-2}$.
+Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{9}-10^{10}$ cm$^{-2}$.
 %
-This is about a factor of 100 smaller than our calculated upper limits.
+This is about a factor of 100 smaller than our measured upper limits above.
 
@@
 %
-While Halley's nucleus is much bigger than most other comets, there have been larger.
+ Comet Halley's nucleus has an effective radius of $5.5$ km \citep{Keller1987}, whereas 
+Comet Hale-Bopp was one of the most intrinsically active comets on record with an extremely large nucleus of radius $\sim 14-21$ km \citep{Weaver1997}.
 %
-Hale-Bopp in 1997 was one of the most intrinsically active comets on record.
+However most of the apparent brightness was due to dust emission, and its only had $Q_{\ce{CN}}\simeq 3\times10^{27}$ molecules/sec \citep{Schleicher2024}.
 %
-This was because of its extremely large nucleus of radius $\sim 30$ km.
-%
-However most of the apparent brightness was due to dust emission, and its only had $Q_{\ce{CN}}\simeq 3\times10^{27}$ molecules/sec.
-%
-Given this, it is likely that comets may exist with gas production rates a factor of 10 higher.
-
-In this case, with all things considered we might anticipate the most active comets in the Solar system to have $Q_{\ce{CN}}\sim \times10^{28}$ molecules/sec, implying a commensurate increase of a factor 10 in $n_{\ce{CN}}$ at \bp{}.
+In this case, we might anticipate the most active comets in the Solar system to have $Q_{\ce{CN}}\sim 10^{28}$ molecules/sec, implying a commensurate increase of a factor 10 in column density $n$ over an exoHalley at \bp{}.
 
@@
 %
-Halley itself only has $\sim 20$\% of the sunlit surface active.
+Halley itself only has $\sim20$\% of the sunlit surface active \citep{Keller1987}.
 %
-Yet we know of some Jupiter-family comets that have $\sim 100$\% fractional active surface, and it is believed that many long-period comets also exhibit high activity.
-%
-Assuming this for \bp{} would increase $Q_{\ce{CN}}$ and $n$ by a factor $\sim 5$.
+Yet some comets are known as hyperactive, as the measured gas productions rates would require $\geq 100$\% of the nucleus surface to be active \citep{Sunshine2021}.
+This is believed to be due to the release of ice-rich dust grains from the nucleus, which sublimate and act as a secondary source of gas.
+Assuming this is possible for exocomets at \bp{} would increase $N_{\ce{CN}}$ and $n$ by a factor $\sim 5$.
 
@@
 
-The closer a comet is to its star, the greater the heating and corresponding production rate as $Q_{\ce{CN}}\propto r_h^{-2}$.
+The closer a comet to its parent star, the greater the heating and corresponding production rate. When insolation completely controls the nuclear surface energy balance we expect
+$Q_{\ce{CN}}\propto r_h^{-2}$.
 %
-Studies of Halley and Hale-Bopp showed power laws close to this, but the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
-
+Studies of Halley and Hale-Bopp showed power laws close to this {\it i.e.} \cite{Biver2002}. But the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
 $$N_{\ce{CN}}=\frac{Q_{\ce{CN}}(1~\rm{au})}{r_h^2}\cdot  \tau_{\ce{CN}} (1~\rm{au}) r_h^2 =\:{\rm constant} $$
-
-Hence the total amount of \ce{CN} should be approximately independent of stellar distance.
+Hence the total amount of \ce{CN} in the coma should be approximately independent of stellar distance, and the total cross-section would not change.
 
 %\subsubsection{Stay up all night to get lucky}
-Comets have impulsive outbursts, where the amount of material ejected into the coma increases significantly over a few hours or less.
+Finally, comets have impulsive outbursts, where the amount of material ejected into the coma increases significantly over a few hours or less.
 %
-This varies from comet to comet; many do not appear to outburst, some have 1--few outbursts per orbit, some have many more.
+%This varies from comet to comet; many do not appear to outburst, some have 1 or a few outbursts per orbit.
 %
-The general causes are unclear, but there is evidence for several physical mechanisms that cause them.
-
+The general causes are unclear, but there is evidence for several physical mechanisms that cause them 
+\citep{Kelley2021,Muller2024}.
 ``Normal'' outbursts generally result in a brightness increases of 1--5 magnitudes, with smaller outbursts being more common.
 %
-As the apparent brightness is directly proportional to the amount of material (gas+dust) in the coma, if we assume the gas follows the dust, this implies short term increases in $N_{\ce{CN}}$ and $n$ of factors $\sim 2-100$.
+As the apparent brightness is directly proportional to the amount of material (gas+dust) in the coma, this implies short term increases in $N_{\ce{CN}}$ and $n$ of factors $\sim 2-100$.
 
-Large outbursts are often due to partial or total disruption of a comet, which often (but not always) occurs when a comet is closer to the Sun.
-%
+Large outbursts are often due to partial or total disruption of a comet and can occur when a comet is closer to the Sun.
 Hence there could be a correlation with faster moving \bp{} exocomets nearer their periastra producing greater measurable column densities of \ce{CN}.
 
-A reasonably active comet would give an effective \ce{CN} column density of $\sim 10^{9}-10^{10}$ cm$^{-2}$.
-%
-A larger or more active nucleus could increase that by a factor 10.
-%
-Even larger increases are possible with an outburst or comet disruption, but the limit is likely to be  $n\sim10^{12}$ cm$^{-2}$.
+In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} could exceed $n\sim10^9-10^{10}$ cm$^{-2}$. 
+A larger and/or hyperactive nucleus could increase $n$ by a factor 10.
+Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{12}$ cm$^{-2}$.
 
@@
 %
-This is a factor of 10 to 100 too high to detect a single Hale-Bopp equivalent comet with a \ce{CN} halo.
+This is a factor of 10 to 100 too high to detect a single Hale-Bopp equivalent comet with a \ce{CN} coma.
 %
@@
 
-%-------------------------------------------------------------------
-
 \bibliographystyle{aa}
@@
 
-%\begin{thebibliography}{}
-
-%  \bibitem[1966]{baker} Baker, N. 1966,
-%      in Stellar Evolution,
-%      ed.\ R. F. Stein,\& A. G. W. Cameron
-%      (Plenum, New York) 333
-
-%   \bibitem[1988]{balluch} Balluch, M. 1988,
-%      A\&A, 200, 58
-
-%   \bibitem[1980]{cox} Cox, J. P. 1980,
-%      Theory of Stellar Pulsation
-%      (Princeton University Press, Princeton) 165
-
- %  \bibitem[1969]{cox69} Cox, A. N.,\& Stewart, J. N. 1969,
- %     Academia Nauk, Scientific Information 15, 1
-
- %  \bibitem[1980]{mizuno} Mizuno H. 1980,
- %     Prog. Theor. Phys., 64, 544
-
-%   \bibitem[1987]{tscharnuter} Tscharnuter W. M. 1987,
-%      A\&A, 188, 55
-
-%   \bibitem[1992]{terlevich} Terlevich, R. 1992, in ASP Conf. Ser. 31, 
-%      Relationships between Active Galactic Nuclei and Starburst Galaxies, 
-%      ed. A. V. Filippenko, 13
-
-%   \bibitem[1980a]{yorke80a} Yorke, H. W. 1980a,
-%      A\&A, 86, 286
-
-%   \bibitem[1997]{zheng} Zheng, W., Davidsen, A. F., Tytler, D. \& Kriss, G. A.
-%      1997, preprint
-%\end{thebibliography}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Examples for figures using graphicx
-A guide "Using Imported Graphics in LaTeX2e"  (Keith Reckdahl)
-is available on a lot of LaTeX public servers or ctan mirrors.
-The file is : epslatex.pdf 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%_____________________________________________________________
-%                 A figure as large as the width of the column
-%-------------------------------------------------------------
-   \begin{figure}
-   \centering
-   \includegraphics[width=\hsize]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure}
-%
-%_____________________________________________________________
-%                                    One column rotated figure
-%-------------------------------------------------------------
-   \begin{figure}
-   \centering
-   \includegraphics[angle=-90,width=3cm]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure}
-%
-%_____________________________________________________________
-%                        Figure with caption on the right side 
-%-------------------------------------------------------------
-   \begin{figure}
-   \sidecaption
-   \includegraphics[width=3cm]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure}
-%
-%_____________________________________________________________
-%
-%_____________________________________________________________
-%                                Figure with a new BoundingBox 
-%-------------------------------------------------------------
-   \begin{figure}
-   \centering
-   \includegraphics[bb=10 20 100 300,width=3cm,clip]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure}
-%
-%_____________________________________________________________
-%
-%_____________________________________________________________
-%                                      The "resizebox" command 
-%-------------------------------------------------------------
-   \begin{figure}
-   \resizebox{\hsize}{!}
-            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure}
-%
-%______________________________________________________________
-%
-%_____________________________________________________________
-%                                             Two column Figure 
-%-------------------------------------------------------------
-   \begin{figure*}
-   \resizebox{\hsize}{!}
-            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
-      \caption{Vibrational stability equation of state
-               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
-               $>0$ means vibrational stability.
-              }
-         \label{FigVibStab}
-   \end{figure*}
-%
-%______________________________________________________________
-%
-%_____________________________________________________________
-%                                             Simple A&A Table
-%_____________________________________________________________
-%
-\begin{table}
-\caption{Nonlinear Model Results}             % title of Table
-\label{table:1}      % is used to refer this table in the text
-\centering                          % used for centering table
-\begin{tabular}{c c c c}        % centered columns (4 columns)
-\hline\hline                 % inserts double horizontal lines
-HJD & $E$ & Method\#2 & Method\#3 \\    % table heading 
-\hline                        % inserts single horizontal line
-   1 & 50 & $-837$ & 970 \\      % inserting body of the table
-   2 & 47 & 877    & 230 \\
-   3 & 31 & 25     & 415 \\
-   4 & 35 & 144    & 2356 \\
-   5 & 45 & 300    & 556 \\ 
-\hline                                   %inserts single line
-\end{tabular}
-\end{table}
-%
-%_____________________________________________________________
-%                                             Two column Table 
-%_____________________________________________________________
-%
-\begin{table*}
-\caption{Nonlinear Model Results}             
-\label{table:1}      
-\centering          
-\begin{tabular}{c c c c l l l }     % 7 columns 
-\hline\hline       
-                      % To combine 4 columns into a single one 
-HJD & $E$ & Method\#2 & \multicolumn{4}{c}{Method\#3}\\ 
-\hline                    
-   1 & 50 & $-837$ & 970 & 65 & 67 & 78\\  
-   2 & 47 & 877    & 230 & 567& 55 & 78\\
-   3 & 31 & 25     & 415 & 567& 55 & 78\\
-   4 & 35 & 144    & 2356& 567& 55 & 78 \\
-   5 & 45 & 300    & 556 & 567& 55 & 78\\
-\hline                  
-\end{tabular}
-\end{table*}
-%
-%-------------------------------------------------------------
-%                                          Table with notes 
-%-------------------------------------------------------------
-%
-% A single note
-\begin{table}
-\caption{\label{t7}Spectral types and photometry for stars in the
-  region.}
-\centering
-\begin{tabular}{lccc}
-\hline\hline
-Star&Spectral type&RA(J2000)&Dec(J2000)\\
-\hline
-69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
-49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
-LS~1267~(86) &O8\,V     &09 15 52.787&11.07\\
-24.6         &7.58      &1.37 &0.20\\
-\hline
-LS~1262      &B0\,V     &09 15 05.17&11.17\\
-MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\\
-LS~1269      &O8.5\,V   &09 15 56.60&10.85\\
-\hline
-\end{tabular}
-\tablefoot{The top panel shows likely members of Pismis~11. The second
-panel contains likely members of Alicante~5. The bottom panel
-displays stars outside the clusters.}
-\end{table}
-%
-% More notes
-%
-\begin{table}
-\caption{\label{t7}Spectral types and photometry for stars in the
-  region.}
-\centering
-\begin{tabular}{lccc}
-\hline\hline
-Star&Spectral type&RA(J2000)&Dec(J2000)\\
-\hline
-69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
-49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
-LS~1267~(86) &O8\,V     &09 15 52.787&11.07\tablefootmark{a}\\
-24.6         &7.58\tablefootmark{1}&1.37\tablefootmark{a}   &0.20\tablefootmark{a}\\
-\hline
-LS~1262      &B0\,V     &09 15 05.17&11.17\tablefootmark{b}\\
-MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\tablefootmark{c}\\
-LS~1269      &O8.5\,V   &09 15 56.60&10.85\tablefootmark{d}\\
-\hline
-\end{tabular}
-\tablefoot{The top panel shows likely members of Pismis~11. The second
-panel contains likely members of Alicante~5. The bottom panel
-displays stars outside the clusters.\\
-\tablefoottext{a}{Photometry for MF13, LS~1267 and HD~80077 from
-Dupont et al.}
-\tablefoottext{b}{Photometry for LS~1262, LS~1269 from
-Durand et al.}
-\tablefoottext{c}{Photometry for MO2-119 from
-Mathieu et al.}
-}
-\end{table}
-%
-%-------------------------------------------------------------
-%                                       Table with references 
-%-------------------------------------------------------------
-%
-\begin{table*}[h]
- \caption[]{\label{nearbylistaa2}List of nearby SNe used in this work.}
-\begin{tabular}{lccc}
- \hline \hline
-  SN name &
-  Epoch &
- Bands &
-  References \\
- &
-  (with respect to $B$ maximum) &
- &
- \\ \hline
-1981B   & 0 & {\it UBV} & 1\\
-1986G   &  $-$3, $-$1, 0, 1, 2 & {\it BV}  & 2\\
-1989B   & $-$5, $-$1, 0, 3, 5 & {\it UBVRI}  & 3, 4\\
-1990N   & 2, 7 & {\it UBVRI}  & 5\\
-1991M   & 3 & {\it VRI}  & 6\\
-\hline
-\noalign{\smallskip}
-\multicolumn{4}{c}{ SNe 91bg-like} \\
-\noalign{\smallskip}
-\hline
-1991bg   & 1, 2 & {\it BVRI}  & 7\\
-1999by   & $-$5, $-$4, $-$3, 3, 4, 5 & {\it UBVRI}  & 8\\
-\hline
-\noalign{\smallskip}
-\multicolumn{4}{c}{ SNe 91T-like} \\
-\noalign{\smallskip}
-\hline
-1991T   & $-$3, 0 & {\it UBVRI}  &  9, 10\\
-2000cx  & $-$3, $-$2, 0, 1, 5 & {\it UBVRI}  & 11\\ %
-\hline
-\end{tabular}
-\tablebib{(1)~\citet{branch83};
-(2) \citet{phillips87}; (3) \citet{barbon90}; (4) \citet{wells94};
-(5) \citet{mazzali93}; (6) \citet{gomez98}; (7) \citet{kirshner93};
-(8) \citet{patat96}; (9) \citet{salvo01}; (10) \citet{branch03};
-(11) \citet{jha99}.
-}
-\end{table}
-%_____________________________________________________________
-%                      A rotated Two column Table in landscape  
-%-------------------------------------------------------------
-\begin{sidewaystable*}
-\caption{Summary for ISOCAM sources with mid-IR excess 
-(YSO candidates).}\label{YSOtable}
-\centering
-\begin{tabular}{crrlcl} 
-\hline\hline             
-ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
-& YSO type$^{d}$ & Status & Comments\\
-\hline
-  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
-\hline
-  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
-  2 & 0.79:           & 0.97: & Class II ?     & New & \\
-  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
-  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
-\hline
-  \multicolumn{6}{c}{\it Previously known YSOs} \\
-\hline
-  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
-  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
-\hline
-\end{tabular}
-\end{sidewaystable*}
-%_____________________________________________________________
-%                      A rotated One column Table in landscape  
-%-------------------------------------------------------------
-\begin{sidewaystable}
-\caption{Summary for ISOCAM sources with mid-IR excess 
-(YSO candidates).}\label{YSOtable}
-\centering
-\begin{tabular}{crrlcl} 
-\hline\hline             
-ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
-& YSO type$^{d}$ & Status & Comments\\
-\hline
-  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
-\hline
-  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
-  2 & 0.79:           & 0.97: & Class II ?     & New & \\
-  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
-  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
-\hline
-  \multicolumn{6}{c}{\it Previously known YSOs} \\
-\hline
-  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
-  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
-\hline
-\end{tabular}
-\end{sidewaystable}
-%
-%_____________________________________________________________
-%                              Table longer than a single page  
-%-------------------------------------------------------------
-% All long tables will be placed automatically at the end, after 
-%                                        \end{thebibliography}
-%
-\begin{longtab}
-\begin{longtable}{lllrrr}
-\caption{\label{kstars} Sample stars with absolute magnitude}\\
-\hline\hline
-Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
-\hline
-\endfirsthead
-\caption{continued.}\\
-\hline\hline
-Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
-\hline
-\endhead
-\hline
-\endfoot
-%%
-Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
-Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
-Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
-         &      &      &      & H & 0.008686\\
-Gl 86 
-\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
-         & 5.92 & K0 V & 10.91& S & 0.058230\\
-\end{longtable}
-\end{longtab}
-%
-%_____________________________________________________________
-%                              Table longer than a single page
-%                                             and in landscape 
-%  In the preamble, use:       \usepackage{lscape}
-%-------------------------------------------------------------
-% All long tables will be placed automatically at the end, after
-%                                        \end{thebibliography}
-%
-\begin{longtab}
-\begin{landscape}
-\begin{longtable}{lllrrr}
-\caption{\label{kstars} Sample stars with absolute magnitude}\\
-\hline\hline
-Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
-\hline
-\endfirsthead
-\caption{continued.}\\
-\hline\hline
-Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
-\hline
-\endhead
-\hline
-\endfoot
-%%
-Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
-Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
-Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
-         &      &      &      & H & 0.008686\\
-Gl 86
-\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
-         & 5.92 & K0 V & 10.91& S & 0.058230\\
-\end{longtable}
-\end{landscape}
-\end{longtab}
-%
-% Online Material
-%_____________________________________________________________
-%        Online appendices have to be placed at the end, after
-%                                        \end{thebibliography}
-%-------------------------------------------------------------
-\end{thebibliography}
-
-\Online
-
-\begin{appendix} %First online appendix
-\section{Background galaxy number counts and shear noise-levels}
-Because the optical images used in this analysis...
-
-\begin{figure*}
-\centering
-\includegraphics[width=16.4cm,clip]{1787f24.ps}
-\caption{Plotted above...}
-\label{appfig}
-\end{figure*}
-
-Because the optical images...
-\end{appendix}
-
-\begin{appendix} %Second online appendix
-These studies, however, have faced...
-\end{appendix}
-
-\end{document}
-%
-%_____________________________________________________________
-%        Some tables or figures are in the printed version and
-%                      some are only in the electronic version
-%-------------------------------------------------------------
-%
-% Leave all the tables or figures in the text, at their right place 
-% and use the commands \onlfig{} and \onltab{}. These elements
-% will be automatically placed at the end, in the section
-% Online material.
-
-\documentclass{aa}
-...
-\begin{document}
-text of the paper...
-\begin{figure*}%f1
-\includegraphics[width=10.9cm]{1787f01.eps}
-\caption{Shown in greyscale is a...}
-\label{cl12301}}
-\end{figure*}
-...
-from the intrinsic ellipticity distribution.
-% Figure 2 available electronically only
-\onlfig{
-\begin{figure*}%f2
-\includegraphics[width=11.6cm]{1787f02.eps}
-\caption {Shown in greyscale...}
-\label{cl1018}
-\end{figure*}
-}
-
-% Figure 3 available electronically only
-\onlfig{
-\begin{figure*}%f3
-\includegraphics[width=11.2cm]{1787f03.eps}
-\caption{Shown in panels...}
-\label{cl1059}
-\end{figure*}
-}
-
-\begin{figure*}%f4
-\includegraphics[width=10.9cm]{1787f04.eps}
-\caption{Shown in greyscale is...}
-\label{cl1232}}
-\end{figure*}
-
-\begin{table}%t1
-\caption{Complexes characterisation.}\label{starbursts}
-\centering
-\begin{tabular}{lccc}
-\hline \hline
-Complex & $F_{60}$ & 8.6 &  No. of  \\
-...
-\hline
-\end{tabular}
-\end{table}
-The second method produces...
-
-% Figure 5 available electronically only
-\onlfig{
-\begin{figure*}%f5
-\includegraphics[width=11.2cm]{1787f05.eps}
-\caption{Shown in panels...}
-\label{cl1238}}
-\end{figure*}
-}
-
-As can be seen, in general the deeper...
-% Table 2 available electronically only
-\onltab{
-\begin{table*}%t2
-\caption{List of the LMC stellar complexes...}\label{Properties}
-\centering
-\begin{tabular}{lccccccccc}
-\hline  \hline
-Stellar & RA & Dec & ...
-...
-\hline
-\end{tabular}
-\end{table*}
-}
-
-% Table 3 available electronically only
-\onltab{
-\begin{table*}%t3
-\caption{List of the derived...}\label{IrasFluxes}
-\centering
-\begin{tabular}{lcccccccccc}
-\hline \hline
-Stellar & $f12$ & $L12$ &...
-...
-\hline
-\end{tabular}
-\end{table*}
-}
-%
-%-------------------------------------------------------------
-%     For the online material, table longer than a single page
-%                 In the preamble for landscape case, use : 
-%                                          \usepackage{lscape}
-%-------------------------------------------------------------
-\documentclass{aa}
-\usepackage[varg]{txfonts}
-\usepackage{graphicx}
-\usepackage{lscape}
-
-\begin{document}
-text of the paper
-% Table will be print automatically at the end, in the section Online material.
-\onllongtab{
-\begin{longtable}{lrcrrrrrrrrl}
-\caption{Line data and abundances ...}\\
-\hline
-\hline
-Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & N & e &  rad & $\delta$ & $\delta$ 
-red & References \\
-\hline
-\endfirsthead
-\caption{Continued.} \\
-\hline
-Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & B & C &  rad & $\delta$ & $\delta$ 
-red & References \\
-\hline
-\endhead
-\hline
-\endfoot
-\hline
-\endlastfoot
-A & CH & 1 &3638 & 0.002 & $-$2.551 &  &  &  & $-$150 & 150 &  Jorgensen et al. (1996) \\                    
-\end{longtable}
-}% End onllongtab
-
-% Or for landscape, large table:
-
-\onllongtab{
-\begin{landscape}
-\begin{longtable}{lrcrrrrrrrrl}
-...
-\end{longtable}
-\end{landscape}
-}% End onllongtab

### 2025-02-06 src/scripts/plot_HARPS_CN_stellar_frame.py
removed macox

@@ -4,7 +4,7 @@ import paths
 from astropy.io import fits
 import matplotlib as mpl
 
-mpl.use('macosx')
+#mpl.use('macosx')
 
 T0=fits.getdata(paths.data/'T_gas.fits')
 N0=fits.getdata(paths.data/'Nf.fits')

### 2025-02-06 src/scripts/plot_HARPS_CN_exocomet_frame.py
removed macox

@@ -4,7 +4,7 @@ import paths
 from astropy.io import fits
 import matplotlib as mpl
 
-mpl.use('macosx')
+#mpl.use('macosx')
 
 
 T0=fits.getdata(paths.data/'T_gas.fits')

### 2025-02-06 src/scripts/analyse_HARPS_spectra.py
removed macox

@@ -618,7 +618,7 @@ if __name__ == "__main__":
    '''
    
 
-   mpl.use('agg')##macosx')
+#   mpl.use('agg')##macosx')
    #mpl.use('macosx')
    mpl.rcParams['figure.figsize'] = 12, 8
    mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')

### 2025-02-06 src/scripts/gauss_slope_fit.py

@@ -17,7 +17,7 @@ import warnings
 
 import matplotlib as mpl
 
-mpl.use('macosx')
+#mpl.use('macosx')
 
 pp1 = models.Gaussian1D(100, 0, 10)
 pp2 = models.Linear1D(slope=0.3, intercept=2.0)

### 2025-02-06 src/scripts/plot_CN_ACF.py

@@ -4,7 +4,7 @@ from astropy.io import fits
 import matplotlib as mpl
 import paths
 
-mpl.use('macosx')
+#mpl.use('macosx')
 mpl.rcParams['figure.figsize'] = 12, 8
 mpl.rc('image', interpolation='nearest', origin='lower', cmap = 'gray')
 

### 2025-02-06 src/scripts/plot_FEB_velocity_depth.py

@@ -3,7 +3,7 @@ from astropy.io import fits
 import numpy as np
 import paths
 import matplotlib as mpl
-mpl.use('macosx')
+#mpl.use('macosx')
 
 FEB_spec=fits.getdata(paths.data/'FEB_spec.fits')
 FEB_idx=fits.getdata(paths.data/'FEB_idx.fits')

### 2025-02-06 src/scripts/plot_HARPS_CN_grid.py

@@ -11,7 +11,7 @@ import paths
 from astropy.io import fits
 import matplotlib as mpl
 
-mpl.use('macosx')
+#mpl.use('macosx')
 
 
 T0=fits.getdata(paths.data/'T_gas.fits')

### 2025-02-07 src/tex/ms.tex
auth
date
cleaned latex

@@
           \and
-          C. Opitom\inst{3}
+          A.\ Brandeker\inst{3}
           \and 
-          A.\ Brandeker\inst{4}
+         C. Opitom\inst{4}
           \and
@@
         \and
+        Institutionen f\"{o}r astronomi, Stockholms universitet, AlbaNova universitetscentrum, 106 91, Stockholm, Sweden
+        \and
         Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, UK
-        \and
-        Institutionen f\"{o}r astronomi, Stockholms universitet, AlbaNova universitetscentrum, 106 91, Stockholm, Sweden
         \and
@@
 
-   \date{Received XXXX; Accepted XXXX}
+   \date{Received 7 Feb 2025; Accepted XXXX}
 
@@
 Release from dust grains as well as molecular processes have been suggested as possible sources of \ion{Na}{i} in the coma and tail of comets annd explain its presence at large solar distances \citep{Cremonese1997}.
-%Na appears to be weakly bound to the dust grains and released at larger solar distances.
 
@@
 
-% \begin{figure}
-%     \begin{centering}
-%         \includegraphics[width=\columnwidth]{figures/asdf.png}
-%         \caption{Test picture}
-%         \label{fig:test}
-%     \end{centering}
-% \end{figure}
-
-% \begin{figure}
-%     \begin{centering}
-%         \includegraphics[width=\columnwidth]{figures/HARPS_CN_grid.pdf}
-%         \caption{Confidence intervals for the signal to noise of \ce{CN} spectra using \ac{harps} spectra of \bp{}.}
-%         \label{fig:HARPS_CN_grid}
-%         \script{plot_HARPS_CN_grid.py}
-%     \end{centering}
-% \end{figure}
-
-%\subsection{Other Species? CO$^+$, C$_2$?}
-
 \subsection{Estimating the \ce{CN} column density limits}\label{sect:CNlim}
@@
 
-%\subsection{Summary of \ce{CN} in comets}
-%\ce{CN} is one of the brightest optically active species in cometary comae.
+As discussed above in the introduction, most studies of Solar system comets observe the \ce{CN} molecules via optical fluorescence. 
 %
-%It is a minor component of the gas coma, with a production rate by number $\sim 1/500$th that of water. 
-As discussed above in the introduction, most studies of Solar system comets observe the \ce{CN} molecules via optical fluorescence.
-From measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
+rom measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
+%
 This means a flux from part of the coma can immediately be converted to a column density using a photon scattering efficiency for the molecular band.
@@
 \ce{CN} in solar system comets comes from two sources.
+%
 Sublimation of nucleus near-surface ices releases \ce{HCN}, which then photo-dissociates into \ce{CN}.
+%
 This in turn eventually photo-dissociates into the component atoms.
@@
 Since observations of Comet Halley \citep{AHearn1986}, it has also been known that dust grains ejected from the nucleus also directly release \ce{CN} into the coma.
+%
 However, \ce{CN} production in comets is usually dominated by nuclear ice sublimation \citep{Fray2005}.
+%
 The resulting \ce{CN} coma will have a true space density and apparent column density distribution centrally peaked at the comet nucleus in this case.
 
-For Solar system comets, measured \ce{CN} column densities are often converted to an overall production rate by the comet of $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model \citep{Haser2020}
-This model gives the on-sky column density as a function of projected radial distance form the nucleus using only 3 parameters; the effective destruction scale length $l_p$ of the parents of \ce{CN} (\ce{HCN}+dust), the photodissociation scale length $l_{\ce{CN}}$ of \ce{CN}, and the gas outflow velocity $v$.
+For Solar system comets, measured \ce{CN} column densities are often converted to an overall production rate by the comet of $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model \citep{Haser2020}.
+%
+This model gives the on-sky column density as a function of projected radial distance form the nucleus using only three parameters; the effective destruction scale length $l_p$ of the parents of \ce{CN} (\ce{HCN}+dust), the photodissociation scale length $l_{\ce{CN}}$ of \ce{CN}, and the gas outflow velocity $v$.
+%
 The Haser model is somewhat simplistic but it represents the data well for solar system comets observed at typical distances from the Sun (1--3 au).
@@
 Although most Solar system comets are observed to be are far less active than Halley, some Long-Period comets show activity in excess of Halley.
+%
 Given that we will be dominated by the most active comets at \bp{}, this seems reasonable as something that can be later scaled to the most active comets such as Hale-Bopp \citep{Schleicher2024}.
@@
 %
-These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ km/sec, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq1$ \kms{} \citep{Combi1980}.
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq1$ \kms{} \citep{Combi1980}.
 
 \subsection{1P/Halley at \bp{}}
-
-%\subsubsection{Total \ce{CN} Abundance}
 
@@
 
-In steady-state sublimation, the sublimation rate is proportional to the photon flux at the comet. For \bp{} $L=8.7L_\odot$, so assuming 
-all \ce{CN} production scales with stellar luminosity, exoHalley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 9\times10^{27}$ molecules/sec.
+In steady-state sublimation, the sublimation rate is proportional to the photon flux at the comet.
+%
+For \bp{} $L=8.7L_\odot$, so assuming all \ce{CN} production scales with stellar luminosity, exoHalley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 9\times10^{27}$ molecules/sec.
 %
@@
 %\subsubsection{\ce{CN} Cross-section}
-The effective cross section of the coma will depend on how much is projected against the disk of \bp{}. The radius of the \ce{CN} coma will be given by
+The effective cross section of the coma will depend on how much is projected against the disk of \bp{}.
+%
+The radius of the \ce{CN} coma will be given by
 $$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$.
+
 The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature, which will increase as a comet moves towards its parent star.
+%
 \citet{Biver2002} found a nuclear gas outflow velocity $v\simeq1.0  r_h^{-0.4}$ \kms{} from sub-mm measurements of Comet Hale-Bopp, close to the canonical relationship of $r_h^{-0.5}$.
+%
 \citet{Harris2002} notes lower activity similar to Halley results in smaller outflow velocities.
-%Dust grains will also be travelling faster due to the larger gas pressure accelerating them.
+%
 The excess photodissociation velocity of \ce{CN} will not change.
+%
 Therefore gas outflow speeds are expected to be $\sim 1-2$ \kms{} at 1 AU, and the \ce{CN} coma radius will be
@@
 $$r\sim (1-2) \times 2\times 10^{4} \leq 4\times 10^{4}\:{\rm km}$$
+%
 This is much smaller than a stellar radius, so we can assume for an exoHalley that all of the coma is projected into the stellar disk as seen from Earth.
@@
 
-%\subsubsection{We need a bigger comet}
 There are several ways exocomets at \bp{} may exhibit larger \ce{CN} production rates.
@@
 %
- Comet Halley's nucleus has an effective radius of $5.5$ km \citep{Keller1987}, whereas 
-Comet Hale-Bopp was one of the most intrinsically active comets on record with an extremely large nucleus of radius $\sim 14-21$ km \citep{Weaver1997}.
+ Comet Halley's nucleus has an effective radius of $5.5$ km \citep{Keller1987}, whereas Comet Hale-Bopp was one of the most intrinsically active comets on record with an extremely large nucleus of radius $\sim 14-21$ km \citep{Weaver1997}.
 %
@@
 In this case, we might anticipate the most active comets in the Solar system to have $Q_{\ce{CN}}\sim 10^{28}$ molecules/sec, implying a commensurate increase of a factor 10 in column density $n$ over an exoHalley at \bp{}.
-
-%\subsubsection{Turn on the taps}
 
@@
 Yet some comets are known as hyperactive, as the measured gas productions rates would require $\geq 100$\% of the nucleus surface to be active \citep{Sunshine2021}.
+%
 This is believed to be due to the release of ice-rich dust grains from the nucleus, which sublimate and act as a secondary source of gas.
+%
 Assuming this is possible for exocomets at \bp{} would increase $N_{\ce{CN}}$ and $n$ by a factor $\sim 5$.
 
-%\subsubsection{Move it closer to \bp{}}
-
-The closer a comet to its parent star, the greater the heating and corresponding production rate. When insolation completely controls the nuclear surface energy balance we expect
+The closer a comet to its parent star, the greater the heating and corresponding production rate.
+%
+When insolation completely controls the nuclear surface energy balance we expect
 $Q_{\ce{CN}}\propto r_h^{-2}$.
 %
-Studies of Halley and Hale-Bopp showed power laws close to this {\it i.e.} \cite{Biver2002}. But the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
+Studies of Halley and Hale-Bopp showed power laws close to this {\it i.e.} \cite{Biver2002}.
+%
+But the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
 $$N_{\ce{CN}}=\frac{Q_{\ce{CN}}(1~\rm{au})}{r_h^2}\cdot  \tau_{\ce{CN}} (1~\rm{au}) r_h^2 =\:{\rm constant} $$
@@
 
-%\subsubsection{Stay up all night to get lucky}
 Finally, comets have impulsive outbursts, where the amount of material ejected into the coma increases significantly over a few hours or less.
-%
-%This varies from comet to comet; many do not appear to outburst, some have 1 or a few outbursts per orbit.
 %
@@
 Large outbursts are often due to partial or total disruption of a comet and can occur when a comet is closer to the Sun.
+%
 Hence there could be a correlation with faster moving \bp{} exocomets nearer their periastra producing greater measurable column densities of \ce{CN}.
@@
 In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} could exceed $n\sim10^9-10^{10}$ cm$^{-2}$.
-A larger and/or hyperactive nucleus could increase $n$ by a factor 10.
+%
+A larger and/or hyperactive nucleus could increase $n$ by a factor of ten.
+%
 Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{12}$ cm$^{-2}$.
@@
 This is a factor of 10 to 100 too high to detect a single Hale-Bopp equivalent comet with a \ce{CN} coma.
-%
-%We detect no \ce{CN} absorption, but can place five sigma upper limits of 10e12 to 10e13 from 10 to 1800 K.
-%
-%Hale-Bopp in transit will be around $10^{10}$, so we are two orders of magnitude above this in our detection.
 %

### 2025-02-08 src/tex/ms.tex
fix pdf section labels

@@
 
-\section{Searches for \ce{CN}}\label{sect:CNsearch}
+\section{Searches for \texorpdfstring{\ce{CN}}{CN}}\label{sect:CNsearch}
 
@@
 
-\subsection{Identifying exocomets from \ion{Ca}{ii} H line}\label{sect:FEBid}
+\subsection{Identifying exocomets from \texorpdfstring{\ion{Ca}{ii}}{CaII} H line}\label{sect:FEBid}
 The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
@@
 
-\subsection{Cross-correlation with \ce{CN} models}\label{sect:CCF}
+\subsection{Cross-correlation with \texorpdfstring{\ce{CN}}{CN} models}\label{sect:CCF}
 
@@
 
-\subsection{Estimating the \ce{CN} column density limits}\label{sect:CNlim}
+\subsection{Estimating the \texorpdfstring{\ce{CN}}{CN} column density limits}\label{sect:CNlim}
 
@@
 
-\subsection{1P/Halley at \bp{}}
+\subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}
 
@@
 
-\subsection{Raising the \ce{CN} production rates}
+\subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}
 

### 2025-04-01 src/tex/ms.tex
partial response

@@
 \newcommand{\kms}{km s$^{-1}$}
+
 \newcommand{\bpb}{$\beta$\,Pic\,b}
@@
 
-%\newcommand\pdfmath[1]{\texorpdfstring{$#1$}{#1}}
-
 \usepackage[nolist,nohyperlinks]{acronym}
@@
 \newacro{uves}[UVES]{Ultra-violet Visible Echelle Spectrograph}
-\newacro{feb}[FEBs]{Falling Evaporating Bodies}
+\newacro{feb}[FEBs]{Exocomets}
 
-%
 \usepackage{graphicx}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{txfonts}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
+
 \usepackage{showyourwork}
@@
 \begin{document} 
-
-   \title{Upper Limits on CN from Falling Evaporating Bodies\\seen towards $\beta$~Pictoris}
-
+   \title{Upper limits on CN from exocomets transiting $\beta$~Pictoris}
    \author{M.A. Kenworthy
@@
           }
-
    \institute{Leiden Observatory, Leiden University, P.O. Box 9513, 2300 RA Leiden, The Netherlands\\
@@
 
-% \abstract{}{}{}{}{} 
-% 5 {} token are mandatory
-
   \abstract
@@
    %
-   Many transient absorption features have been detected in the rotationally broadened stellar lines of the star's chromosphere, and these are thought to be the coma of infalling exocomets crossing the line of sight towards Earth.
-}
+   Many transient absorption features have been detected in the rotationally broadened stellar lines, which are thought to be the coma of infalling exocomets crossing the line of sight towards Earth.}
   % aims heading (mandatory)
@@
    %
-   The high signal to noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal to noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.
-   }
+   The high signal to noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal to noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.}
   % results heading (mandatory)
-   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, which is 100 times higher than seen for comets in our Solar System.
-   }
-  % conclusions heading (optional), leave it empty if necessary 
-   %{\ac{feb} are not Solar System comets in composition.}
+   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, to be compared to the typical 10$^9$ - 10$^{10}$ cm$^{-2}$ expected from scaling of the values in the Solar System comets.}
 
@@
    \maketitle
-%
-%________________________________________________________________
 
@@
 %
-The star is a rapid rotator \citep[$124\pm 3$\,\kms{}; ][]{Koen03} seen close to equator on, resulting in rotational broadening of the chromospheric lines.
+The star is a rapid rotator \citep[$124\pm 3$\,\kms{}; ][]{Koen03} seen close to equator on.
 %
@@
 
-Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to \ac{feb} moving towards the star \citep{Ferlet87}.
+Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to the transit of evaporating exocomets in front of the star \citep{Ferlet87}.
 %
@@
 %
-The absorption can be described by the evaporation of infalling bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing Calcium ions which are then seen as an additional absorption component \citep{Beust91}.
+The absorption can be described by the transit of evaporating bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing calcium ions which are then seen as an additional absorption component \citep{Beust91}.
 %
-Intensive spectroscopic monitoring over several hours show both multiple components transiting the disk of the star \citep{Beust96} and changes of radial velocity of several components are consistent with Keplerian elliptical orbits \citep{Kennedy18} implying at least two \citep{Kiefer14,Pollard24} or more \citep{Heller24} distinct kinematic families of FEBs.
+Intensive spectroscopic monitoring over several hours show both multiple components transiting the disk of the star \citep{Beust96} and changes of radial velocity of several components are consistent with Keplerian elliptical orbits \citep{Kennedy18} implying at least two \citep{Kiefer14,Pollard24} or more \citep{Heller24} distinct kinematic families of Beta Pictoris exocomets.
 %
 At least one event is derived with the orbit parallel to the rotational axis of the star \citep{Tobin19}.
+
+From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted in \citet{1999A&A...343..916L}.
 %
-Given the kinematic and spectroscopic evidence, these have subsequently been labelled as ``exocomets''.
-
-From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted \citep{LecavelierdesEtangs97} and subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
+{\bf A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
+single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.}
 %
@@
 
-To the contrary of what is observed in the case of \ac{feb}, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
+To the contrary of what is observed in the case of Beta Pictoris exocomets, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
 %
@@
 A notable discovery was a spectacular tail of \ion{Na}{i} associated with comet C/1995 O1 Hale-Bopp at $r\sim 1$ au, formed by radiation pressure on the neutral atoms before ionisation \citep{Cremonese1997}.
+%
 Recently, \cite{Hui2023} also demonstrated thet the activity of near-Earth asteroid Phaeton, with a perihelion of only 0.14 au, is associated with emission of sodium.
@@
 Most of the neutral and ionic molecular emission results from resonance fluorescence with solar photons.
+%
 Some species, such as \ce{H2O+} and \ce{CO+} result from ionization of parent molecules (i.e.
@@
 
-The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA \ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
+The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA{}\ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
 %
-The \ce{OH} (0-0) band at $\lambda\simeq 3080$ \AA \ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
+The \ce{OH} (0-0) band at $\lambda\simeq 3080$ \AA{}\ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
 %
@@
 %
-However this is normally significantly weaker than the observed \ce{CN} emission, with only less than 20 comets.
+However this is normally significantly weaker than the observed \ce{CN} emission, with detection in only less than 20 comets.
 %
-Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the \ac{feb} around \bp{}.
+Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the exocomets around \bp{}.
 %
@@
 %
-Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Section~\ref{sect:CNsearch}, and the discussion and interpretaion is in Section~\ref{sec:discuss} with our conclusions in Section~\ref{sec:conclusion}.
+Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Section~\ref{sect:CNsearch}, and the discussion and interpretation is in Section~\ref{sec:discuss} with our conclusions in Section~\ref{sec:conclusion}.
 
@@
 %
-This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\,\AA and 4075\,\AA) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
+This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\,\AA{} and 4075\,\AA) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
 %
@@
 The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
+%
 The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
+%
 Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
+%
 This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin.
 This binned ratio was then fitted using a second order polynomial.
+%
 The original spectrum was finally divided by this polynomial to correct for the changes.
@@
 %For both HARPS and UVES w
-We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}). %For HARPS
-This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, %for both UVES and HARPS
-an 8th order polynomial was used.
+We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}).
+%
+%For HARPS
+This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.
 
@@
 %
-Before binning, the spectrum in each bin was MAD (median absolute deviation) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
+Before binning, the spectrum in each bin was median absolute deviation (MAD) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
 %
@@
 \subsection{Identifying exocomets from \texorpdfstring{\ion{Ca}{ii}}{CaII} H line}\label{sect:FEBid}
-The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 km\,s$^{-1}$.
+
+The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 \kms{}.
 %
@@
 %
-The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}.
+The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}. The dates, velocities and depths of the selected exocomets can be found in Tab.~\ref{tab:FEB_data}
 
@@
         \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
-The large signal around 3860\,\AA is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        %
+        The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
         \label{fig:spec_CN_stellar_frame}
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
-        \caption{Plot of the stacked spectrum in the stellar rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
-The large signal around 3860\,\AA is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        \caption{Plot of the stacked spectrum in the comet rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
         \label{fig:spec_CN_comet_frame}
@@
         \includegraphics[width=\columnwidth]{figures/CN_ACF.pdf}
-        \caption{\ce{CN} autocorrelation function for different temperatures. The aliasing at $\sim50$\,km\,s$^{-1}$ is clearly visible}
+        \caption{\ce{CN} autocorrelation function for different temperatures. The aliasing at $\sim50$\,\kms{} is clearly visible}
         \label{fig:CN_ACF}
@@
 %
-Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} km\,s$^{-1}$.
+Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} \kms{}.
 %
-A value of 2.9 km\,s$^{-1}$ corresponds approximately to the instrumental resolution of HARPS.
+A value of 2.9 \kms{} corresponds approximately to the instrumental resolution of HARPS.
 %
@@
         %
-        Peaks closer than 10 km/s are masked out due to contamination from the circumstellar material.
+        Peaks closer than 10 \kms{} are masked out due to contamination from the circumstellar material.
         %
@@
         \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
-        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7\kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7 \kms{}. Contours show signal to noise upper limits.}
         \label{fig:CN_stellar_frame}
@@
         \includegraphics[width=\linewidth]{figures/HARPS_CN_exocomet_frame.pdf}
-        \caption{\ce{CN} measurement limits in the exocomet frame for a \ce{CN} line width of 2.7, 10 and 20\kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the exocomet frame for a \ce{CN} line width of 2.7, 10 and 20 \kms{}. Contours show signal to noise upper limits.}
         \label{fig:CN_exocomet_frame}
@@
 %
-rom measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
+From measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
 %
@@
 %
-These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq1$ \kms{} \citep{Combi1980}.
-
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and {\bf 
+we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}. 
+}
 \subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}
 
-Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by Ly-$\alpha$ line flux.
-From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A6V/A7V stars is a factor of $\sim10$ higher than for G2V stars.
+Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by {\bf the Ly-$\alpha$ line flux \citep{Combi80}.
 %
-Hence the photodissociation lifetime of \ce{CN}  at 1 au from \bp{} of an `exoHalley' will be approximately 10 times smaller i.e. $\sim 2\times10^4$ sec at 1 au.
+The  Ly-$\alpha$ emission from \bp{} has been measured by \citet{Wilson17} via HST+COS.
+Using their ISM and CSM corrected Voigt line profile parameters, we integrated over $\pm600$ \kms{} and corrected for the distance of \bp{} to derive an intrinsic Ly-$\alpha$ luminosity of $1.4\times10^{30}$ ergs sec$^{-1}$.
+
+The solar Ly-$\alpha$  flux varies by $\sim 50\% $ over the Solar cycle, with a mean value at Earth of $4.7\times10^{11}$ phot s$^{-1}$ cm$^{-2}$ \citep{Woods00}.
+The resulting mean solar Ly-$\alpha$ luminosity is $2.1\times10^{28}$ ergs sec$^{-1}$, a factor of $\sim 67$ lower than \bp{}.
+%From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A6V/A7V stars is a factor of $\sim10$ higher than for G2V stars.
+%
+Hence the photodissociation lifetime of \ce{CN}  at 1 au from \bp{} of an `exoHalley' will be approximately 67 times shorter i.e. $\sim 3000$ sec.
+}
 
@@
 $$N_{\ce{CN}}=Q_{\ce{CN}} \tau_{\ce{CN}}$$
-$$N_{\ce{CN}}\sim 9\times10^{27} \cdot  2\times10^4 \sim 2\times10^{32}\:{\rm molecules}$$
+
+$$N_{\ce{CN}}\sim 9\times10^{27} \cdot  3000 \sim 3\times10^{31}\:{\rm molecules}$$
 
@@
 The radius of the \ce{CN} coma will be given by
-$$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$.
-
+$$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$
 The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature, which will increase as a comet moves towards its parent star.
@@
 %
-$$r\sim (1-2) \times 2\times 10^{4} \leq 4\times 10^{4}\:{\rm km}$$
+$$r\sim (1-2) \times 3000 \leq 6\times 10^{3}\:{\rm km}$$
 %
@@
 
-$$n\sim\frac{2\times10^{32}}{\pi\cdot 1.7\times10^{22}}\sim 3\times10^{9}\:{\rm cm^{-2}}$$
-Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{9}-10^{10}$ cm$^{-2}$.
+$$n\sim\frac{3\times10^{31}}{\pi\cdot 1.7\times10^{22}}\sim 6\times10^{8}\:{\rm cm^{-2}}$$
+Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{8}-10^{9}$ cm$^{-2}$.
 %
-This is about a factor of 100 smaller than our measured upper limits above.
-
+This is 
+{\bf
+$\geq100$ times smaller than our measured upper limits above.
+}
 \subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}
@@
 
-In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} could exceed $n\sim10^9-10^{10}$ cm$^{-2}$.
+In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} 
+{\bf
+could exceed $10^{9}$ cm$^{-2}$.
 %
@@
 %
-Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{12}$ cm$^{-2}$.
+Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{11}$ cm$^{-2}$. 
+}
 
@@
 
+\begin{appendix}
+
+\section{Selected exocomets.}\label{sec:app_FEBs}
+The dates for the nights selected to have the strongest exocomet features, as well as the depths and velocities of these features can be found in Tab.~\ref{tab:FEB_data}.
+\begin{table}
+\caption{Table with the nights with the strongest exocomet features.
+Note that the dates given are for the average of all the observations that were combined during each of the nights.}\label{tab:FEB_data}
+\begin{tabular}{c c c}
+   BJD-2,400,000  &    v$_{comet}$  &  Depth\\
+ & [km/s] & \\
+ \hline
+\hline
+53031.2 & 19.7 & 0.63\\
+53032.2 & 18.9 & 0.74\\
+53033.1 & 22.3 & 0.76\\
+53036.1 & 15.5 & 0.67\\
+53045.1 & 18.0 & 0.72\\
+53046.1 & 18.0 & 0.91\\
+53047.1 & 20.6 & 0.84\\
+53048.0 & 20.6 & 0.83\\
+53049.1 & 20.6 & 0.94\\
+53050.1 & 18.9 & 0.90\\
+53051.1 & 18.9 & 0.87\\
+53052.1 & 18.9 & 0.92\\
+53053.1 & 18.0 & 0.93\\
+53054.1 & 17.2 & 0.83\\
+53056.1 & 16.3 & 0.86\\
+53057.1 & 15.5 & 0.93\\
+53058.1 & 14.6 & 0.92\\
+53059.1 & 14.6 & 0.87\\
+53060.1 & 13.7 & 0.82\\
+53061.1 & 13.7 & 0.72\\
+53062.1 & 12.9 & 0.69\\
+53063.1 & 12.0 & 0.67\\
+53064.1 & 12.0 & 0.61\\
+53581.4 & -8.5 & 0.65\\
+54223.0 &  8.6 & 0.62\\
+54542.1 & 29.2 & 0.91\\
+54544.1 & 28.3 & 0.92\\
+54545.0 & 23.2 & 0.79\\
+54546.0 &  8.6 & 0.80\\
+54799.2 &  8.6 & 0.75\\
+54878.1 & 14.6 & 0.76\\
+54913.0 & 12.0 & 0.81\\
+56524.4 & 31.7 & 0.76\\
+56534.3 & 12.9 & 0.76\\
+56536.3 &  8.6 & 0.61\\
+57849.0 & 10.3 & 0.73\\
+\end{tabular}
+\end{table}
+
+\end{appendix}
+
 \end{document}

### 2025-04-10 src/tex/ms.tex
EdM updates

@@
 
+{\bf When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) masked to avoid contamination, especially for the higher temperature CN models.
+We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm$0.35~$\AA$ for the \ion{Fe}{I} 3859.9$\AA$ line, while for the other lines a width of $\pm$0.15$\AA$ was use.}
+
 Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean} do not show any clear signals, and we therefore proceed to estimate our detection limits.

### 2025-04-10 src/scripts/analyse_HARPS_spectra.py

@@ -55,7 +55,7 @@ def get_mdl(fn='CN/CN_0300K.npy',N=1e15,FWHM_kernel=3e5/1.1e5):
     mdl=prof_i(w_mdl)
 
     ## generate a Gaussian kernel with the FWHM at the instrumental resolution & convolve model
-    print(FWHM_kernel)
+    
     x_kernel=np.arange(-90.,90.001,(3e5/res_interp))
     kernel=np.exp( - ((x_kernel)**2)/2./(FWHM_kernel/2.35)**2)
     kernel=kernel/np.sum(kernel)
@@ -99,13 +99,7 @@ def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=6):
     
     # fit a polynomial to the this ration (should be flat if there was no small residuals)
     # and then divide it out to make this order relatively flat
-    # TODO add sigma clipping for this
     for i in range(spec.shape[0]):
-        #       x=pixels.copy()
-        #       y=spec_cor[i,:].copy()
-        #       idx=(y>0)*np.isfinite(y)*(x>o_start[ord])*(x<o_end[ord])
-        #       l=np.polyfit(x[idx]-x[0],y[idx],poly_order)
-        #       spec_cor[i,:]=spec_cor[i,:]/np.polyval(l,x-x[0])
         x0=pixels.copy()
         bin_spec=spec_cor[i,:nbins*binsize].reshape(nbins,binsize).copy()
         bin_x=x0[:nbins*binsize].reshape(nbins,binsize).astype(float)
@@ -131,12 +125,6 @@ def remove_resid_blaze(pixels,spec,star_spec,ord=3,poly_order=6):
 def remove_stellar_envelope(spec,ord):
     spec0 = spec[:,ord,:].copy()
 
-    '''
-    #####OLD CODE, CLIPS TOO MUCH####
-    #remove outliers to get a good sigma-clipped spectrum for stationary features
-    filtered_data = sigma_clip(spec0, sigma_lower=1.0, sigma_upper=5, maxiters=3, axis=0, copy=True, masked=True,cenfunc='median',stdfunc='mad_std')
-    spec_star_only0 = np.ma.mean(filtered_data, axis=0).filled(np.nan)
-    '''
     ##Estimate the upper envelope. In this case use the [5,15] brightest pixels. Note: This is not robust against outliers...
[…]

### 2025-04-10 src/scripts/plot_exocomet_CCFs.py

@@ -1,0 +1,37 @@
+import matplotlib.pyplot as plt
+from astropy.io import fits
+import numpy as np
+from scipy.interpolate import interp1d
+import paths
+
+hdu=fits.open(paths.data/'v_phasefold.fits')
+v=hdu[0].data
+hdu.close()
+
+hdu=fits.open(paths.data/'phase_cube_comet.fits')
+d=hdu[0].data
+hdu.close()
+
+hdu=fits.open(paths.data/'FEB_idx.fits')
+idx=hdu[0].data.astype(bool)
+hdu.close()
+
+hdu=fits.open(paths.data/'T_gas.fits')
+T_gas=hdu[0].data
+hdu.close()
+
+
+ord=3
+
+
+f,ax=plt.subplots(4,5,sharex=True,sharey=True,figsize=(15,9))
+for i in range(5):
+    for j in range(4):
+        ax[j,i].pcolormesh(v,np.arange(idx.sum()),d[i+j*5,33,0,idx,:])
+        ax[j,i].annotate("{0:} K".format(T_gas[i+j*5]),(84,30),ha='right')
+        if i==0:
+            ax[j,i].set_ylabel('Night Number')
+    ax[3,i].set_xlabel('v$_{rest,comet}$ [km/s]')
+f.tight_layout()
+f.subplots_adjust(hspace=0,wspace=0)
+plt.savefig(paths.figures/'CN_CCF_ExocometRestframe.pdf')

### 2025-04-11 src/tex/ms.tex
final tweaks

@@
 \bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
+\usepackage{float}
+\usepackage{placeins}
 
@@
 
-   \keywords{comets --- transits, spectroscopy}
+   \keywords{comets --- transits, spectroscopy, stars: individual: Beta Pictoris}
 
@@
 %
-This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin.
-This binned ratio was then fitted using a second order polynomial.
+This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, {\bf clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.} This binned ratio was then fitted using a second order polynomial.
 %
@@
 %For both HARPS and UVES w
-We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}).
+We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), {\bf similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.}
 %
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
-        \caption{Plot of the stacked spectrum in the comet rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
-The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
+        \caption{{\bf Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the cometp.} The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
         \label{fig:spec_CN_comet_frame}
@@
 
+\clearpage
+\FloatBarrier
+
 \begin{appendix}

### 2025-04-11 src/tex/ms.tex
removed bolding

--- 2025-04-01 src/tex/ms.tex
@@
 %
-{\bf A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
-single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.}
+A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
+single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
 %
@@
 %
-This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin.
+This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.
+%
 This binned ratio was then fitted using a second order polynomial.
@@
 %For both HARPS and UVES w
-We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}).
+We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
 %
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
-        \caption{Plot of the stacked spectrum in the comet rest frame (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+        \caption{Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet.
 The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
@@
 The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.
+
+When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) were masked to avoid contamination, especially for the higher temperature CN models.
+%
+We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm$0.35~$\AA$ for the \ion{Fe}{I} 3859.9$\AA$ line, while for the other lines a width of $\pm$0.15$\AA$ was used.
 
@@
 %
-These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and {\bf 
-we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}. 
-}
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}.
+
 \subsection{1P/Halley at \texorpdfstring{\bp{}}{Beta Pictoris}}
 
-Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by {\bf the Ly-$\alpha$ line flux \citep{Combi80}.
+Photodissociation is  driven by the UV photon flux at the comet, which in turn is dominated by the Ly-$\alpha$ line flux \citep{Combi80}.
 %
 The  Ly-$\alpha$ emission from \bp{} has been measured by \citet{Wilson17} via HST+COS.
+%
 Using their ISM and CSM corrected Voigt line profile parameters, we integrated over $\pm600$ \kms{} and corrected for the distance of \bp{} to derive an intrinsic Ly-$\alpha$ luminosity of $1.4\times10^{30}$ ergs sec$^{-1}$.
@@
 The solar Ly-$\alpha$ flux varies by $\sim 50\% $ over the Solar cycle, with a mean value at Earth of $4.7\times10^{11}$ phot s$^{-1}$ cm$^{-2}$ \citep{Woods00}.
+%
 The resulting mean solar Ly-$\alpha$ luminosity is $2.1\times10^{28}$ ergs sec$^{-1}$, a factor of $\sim 67$ lower than \bp{}.
-%From Ly-$\alpha$ measurements in \citet{Landsman93} the intrinsic Ly-$\alpha$ luminosity of A6V/A7V stars is a factor of $\sim10$ higher than for G2V stars.
 %
 Hence the photodissociation lifetime of \ce{CN} at 1 au from \bp{} of an `exoHalley' will be approximately 67 times shorter i.e. $\sim 3000$ sec.
-}
 
@@
 %
-This is 
-{\bf
-$\geq100$ times smaller than our measured upper limits above.
-}
+This is $\geq100$ times smaller than our measured upper limits above.
+
 \subsection{Raising the \texorpdfstring{\ce{CN}}{CN} production rates}
@@
 
-In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} 
-{\bf
-could exceed $10^{9}$ cm$^{-2}$.
+In summary, mechanisms exist by which the \ce{CN} column density of an exocomet at \bp{} could exceed $10^{9}$ cm$^{-2}$.
 %
@@
 Even larger increases are possible with an outburst or comet disruption, but the upper boundary is likely to be near $n\sim10^{11}$ cm$^{-2}$.
-}
 
@@
 \bibliography{bib.bib}
+
+\clearpage
+\FloatBarrier
 

### 2025-04-14 src/tex/ms.tex
accepted

@@
         \and
-        Astrophysics Research Centre, School of Mathematics and Physics, Queen’s University Belfast, BT7 1NN Belfast, UK
+        Astrophysics Research Centre, School of Mathematics and Physics, Queen's University Belfast, BT7 1NN Belfast, UK
         \and
@@
         \and
-        LESIA, Observatoire de Paris, Université PSL, CNRS, 5 Place Jules Janssen, 92190 Meudon, France}
+        LESIA, Observatoire de Paris, Universit\'{e} PSL, CNRS, 5 Place Jules Janssen, 92190 Meudon, France}
 
-   \date{Received 7 Feb 2025; Accepted XXXX}
+   \date{Received 7 Feb 2025; Accepted 13 Apr 2025}
 
@@
 All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.
-%For UVES, the \ce{Fe} \hl{NNNN angstrom} line was used to track global wavelength drifts between different exposures which were corrected for at the same time.
-To measure these, a Gaussian was fit to the line, and the velocity offset from the rest frame position determined.
 
-%
 After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
 This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption, etc.), as outlined below.
-Note that after this correction, the %HARPS
-data still have the overall instrumental blaze-profile included.%, while the 2d-spectra from UVES were already corrected for this.
+Note that after this correction, the data still have the overall instrumental blaze-profile included.
 
@@
 
-The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.%(the night of 2018-05-06 and \hl{DATE} for UVES).
+The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.
 %
@@
 %
-Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,\AA{} - 4075\AA).%\hl{, and OO and PP} for HARPS and UVES respectively.
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,\AA{} - 4075\AA).
 
@@
 
-%For both HARPS and UVES w
 We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
 %
-%For HARPS
 This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.
@@
 %
-These coadded spectra %for \ac{harps} and \ac{uves} 
-are shown in Figure~\ref{fig:spec_CN_stellar_frame}.
+These coadded spectra are shown in Figure~\ref{fig:spec_CN_stellar_frame}.
 %
@@
 %
-For the comet sample we selected features deeper than 60\% %\hl{and 40\%} for HARPS and UVES, respectively, 
-while spectra with features below 15\% %for both HARPS and UVES 
-were flagged as `low activity'.
+For the comet sample we selected features deeper than 60\% while spectra with features below 15\% were flagged as `low activity'.
 %
@@
 %
-We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm$0.35~$\AA$ for the \ion{Fe}{I} 3859.9$\AA$ line, while for the other lines a width of $\pm$0.15$\AA$ was used.
+We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm0.35$\AA{} for the \ion{Fe}{I} 3859.9\AA{} line, while for the other lines a width of $\pm0.15$\AA{} was used.
 
-Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean} do not show any clear signals, and we therefore proceed to estimate our detection limits.
+Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean}) do not show any clear signals, and we therefore proceed to estimate our detection limits.
 
@@
 Part of this work was supported by the German \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project number Ts~17/2--1.
-
+%
 AF acknowledges support from STFC award ST/T00021X/1. EdM acknowledges support from STFC award ST/X00094X/1.

### 2025-04-16 src/scripts/calc_ccf.py
unused scripts

@@ -1,25 +1,0 @@
-import numpy as np
-from astropy.table import Table
-import paths
-
-
-# dummy file that generates the output for plot_ccf.py
-#
-# this should contain the CCF generating code
-#
-#
-# output files should be ccf_data1.txt
-
-from numpy.random import default_rng
-rng = default_rng(12345) # seed number guarantees this is repeatable
-
-vel = np.arange(-50,50,10)
-
-N11 = np.ones_like(vel)*11 + rng.standard_normal(10)
-N12 = np.ones_like(vel)*12 + rng.standard_normal(10)
-N13 = np.ones_like(vel)*13 + rng.standard_normal(10)
-
-
-t = Table([vel,N11,N12,N13],names=['vel', 'N11', 'N12', 'N13'])
-
-t.write(paths.data / 'ccf_data1.ecsv',format='ascii.ecsv',overwrite=True)

### 2025-04-16 src/scripts/calc_ccf_mean.py

@@ -1,25 +1,0 @@
-import numpy as np
-from astropy.table import Table
-import paths
-
-
-# dummy file that generates the output for plot_ccf.py
-#
-# this should contain the CCF generating code
-#
-#
-# output files should be ccf_data1.txt
-
-from numpy.random import default_rng
-rng = default_rng(5555) # seed number guarantees this is repeatable
-
-vel = np.arange(-50,50,10)
-
-N11 = np.ones_like(vel)*1 + rng.standard_normal(10)
-N12 = np.ones_like(vel)*2 + rng.standard_normal(10)
-N13 = np.ones_like(vel)*3 + rng.standard_normal(10)
-
-
-t = Table([vel,N11,N12,N13],names=['vel', 'N11', 'N12', 'N13'])
-
-t.write(paths.data / 'ccf_data1_mean.ecsv',format='ascii.ecsv',overwrite=True)

### 2025-04-16 src/scripts/gauss_slope_fit.py

@@ -1,79 +1,0 @@
-import numpy as np
-from astropy.table import Table
-import paths
-from astropy.modeling import models, fitting
-from astropy.modeling.models import Polynomial1D
-from astropy.modeling.models import Linear1D
-
-import matplotlib.pyplot as plt
-import warnings
-
-# dummy file that generates the output for plot_ccf.py
-#
-# this should contain the CCF generating code
-#
-#
-# output files should be ccf_data1.txt
-
-import matplotlib as mpl
-
-#mpl.use('macosx')
-
-pp1 = models.Gaussian1D(100, 0, 10)
-pp2 = models.Linear1D(slope=0.3, intercept=2.0)
-model = pp1+pp2
-
-rng = np.random.default_rng(seed=42)
-
-x = np.linspace(-50,50,100)
-
-y = pp1(x) + pp2(x) + rng.normal(0,5,x.shape)
-
-
-
-# Now to fit the data create a new superposition with initial
-# guesses for the parameters:
-gg_init = models.Gaussian1D(50, 0, 5) + models.Linear1D(0,0)
-fitter = fitting.SLSQPLSQFitter()
-
-
-
-with warnings.catch_warnings():
-    # Ignore a warning on clipping to bounds from the fitter
-    warnings.filterwarnings('ignore', message='Values in x were outside bounds',
-                            category=RuntimeWarning)
-    gg_fit = fitter(gg_init, x, y)
-
-print(gg_fit)
-
-plt.plot(x, y, 'ko')
-plt.plot(x, gg_fit(x))
-plt.xlabel('Position')
-plt.ylabel('Flux')
-
-plt.show()
-quit()
-
-def gsv():
-
-	return func
-
-
-def gauss_slope_fit():
-	'fit a gaussian plus a slope plus an offset'
-
-
-
-from numpy.random import default_rng
-rng = default_rng(5555) # seed number guarantees this is repeatable
-
-vel = np.arange(-50,50,10)
-
-N11 = np.ones_like(vel)*1 + rng.standard_normal(10)
-N12 = np.ones_like(vel)*2 + rng.standard_normal(10)
-N13 = np.ones_like(vel)*3 + rng.standard_normal(10)
-
-
-t = Table([vel,N11,N12,N13],names=['vel', 'N11', 'N12', 'N13'])
-
-t.write(paths.data / 'ccf_data1_mean.ecsv',format='ascii.ecsv',overwrite=True)

### 2025-04-16 src/scripts/plot_HARPS_CN_grid.py

@@ -1,210 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Dec 20 11:29:29 2022
-
-@author: demooij
-"""
-
-import matplotlib.pyplot as plt
-import numpy as np
-import paths
-from astropy.io import fits
-import matplotlib as mpl
-
-#mpl.use('macosx')
-
-
-T0=fits.getdata(paths.data/'T_gas.fits')
-N0=fits.getdata(paths.data/'Nf.fits')
-w=fits.getdata(paths.data/'broadening.fits')
-
-midpts_T=(T0[1:]+T0[:-1])/2.
-x=np.arange(midpts_T.shape[0])+1
-#T=10**np.polyval(np.polyfit(x,np.log10(midpts_T),1),np.arange(T0.shape[0]+1))
-T=np.hstack((0.,midpts_T,1.5*T0[-1]))
-
-midpts_N=(N0[1:]+N0[:-1])/2.
-x=np.arange(midpts_N.shape[0])+1
-N=10**np.polyval(np.polyfit(x,np.log10(midpts_N),1),np.arange(N0.shape[0]+1))
-
-
-
-fit=fits.getdata(paths.data/'fit_cube_comet.fits')
-sig0=fits.getdata(paths.data/'fit_err_cube_comet.fits')
-
-mean=fit[:,:,:,-1,:]
-sig=sig0[:,:,:,-1,:]#np.std(fit[:,:,:,:-1,:],axis=-2)/np.sqrt(fit.shape[-2])
-SN=mean/sig
-print(SN.shape,T.shape,N.shape,w.shape)
-
-f,ax=plt.subplots(1,6,figsize=(16,6),gridspec_kw={"width_ratios":[1,1,1,1,1,0.1]})
-vmin=np.min(SN[:,:,:,0])
-vmax=np.max(SN[:,:,:,0])
-for i in range(5):
-    im=ax[i].pcolormesh(N,T,SN[:,:,i,0],vmin=vmin,vmax=vmax,shading='flat')
-    ax[i].set_xscale('log')
-f.colorbar(im,cax=ax[-1])
-
-ax[0].set_ylabel('T [K]',fontsize=12)
-for i in range(5):
-    ax[i].set_xlabel('N$\cdot$f [cm$^{-2}$]',fontsize=12)
-    
-f.tight_layout()
-
-
-
-
-##run for simulation
[…]

### 2025-04-18 src/tex/ms.tex
tweaks
deps for analyze script

@@
 %
-Amongst these, the Ca H and K lines show deep absorption down to 0.1 of the continuum level.
+Amongst these, the \ce{Ca} H and K lines show deep absorption down to 0.1 of the continuum level.
 %
@@
 \subsection{Removing the stellar spectrum}\label{sect:starcor}
+
 The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and, for HARPS, shape of the blaze profile, are still present and need to be removed.
@@
 
-%\subsubsection{\ce{CN} Cross-section}
 The effective cross section of the coma will depend on how much is projected against the disk of \bp{}.
@@
 %
-The general causes are unclear, but there is evidence for several physical mechanisms that cause them 
-\citep{Kelley2021,Muller2024}.
+The general causes are unclear, but there is evidence for several physical mechanisms that cause them \citep{Kelley2021,Muller2024}.
+%
 ``Normal'' outbursts generally result in a brightness increases of 1--5 magnitudes, with smaller outbursts being more common.
@@
 %
-AF acknowledges support from STFC award ST/T00021X/1. EdM acknowledges support from STFC award ST/X00094X/1.
+AF acknowledges support from STFC award ST/T00021X/1.
+%
+EdM acknowledges support from STFC award ST/X00094X/1.
 %
@@
 %      
-An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/BetaPicCN}
+An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/BetaPicCN} using the {\tt showyourwork!} package \citep{Luger2021}.
 
@@
 
-\section{Selected exocomets.}\label{sec:app_FEBs}
-The dates for the nights selected to have the strongest exocomet features, as well as the depths and velocities of these features can be found in Tab.~\ref{tab:FEB_data}.
-\begin{table}
-\caption{Table with the nights with the strongest exocomet features.
-Note that the dates given are for the average of all the observations that were combined during each of the nights.}\label{tab:FEB_data}
+\section{Selected exocomets}\label{sec:app_FEBs}
+The dates for the nights selected to have the strongest exocomet features, as well as the depths and velocities of these features can be found in Table~\ref{tab:FEB_data}.
+\begin{table}[h]
+\caption{Nights with the strongest exocomet features.}
+\label{tab:FEB_data}
 \begin{tabular}{c c c}
-   BJD-2,400,000  &    v$_{comet}$  &  Depth\\
+   BJD-2,400,000\tablefootmark{a}  &    v$_{comet}$  &  Depth\\
  & [km/s] & \\
@@
 57849.0 & 10.3 & 0.73\\
+\hline
 \end{tabular}
+\tablefoot{\tablefoottext{a}{Dates given are for the average of all the observations that were combined during each of the nights.}}
 \end{table}

### 2025-04-18 src/scripts/analyse_HARPS_spectra.py

@@ -1,4 +1,4 @@
-#-*- coding: utf-8 -*-
+-*- coding: utf-8 -*-
 """
 Created on Tue Jul 26 15:54:53 2022
 
@@ -324,7 +324,7 @@ def generate_CCFs_orders(wlens,data_for_ccf,spec,pixels,broadening=5.,binsize=80
         ## Filter out the strongest circumstellar Fe I lines, that could contaminate the signal.
         idx=(indexing >= o_start[ord])*(indexing<o_end[ord])*(np.abs(wlens[ord,:]-3860.18)>0.35)*(np.abs(wlens[ord,:]-3856.63)>0.15)*(np.abs(wlens[ord,:]-3865.78)>0.1)*(np.abs(wlens[ord,:]-3878.83)>0.1)*(np.abs(wlens[ord,:]-3886.54)>0.1)
         
-        #ccf,ccf0=c_correlate(wlens[ord,o_start[ord]:o_end[ord]],data_for_ccf[:,ord,o_start[ord]:o_end[ord]],imdl_conv,dv=v_ccf)
+
         ccf,ccf0=c_correlate(wlens[ord,idx],data_for_ccf[:,ord,idx],imdl_conv,dv=v_ccf)
         m_ccf[:,ord,:]=ccf.copy()
 
@@ -344,17 +344,6 @@ def generate_CCFs_orders(wlens,data_for_ccf,spec,pixels,broadening=5.,binsize=80
         sim_ccf,sim_ccf0=c_correlate(wlens[ord,idx],sim_dat[:,ord,idx],imdl_conv,dv=v_ccf)
         m_sim_ccf[:,ord,:]=sim_ccf.copy()
 
-    '''
-    hdu=fits.PrimaryHDU( align_spectra(wlens,sim_dat,v_comet).swapaxes(1,0))
-    hdu.writeto('sim_tmp_{0:04d}_{1:.2e}.fits'.format(T_gas,N),overwrite=True)
-    
-    idx=(np.abs( 3e5*(wlens[7,:]-3933.663)/3933.663) < 10)+(np.abs( 3e5*(wlens[7,:]-3968.469)/3968.469) < 10)
-    for i in range(sim_dat.shape[0]):
-        sim_dat[i,7,idx]=np.nan
-    hdu=fits.PrimaryHDU( sim_dat.swapaxes(1,0))
[…]

### 2025-04-18 src/tex/ms.tex
language corrections

@@
 \usepackage{placeins}
-
 \newcommand{\angstrom}{\textup{\AA}}
@@
   % aims heading (mandatory)
-   {In the Solar system, the molecule cynaogen (\ce{CN}) and its associated ionic species are one of the most detectable molecules in the coma and tails of comets.
+   {In the Solar System, the molecule cynaogen (\ce{CN}) and its associated ionic species are one of the most detectable molecules in the coma and tails of comets.
    %
@@
    %
-   The high signal to noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal to noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.}
+   The high signal-to-noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal-to-noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.}
   % results heading (mandatory)
@@
 %
-Within our Solar system, comets deliver volatiles from the outermost reaches of the Oort cloud \citep{Obrien2018}, past the gas giants and terrestrial planets, even as close as a few solar radii.
+Within our Solar System, comets deliver volatiles from the outermost reaches of the Oort cloud \citep{Obrien2018}, past the gas giants and terrestrial planets, even as close as a few solar radii.
 %
@@
 %
-Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few km/s, attributed to the presence of the circumstellar material \citep{Hobbs85,VidalMadjar86}.
+Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few \kms{}, attributed to the presence of the circumstellar material \citep{Hobbs85,VidalMadjar86}.
 
-Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to the transit of evaporating exocomets in front of the star \citep{Ferlet87}.
+Transient absorption features appearing in the rotationally broadened \ce{Ca} H and K features were proposed to be due to the transit of evaporating exocomets in front of the star \citep{Ferlet87}.
 %
-These features appear and disappear on the timescale of hours to days, with some features lasting up to tens of days and have red-shifted velocities from eighty kilometers per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blueward side \citep{LagrangeHenri92} with widths from a few up to tens of kilometers per second.
+These features appear and disappear on the timescale of hours to days, with some features lasting up to tens of days and have red-shifted velocities from eighty kilometres per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blueward side \citep{LagrangeHenri92} with widths from a few up to tens of kilometres per second.
 %
@@
 %
-Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
+Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar System \citep{LecavelierdesEtangs22,Pavlenko22}.
 %
@@
 
-To the contrary of what is observed in the case of Beta Pictoris exocomets, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
+To the contrary of what is observed in the case of Beta Pictoris exocomets, most molecular and atomic signatures detected in the coma of Solar System comets are emission lines (or bands) instead of absorptions.
 %
-Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
+Spectroscopic observations of Solar System comets when they are very close to the Sun are rare due to observational difficulties.
 %
@@
 %
-For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
+For this comet, it was noticed that the main emission bands or lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
 %
@@
 %
-Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and Na and K were detected for comet C/2011 L4 \citep{Fulle13} at 0.46 au.
+Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and \ce{Na} and \ce{K} were detected for comet C/2011 L4 \citep{Fulle13} at 0.46 au.
 
@@
 
-For the majority of Solar system comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines \citep[e.g.
+For the majority of Solar System comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines \citep[e.g.
 ][]{hyland2019}.
@@
 %
-It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the comae of comets observed at relatively large distances from the Sun \citep[e.g.
-][]{Bus1991,Fitzsimmons1996}.
+It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the comae of comets observed at relatively large distances from the Sun \citep{Bus1991,Fitzsimmons1996}.
 %
-The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas coma.
+The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of approximately 2.6 photons per second per molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas coma.
 %
@@
 
-The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA{}\ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
+The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA{} may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
 %
-The \ce{OH} (0-0) band at $\lambda\simeq 3080$ \AA{}\ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
+The \ce{OH} (0-0) band at $\lambda\simeq 3080$\AA{} generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
 %
@@
 %
-Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the exocomets around \bp{}.
+Given the ubiquitous signature of \ce{CN} emission in Solar System comets, we have embarked on an archival search for this species in the exocomets around \bp{}.
 %
-Detection of this species would provide a solid link between cometary bodies in our Solar system and the \bp{} system.
+Detection of this species would provide a solid link between cometary bodies in our Solar System and the \bp{} system.
 
-We detail the observations in Section~\ref{sec:data}, along with the correction for the echelle blaze function and normalization of the spectra to a continuum.
+We detail the observations in Sect.~\ref{sec:data}, along with the correction for the echelle blaze function and normalization of the spectra to a continuum.
 %
-Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Section~\ref{sect:CNsearch}, and the discussion and interpretation is in Section~\ref{sec:discuss} with our conclusions in Section~\ref{sec:conclusion}.
+Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Sect.~\ref{sect:CNsearch}, and the discussion and interpretation is in Sect.~\ref{sec:discuss} with our conclusions in Sect.~\ref{sec:conclusion}.
 
@@
 %
-Although these observations cover a large baseline, the time between visits varies between 1 day and $\sim$2.2 years.
+Although these observations cover a large baseline, the time between visits varies between 1 day and approximately 2.2 years.
 %
-Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
+Similarly, the number of observations per epoch spans a wide range, between one and 356 exposures, while the exposure times vary between 12 and 900 seconds.
 %
-This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\,\AA{} and 4075\,\AA) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
+This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\AA{} and 4075\AA{}) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
 %
@@
 After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations.
-This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption, etc.), as outlined below.
+This was done after correcting for variations in the effective blaze profile (for example due to instrumental changes, differential slit or fibre losses, atmospheric absorption, etc.), as outlined below.
 Note that after this correction, the data still have the overall instrumental blaze-profile included.
@@
 
-The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.
+The night of 06 May 2018, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.
 %
@@
 The original spectrum was finally divided by this polynomial to correct for the changes.
-
-Note that the change of fiber for HARPS in June 2015 (JD$\sim$2,457,180) resulted in an overall change in the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in Sect.~\ref{sect:starcor}.
+%
+Note that the change of fibre for HARPS in June 2015 (JD$\sim$2,457,180) resulted in an overall change in the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in Sect.~\ref{sect:starcor}.
 
@@
 %
-Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,\AA{} - 4075\AA).
+Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\AA{} - 4075\AA{}).
 
@@
 
-The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and, for HARPS, shape of the blaze profile, are still present and need to be removed.
-
+The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and shape of the blaze profile, are still present and need to be removed.
+%
 We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
 %
-This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.
+This is done separately pre- and post-fibre change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.
 
-After this post-processing the overall (residual) blaze profile and stellar spectrum still need to be removed.
+After this post-processing the overall (residual) blaze profile and stellar spectrum  needs to be removed.
 %
-Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in e.g., the \ce{Fe} and \ion{Ca}{II} lines).
+Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in, for example, the \ce{Fe} and \ion{Ca}{II} lines).
 %
@@
 %
-As before, this was done separately pre- and post-fiber change.
+As before, this was done separately pre- and post-fibre change.
 
@@
 %
-These coadded spectra are shown in Figure~\ref{fig:spec_CN_stellar_frame}.
+These coadded spectra are shown in Fig.~\ref{fig:spec_CN_stellar_frame}.
 %
@@
 %
-The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}. The dates, velocities and depths of the selected exocomets can be found in Tab.~\ref{tab:FEB_data}
+The distribution of feature locations and depths is shown in Fig.~\ref{fig:FEB_velocity}. The dates, velocities and depths of the selected exocomets can be found in Tab.~\ref{tab:FEB_data}
 
-The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in Figure~\ref{fig:spec_CN_comet_frame}.
+The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in Fig.~\ref{fig:spec_CN_comet_frame}.
 %
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_stellar.pdf}
-        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
+        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300~K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
         %
@@
         \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
-        \caption{Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet.
+        \caption{Similar to Fig.~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet.
 The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
@@
 %
-The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.
+The theoretical spectra of \ce{CN} for several different temperatures are shown in Fig.~\ref{fig:CN_theory}.
 
@@
 We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm0.35$\AA{} for the \ion{Fe}{I} 3859.9\AA{} line, while for the other lines a width of $\pm0.15$\AA{} was used.
-
+%
 Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean}) do not show any clear signals, and we therefore proceed to estimate our detection limits.
@@
         \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
-        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7 \kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7 \kms{}. Contours show signal-to-noise upper limits.}
         \label{fig:CN_stellar_frame}
@@
         \includegraphics[width=\linewidth]{figures/HARPS_CN_exocomet_frame.pdf}
-        \caption{\ce{CN} measurement limits in the exocomet frame for a \ce{CN} line width of 2.7, 10 and 20 \kms{}. Contours show signal to noise upper limits.}
+        \caption{\ce{CN} measurement limits in the exocomet frame for a \ce{CN} line width of 2.7, 10 and 20 \kms{}. Contours show signal-to-noise upper limits.}
         \label{fig:CN_exocomet_frame}
@@
 %
-To avoid the aliasing peaks of the \ce{CN} band (see Figure~\ref{fig:CN_ACF}), we only fit the central $\pm$35 \kms{} of the CCF.
+To avoid the aliasing peaks of the \ce{CN} band (see Fig.~\ref{fig:CN_ACF}), we only fit the central $\pm$35 \kms{} of the CCF.
 %
-Fitting is done using the curve\_fit function from SciPy \citep{2020SciPy-NMeth}.
+Fitting is done using the {\tt curve\_fit} function from SciPy \citep{2020SciPy-NMeth}.
 %
@@
 %
-The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in Figure~\ref{fig:CN_stellar_frame} for the circumstellar gas and in Figure~\ref{fig:CN_exocomet_frame} for the strongest exocomet features.
+The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in Fig.~\ref{fig:CN_stellar_frame} for the circumstellar gas and in Fig.~\ref{fig:CN_exocomet_frame} for the strongest exocomet features.
 
@@
 
-As discussed above in the introduction, most studies of Solar system comets observe the \ce{CN} molecules via optical fluorescence. 
+As discussed above in the introduction, most studies of Solar System comets observe the \ce{CN} molecules via optical fluorescence. 
 %
-From measurements and simple physical arguments the \ce{CN} absorption/emission is optically thin everywhere.
+From measurements and simple physical arguments the \ce{CN} absorption or emission is optically thin everywhere.
 %
@@
 
-\ce{CN} in solar system comets comes from two sources.
+\ce{CN} in Solar System comets comes from two sources.
 %
@@
 %
-This in turn eventually photo-dissociates into the component atoms.
+This in turn eventually photo-dissociates into the component atoms:
 
@@
 
-For Solar system comets, measured \ce{CN} column densities are often converted to an overall production rate by the comet of $Q_{\ce{CN}}$ molecules/sec via an analytical model known as the ``Haser'' model \citep{Haser2020}.
+For Solar System comets, measured \ce{CN} column densities are often converted to an overall production rate by the comet of $Q_{\ce{CN}}$ molecules per second via an analytical model known as the ``Haser'' model \citep{Haser2020}.
 %
@@
 %
-The Haser model is somewhat simplistic but it represents the data well for solar system comets observed at typical distances from the Sun (1--3 au).
+The Haser model is somewhat simplistic but it represents the data well for Solar System comets observed at typical distances from the Sun (1--3 au).
 
@@
 
-We take the observed activity of 1P / Halley in 1985 / 1986 as a reference point for our estimates.
+We take the observed activity of 1P/Halley in 1985/1986 as a reference point for our estimates.
 %
-Although most Solar system comets are observed to be are far less active than Halley, some Long-Period comets show activity in excess of Halley.
+Although most Solar System comets are observed to be are far less active than Halley, some Long-Period comets show activity in excess of Halley.
 %
@@
 %
-When Halley was at $\sim 1$ au from the Sun, it was measured to have $Q_{\ce{CN}}\simeq 10^{27}$ molecules/sec using Haser models \citep{AHearn1995}.
+When Halley was approximately one au from the Sun, it was measured to have $Q_{\ce{CN}}\simeq 10^{27}$ molecules per second using Haser models \citep{AHearn1995}.
 %
 The assumed outflow velocity in the models was generally  $0.85 - 1$ \kms{} at this distance.
-
-For solar system comets, the normal Haser scale lengths used are \citep{Cochran86,AHearn1995} :
+%
+For Solar System comets, the normal Haser scale lengths used are \citep{Cochran86,AHearn1995}:
 
@@
 Both are assumed to scale with heliocentric distance $r_h^2$ as photodissociation or thermal desorption is assumed the main physical pathway for both the parent and \ce{CN}.
-
+%
 The lifetime of \ce{HCN} for photodissociation into \ce{H}+\ce{CN} at 1~au has been calculated to be $(3.2-7.7)\times10^4$ sec, with lifetime of \ce{CN} dissociating into \ce{C}+\ce{N} being $(1.3-3.1)\times10^5$ sec \citep{Huebner92}, depending on solar activity levels.
 %
-These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at $\sim 0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}.
+These are consistent with the measured scale lengths above if the parents of \ce{CN} are ejected at approximately $0.5$ \kms{}, and we take into account the excess photodissociation energy giving \ce{CN} an extra kick of $\simeq0.9$ \kms{} \citep{Fray2005}.
 
@@
 %
-Hence the photodissociation lifetime of \ce{CN} at 1 au from \bp{} of an `exoHalley' will be approximately 67 times shorter i.e. $\sim 3000$ sec.
+Hence the photodissociation lifetime of \ce{CN} at 1 au from \bp{} of an `exoHalley' is approximately 67 times shorter, for example around $3000$ sec.
 
@@
 %
-For \bp{} $L=8.7L_\odot$, so assuming all \ce{CN} production scales with stellar luminosity, exoHalley would have a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 9\times10^{27}$ molecules/sec.
+For \bp{} $L=8.7L_\odot$, so assuming all \ce{CN} production scales with stellar luminosity, an exoHalley has a larger \ce{CN} production rate of $Q_{\ce{CN}}\sim 9\times10^{27}$ molecules per second.
 %
-The total number of \ce{CN} molecules in the coma at 1~au at any given time would therefore be
+The total number of \ce{CN} molecules in the coma at 1~au at any given time would therefore be:
 
@@
 %
-The radius of the \ce{CN} coma will be given by
+The radius of the \ce{CN} coma is then given by
 $$r\sim v_{\ce{CN}} \tau_{\ce{CN}}$$
+%
 The outflow velocity of the parent \ce{HCN} will depend on the nuclear surface temperature, which will increase as a comet moves towards its parent star.
@@
 %
-Therefore gas outflow speeds are expected to be $\sim 1-2$ \kms{} at 1 AU, and the \ce{CN} coma radius will be
+Therefore gas outflow speeds are expected to be $\sim 1-2$ \kms{} at 1 AU, and the \ce{CN} coma radius will be:
 %
-$$r\sim (1-2) \times 3000 \leq 6\times 10^{3}\:{\rm km}$$
+$$r\sim (1-2) \times 3000 \leq 6\times 10^{3}\:{\rm km}.$$
 %
@@
 %
-Given that the coma is optically thin, and we do not resolve the star, the effective average column density towards \bp{} is
+Given that the coma is optically thin, and we do not resolve the star, the effective average column density towards \bp{} is:
 
@@
 
-$$n\sim\frac{3\times10^{31}}{\pi\cdot 1.7\times10^{22}}\sim 6\times10^{8}\:{\rm cm^{-2}}$$
-Therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{8}-10^{9}$ cm$^{-2}$.
+$$n\sim\frac{3\times10^{31}}{\pi\cdot 1.7\times10^{22}}\sim 6\times10^{8}\:{\rm cm^{-2}},$$
+therefore an exoHalley at 1~au from \bp{} would result in a \ce{CN} column density of $10^{8}-10^{9}$ cm$^{-2}$.
 %
@@
 %
- Comet Halley's nucleus has an effective radius of $5.5$ km \citep{Keller1987}, whereas Comet Hale-Bopp was one of the most intrinsically active comets on record with an extremely large nucleus of radius $\sim 14-21$ km \citep{Weaver1997}.
+ Comet Halley's nucleus has an effective radius of $5.5$ km \citep{Keller1987}, whereas Comet Hale-Bopp was one of the most intrinsically active comets on record with an extremely large nucleus of radius around $14-21$ km \citep{Weaver1997}.
 %
-However most of the apparent brightness was due to dust emission, and its only had $Q_{\ce{CN}}\simeq 3\times10^{27}$ molecules/sec \citep{Schleicher2024}.
+However most of the apparent brightness was due to dust emission, and its only had $Q_{\ce{CN}}\simeq 3\times10^{27}$ molecules per second \citep{Schleicher2024}.
 %
-In this case, we might anticipate the most active comets in the Solar system to have $Q_{\ce{CN}}\sim 10^{28}$ molecules/sec, implying a commensurate increase of a factor 10 in column density $n$ over an exoHalley at \bp{}.
+In this case, we might anticipate the most active comets in the Solar System to have $Q_{\ce{CN}}\sim 10^{28}$ molecules per second, implying a commensurate increase of a factor 10 in column density $n$ over an exoHalley at \bp{}.
 
@@
 %
-Assuming this is possible for exocomets at \bp{} would increase $N_{\ce{CN}}$ and $n$ by a factor $\sim 5$.
+Assuming this is possible for exocomets at \bp{} would increase $N_{\ce{CN}}$ and $n$ by a factor of around five.
 
@@
 %
-Studies of Halley and Hale-Bopp showed power laws close to this {\it i.e.} \cite{Biver2002}.
+Studies of Halley and Hale-Bopp showed power laws close to this \citep[e.g. ][]{Biver2002}.
 %
-But the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically
-$$N_{\ce{CN}}=\frac{Q_{\ce{CN}}(1~\rm{au})}{r_h^2}\cdot  \tau_{\ce{CN}} (1~\rm{au}) r_h^2 =\:{\rm constant} $$
-Hence the total amount of \ce{CN} in the coma should be approximately independent of stellar distance, and the total cross-section would not change.
+But the photodissociation lifetime $\tau_{\ce{CN}}\propto r_h^{2}$, so theoretically:
+$$N_{\ce{CN}}=\frac{Q_{\ce{CN}}(1~\rm{au})}{r_h^2}\cdot  \tau_{\ce{CN}} (1~\rm{au}) r_h^2 =\:{\rm constant},$$
+hence the total amount of \ce{CN} in the coma should be approximately independent of stellar distance, and the total cross-section would not change.
 
@@
 %
-As the apparent brightness is directly proportional to the amount of material (gas+dust) in the coma, this implies short term increases in $N_{\ce{CN}}$ and $n$ of factors $\sim 2-100$.
-
+As the apparent brightness is directly proportional to the amount of material (gas+dust) in the coma, this implies short term increases in $N_{\ce{CN}}$ and $n$ of factors ranging from 2 to 100.
+%
 Large outbursts are often due to partial or total disruption of a comet and can occur when a comet is closer to the Sun.
@@
 %
-A larger and/or hyperactive nucleus could increase $n$ by a factor of ten.
+A larger or more hyperactive nucleus could increase $n$ by a factor of ten.
 %
@@
 %
-Below 100K the sensitivity is $10^{12}$cm$^{-2}$ and above from 100 - 1800~K, is $10^{13}$cm$^{-2}$.
+Below 100~K the sensitivity is $10^{12}$cm$^{-2}$ and above from 100 - 1800~K, is $10^{13}$cm$^{-2}$.
 %
@@
 %
-A more dedicated observing campaign over several years using dedicated spectrographs can reach the equivalent Solar system limits for \ce{CN}.
+A more dedicated observing campaign over several years using dedicated spectrographs can reach the equivalent Solar System limits for \ce{CN}.
 %
-PLATO will carry out a dedicated long stare campaign that will observe the star with sub-millimagnitude photometry over 2 to 3 years.
+PLATO will carry out a dedicated long stare campaign that will observe the star with sub-millimagnitude photometry over two to three years.
 %
-This presents an excellent opportunity for coordinated spectroscopic campaigns where the exocomet population of \bp{} can be characterised, with \ce{CN} and ideally other molecules known from Solar system comets to be identified in another stellar system.
+This presents an excellent opportunity for coordinated spectroscopic campaigns where the exocomet population of \bp{} can be characterised, with \ce{CN} and ideally other molecules known from Solar System comets to be identified in another stellar system.
+
+\section*{Data availability}
+
+An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/BetaPicCN} using the {\tt showyourwork!} package \citep{Luger2021}.
 
@@
 %
-An online repository with materials used in this work is available at \url{https://github.com/mkenworthy/BetaPicCN} using the {\tt showyourwork!} package \citep{Luger2021}.
 

### 2025-04-18 src/scripts/analyse_HARPS_spectra.py

@@ -1,4 +1,3 @@
--*- coding: utf-8 -*-
 """
 Created on Tue Jul 26 15:54:53 2022
 
